% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggLeech}{%
  \mychapter{Leeches}{leeches}
}

\renewcommand{\yggLeechText}{%

  \mysection{Knowledge }{leech-knowledge}

  \mytable{l X}{
    \thead{Level} & \thead{Knowledge} \\
  }{
    1 & d8 \STATIC \\
    2-3 &  d10 \STATIC \\
    4-5 &  d12 \STATIC \\
    6-7 &  d16 \STATIC \\
    8 &  d20 \STATIC \\
    9 &  d24 \STATIC \\
  }

  The Crux of Knowledge is represented by a the \STATIC Knowledge Die.  Sometimes you may be asked to make a Knowledge Test.  To do so, \RO using your Knowledge Die plus \INT and any other modifiers.
  \example {
    \mybold{Knowledge Test}

    \RO: \INT plus \mybold{Knowledge Die} plus \mybold{Modifiers}

  }

  Any time you fail a Knowledge Test, you begin to accumulate negative modifiers.  The modifiers reset once you take a Bivouac or longer rest.

  \mytable{l X} {
    \thead{Failure} & \thead{Modifier} \\
  } {
      1st  & -1 \\
      2nd  & -1 \\
      3rd  & -2 \\
      4th  & -3 \\
      5th  & -5 \\
      6th  & -8 \\
      7th  & -13 \\
      8th  & etc. \\
}

\cbreak

\mysection{Research}{leech-research}

Research is used to perform \mylink{Chymistry}{leech-chymistry}, and can be used to help Sorcerers practice \mylink{Inscription}{sorcerer-inscription}.  Your Research is equal to your maximum \INT (so if you have a d12 \INT, you have 12 Research). You may only perform Research in a Civilization with a library 

If you take a Sabbatical, the number of Research Die you have is tripled (so 12 Research becomes 36).

Use your Research to "build" one or more \KNACK called Research Die. You can "build" as many Research Die as you choose up to your Research total. For example, if you have 12 Research, you could create:

\mybullet {
  \item 2 6-in-6 Research Die
  \item 3 4-in-6 Research Die
  \item 6 2-in-6 Research Die
  \item etc.
}

Remember that a Research Die is a \KNACK.  If your Research Die is a 2-in-6, you get a success if you roll a 1 or a 2 on a d6; if the die is 6-in-6, you roll 2d6 and only fail on a 2 (snake eyes).  You can only roll each Research Die once per Sabbatical.

Research Dice can be traded to \mylink{Sorcerers}{sorcerers} as well as to other Leeches (knowledge is shared, after all). You can give as many of your Research Dice to different people as you wish, but you can only accept a number of Research Dice up to your \LVL-1.

\newpage

\mysection{Leechcraft}{leech-leechcraft}

The skills of healing and mending.  To perform Leechcraft, you must make a \mylink{Knowledge Test}{leech-knowledge}

  \example {
    \mybold{Knowledge Test}

    \RO: \INT plus \mybold{Knowledge Die} plus \mybold{Modifiers}

  }



  You can perform Leechcraft as many times as you'd like, but remember that failed Knowledge Tests add progressively higher negative modifiers.

  Note that Leechcraft will only fix temporary effects (usually an effect with a \mylink{Markovian}{duration-markovian} duration) unless the \mylink{Purge}{keyword-purge} keyword is indicated.

  Finally, Leechcraft with a length of Minutes can be performed during a Breather, and Hours can be performed during a Bivouac.  If taking a Bivouac, you must roll \mybold{before} you reset the negative modifiers on your Knowledge.  You can try again after you reset your negative modifiers, but this would require another Bivouac.  

 
  \LEECHCRAFT[
    Name=Bonesetting,
    Link=leechcraft-bonesetting,
    Mod=+3,
    Length=Hours,
    Keywords=Purge
  ]
  Purge a single non-serious Physical Wound

  \LEECHCRAFT[
    Name=Delay Infection,
    Link=leechcraft-delay-infection,
    Mod=+3,
    Length=2 Maneuvers,
    Keywords=None 
  ]
  
  Delay the onset of a single Disease (including contagion) for Hours.  Curing the disease requires \mylink{Medicinals}{leech-medicinals}

  \cbreak

  \LEECHCRAFT[
    Name=Hair of the Dog,
    Link=leechcraft-hair-of-the-dog,
    Mod=+9,
    Length=Minutes,
    Keywords=Purge 
  ]
  Purge the effect of a Hang Over on a single person

  \LEECHCRAFT[
    Name=Laudanum,
    Link=leechcraft-laudanum,
    Mod=+0,
    Length=see below,
    Keywords=Purge 
  ]
  Purge a single non-serious Mental Wound (Minutes) OR remove a Disgusted, Shaken, or Sickened effect (1 Maneuver) on a single patient

  \LEECHCRAFT[
    Name=Mend,
    Link=leechcraft-mend,
    Mod=+9,
    Length=1 Maneuver,
    Keywords=None 
  ]
  Can only be applied to a patient on Death's Door. Heal 1 Flesh

  \LEECHCRAFT[
    Name=Purge Toxin,
    Link=leechcraft-purge-toxin,
    Mod=+3,
    Length=1 Maneuver,
    Keywords=Purge 
  ]
  Immediately purge a toxin from the body of a single patient

  \LEECHCRAFT[
    Name=Restore Senses,
    Link=leechcraft-restore-senses,
    Mod=+6,
    Length=2 Maneuvers,
    Keywords=None 
  ]
  Remove a Blindness or Deafness effect on a single patient

  \LEECHCRAFT[
    Name=Sew Wounds,
    Link=leechcraft-sew-wounds,
    Mod=+9,
    Length=Minutes,
    Keywords=None 
  ]
  The patient rolls 1 \FLESH and heals that much Flesh. You can only do this once per patient during a Breather or Bivouac (before you erase your Knowledge failures).

  \LEECHCRAFT[
    Name=Smelling Salts,
    Link=leechcraft-smelling-salts,
    Mod=+6,
    Length=2 Maneuvers,
    Keywords=Purge 
  ]
  Purge a Knocked Out effect on a single patient


  \LEECHCRAFT[
    Name=Staunch,
    Link=leechcraft-staunch,
    Mod=+6,
    Length=1 Maneuver,
    Keywords=Purge 
  ]
  Purge a Bleed effect on a single patient

  \cbreak

  \LEECHCRAFT[
    Name=Trepanation,
    Link=leechcraft-trepanation,
    Mod=+0,
    Length=Hours,
    Keywords=Purge 
  ]
  Purge a Woozy effect on a single patient

  \LEECHCRAFT[
    Name=Virtigo,
    Link=leechcraft-virtigo,
    Mod=+6,
    Length=Hours,
    Keywords=Purge 
  ]
  Purge a Befuddled or Concussed effect on a single patient

  \newpage

\end{multicols}

\mysection{Medicinals}{leech-medicinals}



\myital{These are pretty much verbatim from Logan Knight's amazing \href{https://www.lastgaspgrimoire.com/does-this-look-infected}{Does This Look Infected?}}

\hrulefill



Medicinals are practiced during Sabbatical to purge Disease, Addiction, and Madness as well as repair the effects of a serious Physical wound.  Leeches are able to purge these afflictions using a Research Die.

\mynumlist {
  \item State how many Research Die you wish to roll.  These will be rolled regardless of what happens in step \#2
  \item Roll a d16 and consult the chart below.  If you do not have enough coins, the Medicinal immediately fails and victim suffers the \mybold{Misdiagnosis}
  \item \RS your Research Dice.  If the number of failures exceed the number of successes, you have a Misdiagnosis: the Wound, Disease, Addiction, or Madness is not cured and you lose the money invested. 
}

You can try for as long as you have Research Die.

If you don't have a Leech in your party, you can find one (or more) in a Sanitarium (see Core Rules). The Research Die used by a leech or wisewoman you find are the same as the odds of finding a Sanitarium (i.e. 2-in-6 for Medium and 6-in-6 for Large), and the cost in coins is the same.

The \COST depends on the Civilization - Iron (Small), Silver (Medium), or Gold (Large)


\mynumlist {
  \item \COST 10.  The patient must eat the worm-infested testicles of a rabid baboon. They populate quickly and enter the bloodstream, consuming insantities and diseases. Before the worms turn to feast upon healthy tissue, their veins will be opened so that they fall from them onto an open flame. 

\myital{Misdiagnosis:  Not all of the worms are removed, which makes things rather uncomfortable for the patient}

  \hrulefill

  \item \COST 10.  A clyster of hot eel blood and the crushed eggs of a Horned Soldier Crab. 

\myital{Misdiagnosis:  Not all of the eggs were crushed, after a week they begin to hatch and leave their body}

\hrulefill



  \item \COST 15. An incision must be made along the abdomen  with a golden blade. After it has been allowed to weep the wound will be smeared with saccharine nectar squeezed from the abdomen of Larder Ants, then sutured with the final dying bite of their heads. 

\myital{Misdiagnosis:  No matter how hard they try flies keep getting into the wound. That's how you get maggots.} 

\hrulefill



  \item \COST 15. Swallow a ward-inscribed lead ball, still glowing from the fire. 

\myital{Misdiagnosis:  The ball sears their esophagus on the way down; say goodbye to solid food for at least a week.}

\hrulefill



  \item \COST 20. Bloodletting of one or more limbs. Once venesected, the blood must be allowed to flow into heated iron bowls to be boiled away, banishing the maladies in acrid smoke. 

\myital{Misdiagnosis:  That was a little too much blood. They lose 1 Flesh permanently}

\hrulefill



  \item \COST 20. Sin-Eater. It is an uncleanliness of the spirit that has caused the blight to manifest. A layer of skin must be flayed from the thigh and offered to the Leech, who will sear it over a flame for consumption along with a cup of blood from the afflicted. 

\myital{Misdiagnosis:  you are overcome with revulsion and throw the victim out onto the street without further explanation}

\hrulefill



  \item \COST 25. The purifying qualities of quicksilver will remove the taint from them. Thin, steady streams are to be poured into the eyes, windows of the soul. 

\myital{Misdiagnosis:   They are inflicted with a random Insanity}

\hrulefill



  \item \COST 30. A limb is covered with grubs sourced from the rotting undergrowth of the Grimm Wood, who consume a few dozen mouthfulls of flesh, transfering the malady to themselves and falling dead.The hardened bodies should then be ground to a fine powder and insufflated to prevent the infection from returning. 

\myital{Misdiagnosis:  When you grind the bodies of the grubs you finds them rock hard. In frustration you take to them with a hammer and they shatter into red crystalline shards.}

\hrulefill



  \item \COST 30. Upon a stone slab, lathered with the blood honey of the spore-crazed bees from deep within the Veins of the Earth, flaming torches will be passed over your body until the moisture has been sapped from the honey. Once it has cooled and crystallised from your skin the malady will be gone. 

\myital{Misdiagnosis:  For the next week the patient awakens each night at the edge of their roof, toes overhanging and ready to fall.}

\hrulefill



  \item \COST 35. The malady is inside of your stomach. You must swallow a live Hagora Fish caught in the foetid, sluggish streams of the Weald. As it digests your diseased stomach lining it will defecate the remedy into your bloodstream.  

\myital{Misdiagnosis:  Before it is digested the fish continues to devour your stomach lining once the diseased flesh is gone. Take a -1 to their Max Flesh.}

\hrulefill



  \item \COST 40. The thumb-sized yellow mould leeches from the stagnant pools of the Quenchless Mouth of Many can drain the corruption from your blood, but only if kept sufficiently warm and moist while they feed over two days. You may attempt to take them in your mouth, but it is recommended as a suppository. 

\myital{Misdiagnosis:  Swollen with blood, the leeches block whichever passage you chose to deposit them in. They will need to be burnt out.}

\hrulefill



  \item \COST 50. An excess of phlegm is the cause of your infection and discomfort. Four golden tubes will be tapped through your chest and into your lungs before fastening a bellows-mask over your face, forcefully pushing air down your throat in order to discharge the malady. 

\myital{Misdiagnosis:  The initial trickle of phlegm stops with a muted thump through the golden tubes. You heave on the bellows-mask and a writhing mass of black maggots discharge into the bowl.}

\hrulefill



  \item \COST 50. Trepanation of the skull should relieve the affliction. 

\myital{Misdiagnosis:  The patient should probably wear a helmet for awhile}

\hrulefill



  \item \COST 50. The malady persists because it dwells in the heart, pumping its filth throughout your body. Your lips will be painted with the venom of the Blue Lesionaire Spider, and when your vitals slow your heart must be removed and pierced with heated copper needles, draining it of trapped black bile.  

\myital{Misdiagnosis:  The venom eats away part of the patient's lips, making speaking difficult}

\hrulefill



  \item \COST 75. It is an overabundance and corruption of yellow bile that causes your fever and rot. An incision must be made below the ribs to allow the tainted bile to be expressed from the gallbladder. 

\myital{Misdiagnosis:  You discover a tumor full of teeth and auburn hair nestled below the patients ribs. A Sorcerer can use this as a spell component, but it's unsure what the effect might be on the patient ...}

\hrulefill



  \item \COST 100. You have the evil eye. It offends with its infection and must be plucked from you. 

\myital{Misdiagnosis:  Whoops.  Apologies for the error, would you like a false replacement or an experimental transplant? No charge!}

\hrulefill


}

\newpage

\begin{multicols}{2}

\newpage




} % end
