% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons
% Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggAppendices}{%
  \mychapter{Appendices}{Appendices}
}

\renewcommand{\yggAppendicesText}{%
  
  
  \mysection{Appendix A}{appendix-a}

  \mysubsection{Mishaps}{table-mishap}

  \myital{These are pretty much verbatim from Logan Knight's preposterous \href{https://www.lastgaspgrimoire.com/do-not-take-me-for-some-turner-of-cheap-tricks/}{Do Not Take Me For Some Turner of Cheap Tricks!}}

  \mybold{Roll your \INT (don't forget to add your level if you're a Philosopher!).   If you roll a Mishap you've already endured, roll again}


  \mytable{l X} {  
  } {
    1 &  Arbiter's Choice \\
    2 &  When you take damage to Flesh your body gushes saltwater instead of blood, tiny translucent organisms and vibrant crustaceans you never imagined writhe about on the floor. \\
    3 &  You grow thick white hair all over your torso.  No matter how many times you shave it comes back. \\
    4 &  Your eye color changes (doesn't affect sight): 1) blood-red and goat-like; 2) white and pupiless; 3) yellow and cat-like; 4) kaleidoscope \\
    5 &  You let out a deafening fart, extinguishing all Nearby torches and candles \\
    6 &  Brightly colored sparks fly from your ears \\
    7 &  An acrid stench wafts over you, every hair on your body is decomposing, you'll be bald by morning. You lose all your hair and it never grows back. \\
    8 &  Your tongue changes (doesn't affect speech): 1) forked; 2) long (down past your chin); 3) black and scaly;  4) two tongues! \\
    9 &  Your ears change (doesn't affect your hearing):  1) they fall off; 2) they become pointed and really long like an anime elf; 3) they become cat's ears and move to the top of your head; 4) they become long and floppy, like a basset hound \\
    10 &  You grow small ridged scales on your back, from your shoulders to your tailbone.  The itch terribly unless they are moistened occasionally.   \\
    11 &  You grow a ruff of feathers around your neck.  You like to keep them well preened. \\
    12 &  You grow a beard down to your chest, regardless of your gender.  The beard cannot be shaved off but it can be styled.  The color of the beard is: 1) white; 2) blue; 3) jet black; 4) rainbow  \\
    13 &  Your fingernails all grow to 5cm in length.  Trimming them never helps. \\
    14 &  One of your feet changes into a : 1) hoof; 2) chicken foot; 3) copy of the other foot (2 left feet); 4) backwards foot.  This doesn't affect your \MD \\
    15 &  Roll a d4.  Grow that many extra fingers, distributed on your hands however you want.  (the fingers have no other benefit, but buying gloves is more difficult) \\
    16 &  The hair on your head always stick straight out, and changes color to: 1) bone white; 2) bright blue; 3) jet black; 4) rainbow colored, like a clown wig \\
    17 &  Your nose changes (doesn't affect your sense of smell):  1) falls off and becomes 2 nostril slits; 2) becomes elongated and warty; 3) becomes a pig's snout; 4) becomes a mouth (can't talk) \\
    18 &  A tiny raincloud appears directly over your head and begins raining.  Hard.  Everyone Close to get you will get drenched, as will every light source. The raincloud lasts for the remainder of the Session. \\
    19 &  Your footsteps produce: 1) wisps of smoke; 2) a faint sulphorous smell; 3) birdlike footprints, no matter what footwear you're wearing 4)  no footprints at all \\
    20+ & Nothing happens \\
  }

  \newpage


  \mysubsection{Calamities}{table-calamities}

  \myital{These are pretty much verbatim from Logan Knight's preposterous \href{https://www.lastgaspgrimoire.com/do-not-take-me-for-some-turner-of-cheap-tricks/}{Do Not Take Me For Some Turner of Cheap Tricks!}}


  \mybold{Roll your \INT (don't forget to add your level if you're a Philosopher!).   If you roll a Calamity you've already survived, roll again}


  \mytable{l X} {  
  } {
    1 &  A dripping ball of smouldering black sludge consumes your heart, burning a hole through your chest. You still live, but you are now Unhallowed. \\
    2 &  Everything Nearby with a mouth must Save or vomit slick red fish for d4 Markovian.  While vomiting they are effecitively Paralyzed \\
    3 &  A mouth grows from a random location on your body. For the most part it just breathes loudly and tries to bite anything that comes near it, but as soon as you tell a lie it will yell the truth. \\
    4 &  d4 small hard nodules push out of your shoulders around the base of your neck. They continue to grow and twist out into hard, ridged horns, like some kind of morbid cage collar behind your head, within a month they're about 3 feet long, but they won't stop there.  \\
    5 &  Your jaw dislocates and your throat dangles like a crop. Your jaw now hinges on over- elasticised tendons and your throat can stretch and swell like that of a pelican or frog. \\
    6 &  Your head and face swell and turn black, and the flesh begins to slough away from it.  In Days your head is replaced with that of 1) a bat; 2) a tiger; 3) a cobra; 4) a lizard \\
    7 &  The skin of your back becomes porous and elastic and you sprout thousands of thick dry skin tags. Your tongue can now extend 3 feet in length and sweats some kind of oil, you find yourself licking your back to relieve the dry pain. \\
    8 &  Hundreds of blueish 6 inch long tendrils grow below your jaw and down your throat.  \\
    9 &  Your legs become pudgy and pink and your feet turn black like frostbite. When the flesh sloughs away from your feet they are cloven like a pig's. You discover you now have three sets of distended teats lining your stomach. Two pudgy, pliable arms gradually grow from just above your hips, if a pig had fingers they would look like this.  The arms cannot move. \\
    10 &  Short fleshy stalks bearing pink textured globes grow from a random location on your body. In times of extreme stress these globes explode into violet flowers in a cloud of white dead-skin spores. You immediately feel the sensation of being wildly licked by multiple tongues over the stalked area by something you cannot see. The stalks will regrow in a new location in Weeks. Over time you will learn to control the spores, but hope you never see the things following you for nourishment. \\
    11 &  Vaguely translucent oyster-like keratin growths appear in multiple places on your body. \\
    12 &  You can't stop drooling black bile. It seems to be mildly acidic to everything but your own flesh. If you regurgitate a pool of it eyes emerge and pop amongst its surging mass. \\
    13 &  You grow a set of breasts in addition to any you may have already. These breasts constantly leak a bitter smelling amber fluid. You keep waking up with small soft crawling things with bright eyes feeding from you in the dark. \\
    14 &  A random part of your body begins to swell, and fine layers of sticky silk thread develop over it until it is no more than a webbed mound. Delicate pure white moths constantly fly in and around it, if you cover it the flesh beneath burns as if being bitten by a thousand ants, making it impossible to cast spells. Every now and then it will burst in a cloud of small flying moths that all seem to hum the same dirge. \\
  }

  \mytable{l X} {  
  } {
    15 &  Until you take a Vacation, your nose becomes an ideal environment for the incubation of hundreds of small seed-shaped slippery tags of flesh, like a capsicum. If the seeds aren't harvested daily you are likely to become a target for birds and rodents. \\
    16 &  Thick mounded glands swell from the sides of your throat, when pressed they secrete a pungent black grease. Female rats are drawn to you, forming a protective maternal coven. \\
    17 &  Luminous orange anemone fronds grow in and around your eye sockets, engulfing your eyes. You now have Low Light vision. \\
    18 &  Your eyes boil and burst and the skin of your arms and hands splits as new eyes bubble out like eggs on a frog's back.  Your \MAX Awareness is increased \DCUP \\
    19 &  Fluted holes appear in your skin near hard areas of bone, particularly your elbows, shins, shoulders and spine. A colony of glassy purple ant-like creatures takes residence inside your bones, feeding on the marrow. Your \MAX Flesh is reduced by 1, but your Grit is increased by d4. \\
    20+ & Roll on Mishaps instead \\
  }

\newpage

  \mysubsection{Ruin}{table-ruin}

  \myital{These are pretty much verbatim from Logan Knight's delightful \href{https://www.lastgaspgrimoire.com/do-not-take-me-for-some-turner-of-cheap-tricks/\#thatwhichshouldnotbe}{That Which Should Not Be!}}

  \mybold{Roll your \INT (don't forget to add your level if you're a Philosopher!).   If you roll Ruin you've already miraculously survived, roll again}

  \mytable{l X} {  
  } {
    1-2 &  You immediately die and melt into a puddle of blood.  The puddle is impossibly deep, and dark shapes can be seen stirring in its depths.  Anyone who steps into the puddle plunges and sinks for eternity, lost in the depths of space and time. \\
    3-4 &  You suddenly find yourself with a piece of chalk in your hand. You sketch a door on the nearest flat surface. It is real, and leads into some sort of cave. You walk in and do not come out. Your allies can hear slithering noises from beyond the threshold.  If they walk in they don't come out either. \\
    5-6 &  Everything goes dark, you lose sight of the walls, your companions are around you with shining white eyes, they rend and tear at your flesh, stuffing their mouths, not even chewing in their haste to fill their bellies, your attempts to fight back pass through them like a shadow.  Moments later your companions find themselves sitting in a circle around the place where you last stood with distended bellies and blood soaked hands and mouths. The only remaining trace of the caster is a wax-sealed skull sitting in their midst.  \\
    7-8 &  You are wracked with unimaginable pain and turn white hot.  It is impossible to look at you.  There is a high pitched screaming on the air, like a tea kettle left on too long.  After a few Moments you detonate.  Everyone Nearby takes [sum] {lvl}d6 damage (Save vs. Doom for half).  You are very dead. \\
    9-10 &  Your head shreds open and a fountain of blood towers out of your kneeling body. The blood is thick and viscous and shifts into surprising palettes of colour, it splatters and spreads across the roof, there are things in it. They reach out with breaking joints before slopping to the floor and reforming as something else, they give birth to things which consume them and crawl towards you with a scream that is a gurgle then float to the roof like a drop of water watched in reverse.  You should probably seal the door. \\
    11-12 &  You lift into the air and d4 limbs tear themselves away from your body. Flesh rips and tendons snap, you watch as the limbs dissolve in mid air as if being digested before you drop to the floor.  You immediately fall to Death's Door, and begin Bleeding. \\
    13-14 &  Another, naked you falls away from you to the floor, like a photograph being moved away from another, strands of pus and membrane string between you. There is a 3-in-6 chance that the naked one is actually you.  The Arbiter will privately inform you which one is you at the end of the Session. If you are killed and the Other lives, or the Other is allowed to stay with the party for some other reason, they will be friendlier than ever, and will become steadfastly loyal to whoever shows the most interest in a true friendship. Once they have made a true friend they will want to be near them always, and one night while their friend sleeps by their side the Other's jaw will dislocate and stretch, and they will try to swallow their friend whole. \\
  }

  \mytable{l X} {  
  } {
    15-16 &  For the next d3 Moments including this one, your head explodes and reforms itself.  Every Moment, roll all of your Blood Die for each spell etched in your skull as if you were casting the spell on yourself.  You decide the order you want to roll in.  If you run out of Blood Die before you "finish", your head doesn't reform itself (and you die). \\
    17-18 &   A dozen hands push out in a line down your torso, drawing back your flesh like a stage curtain. When you look into the darkness it's like going through a tunnel until you reach yourself illuminated by a hundred tallow candles, seated upon a throne of flesh and bone, staring back down the tunnel into the abyss.  You remain this way for d3 Hours.  If you are moved during this time, the hands finish ripping you open and fold back in on themselves, killing you.  Otherwise, the hands pull your torso back together (leaving a hideous scar) and you immediately fall to Death's Door.  Your \MAX Sanity is permanently reduced by \DCDOWN \\
    19-20 &  Your throat expands and snakes begin to slide out of your mouth, your stomach splits open and piles of them slop to the floor, offspring slime out of their wombs and reach adulthood almost as fast as they are born, in turn giving birth to their own young, they slither across the floor in an ever expanding pile of writhing flesh and scales. They'll stop birthing after they've multiplied enough to fill a 10m room (will take Minutes).  The snakes are a Swarm (see core rules), and have 1 {hd} for every square meter of space they would fill.  The snakes will attack everyone but you.  Once they have all been birthed, you immediately fall to Death's Door. \\
    21+ &  Roll on the Calamity table instead. \\
  }

  \newpage

  \mysubsection{Crisis of Faith}{table-crisis-of-faith}

  \myital{The Legend: Logan Knight: \href{https://www.lastgaspgrimoire.com/ive-gotta-have-faith/}{I've Gotta Have Faith}}

  \mybold{Roll your \FOC (don't forget to add your level!).   If you roll a Crisis of Faith you've already survived, roll again}
  
  \mytable{l X} {  
  } {
    1 &   A new eye emerges on either side of the base of your throat. When you witness things that would normally gain Faith, there is a 3-in-6 chance that the eyes see the truth that there was nothing divine about it and you gain nothing. \\
    2 &  It all suddenly becomes clear. You realise there are no true gods and fly into a violent rage against any and all around you. If you survive you are no longer a Mystic, and hold nothing but contempt for those who maintain their religious beliefs.  Immediately change your Flavor to something other than Mystic.  You gain all of the abilities of this Flavor at your level, but do not get anything that would be gained during character creation. \\
    3 &    You fall to your knees and regurgitate page after page scrawled with your own writing. They are filled with lies about your god, filled with doubt and blasphemy, there is enough to fill a tome. It will be Days before you are able to regain Faith. \\
    4 &  Stigmata. Pain racks your body as if splintering wooden spikes were being pushed into your flesh, wounds stretch open and blood seeps out around the edge. The blood is dark and viscous and reeks of age. Lose 1 Flesh permanently. \\
    5 &   You experience the agonising birth of your god for the next d3 Minutes. They just want you to know how much they went through for you, and you've let them down.  You are completely incapacitated for the entire experience, and fall to Death's Door when it's over. \\
    6 &  The integrity of the your flesh becomes dubious, you feel numb and lesions break out across your skin. For the next Days you take double damage.  \\
    7 &  Your holy symbol melts or crumbles into shards of refuse, like burs pulled from a dog's fur. If you do not have your holy symbol, your non-dominant hand shrivels to a black stump permanently. \\
    8 &  Your vision is stolen until you Bivouac (you are Blinded). When it returns you recall phantom flesh memory glimpses that you would rather not understand. \\
    9 &  For the next Weeks animals shy and howl and cry when you are near, and you suffer from Anathema. \\
    10 &  The floor splits and steam the colour of orange rot billows out like a mushroom cloud. Darkness rolls within its mass and everyone Nearby but the Mystic must make a Save vs. Doom. Those who fail lapse into seizures and speak in tongues for the d3 Minutes. Days afterward they'll notice the swollen lump at the base of their skull. \\
    11 &  Locusts the colour of bronze infested with corrosion pull themselves from the pores of your skin and swarm around you. Everyonen Nearby is Befuddled, stumbling around in a cloud of wings and mandibles for 2d4 Moments until they burrow back into your flesh. \\
    12 &  Insect legs bristle out of your skin like hair, when you break them they leak the blood of infants died in the womb. It smells like limbo. \\
    13 &  Visions of floating in the infinite while your god slowly consumes your mind and flesh fill your senses. For d3 Minutes collapse in terror/ecstasy depending on your god. \\
    14 &  Your tongue burns with an intense heat, you open your mouth and spit something to the floor, you smell your roasted flesh, your saliva still pops and sizzles. The orange hunk of metal on the ground cools into an image of a plump locust, lying on its back displaying bloated clusters of eggs coating its abdomen like a lobster. Whether you keep the idol or not you dream of the Locust Queen for the next month, of her desire for her children to blanket the land, of your special role in all this. \\
  }

  \mytable{l X} {  
  } {
    15 &  Any light sources in the area blow out, dark clouds cover the sun during the day, worms that you can only see because they're so much darker than anything around them squirm from the earth and wriggle around your feet. It will be over in d4 Hours. \\
    16 &  Your \VIG and \DEX are reduced to d3, and you cannot gain any Faith.  This persists until you take a Vacation and visit a shrine, temple, etc. of your Small God.  If you survive this test of Faith, gain 2 Faith. \\
    17 &  A manifestation of another god appears before you and proclaims that you have been worshipping a false idol. They give you this one chance of conversion; if you take it, gain 2 Faith and convert to the worship of this new god.  If you decide against it, you fall to Death's Door and begin Bleeding.  Let your god save you now. \\
    18 &  Your god demands that you recover a sacred relic from heathen hands, until you do so you cannot gain any further Faith. (Arbiter places relic and those holding it no more than a few days away, the Mystic instinctively knows where it is).  If you regain the sacred relic, gain 2 Faith. \\
    19 &  You sweat and shake with religious fever, incapacitated for Hours, but when you regain control of yourself you gain 2 Faith. \\
    20+ &  Nothing happens \\
  }

  \newpage

  \mysubsection{Lesser Curses}{table-lesser-curses}

  \mytable{l X} {  
  } {
    1 & All of your hair immediately falls off in a pile on the floor, and won't grow back \\
    2 & You can't enter a house or cross a threshold without the permission of someone already inside. \\
    3 & You can't cross running water (even over a bridge) unless someone carries you. \\
    4 & You sprout thick, white hair from the palms of your hands and your ears.  Close observation shows very tiny translucent crabs that make their home in the strands.  No one wants to shake your hand, but cats love licking up the crabs. \\
    5 & You are unable to speak your own name \\
    6 & The Arbiter gives you a new name.  Everyone (except you) thinks this is your real name, and you can't change their mind. \\
    7 & You become Unhallowed \\
    8 & Like a Spriggan, you can't hold anything made of Iron.  If you do, you take 1 point of damage directly to Flesh every Moment. \\
    9 & A small imp appears on your shoulder. The imp is played by the Arbiter, and causes no end of mischief.  You can slap, step on, stab, etc. the imp, who immediately disappears with a pop - but returns in Minutes.  Angry. \\
    10 & You fall into deep slumber when you hear music. You can only be woken by being shaken / slapped awake. \\
    11 & Everything you say is believed to be a lie \\
    12 & You can only speak in rhymes \\
}



  \mysubsection{Greater Curses}{table-greater-curses}


  \mytable{l X} {  
  } {

    1 & Your limbs become leaden and weighty, and now take up 4 Significant Items. \\
    2 & You are unlucky, and take an automatic 1 on any luck contest. \\
    3 & You are unable to hold coins of any sort.  Handing you any coins makes the coins disappear, permanently. \\
    4 & Dyslexia. You cannot read written words (including from a Grimoire) \\
    5 & Your eyes disappear from your face. You are Blinded \\
    6 & Your ears disappear from your head. You are Deafened \\
    7 & For any die you roll, if you roll a 13, treat it as a natural 1. \\
    8 & The sun burns and blisters your skin, doing 1 Flesh damage for every Moment in direct sunlight \\
    9 & You can't add the result of an Intangible Stat roll to any \RO or \RS attempt \\
    10 & You suffer from Anathema \\
    11 & When you are sneaking around, you have an uncontrollable urge to sing "Here Comes a Sneaky Boy!" at top volume (regardless of gender).  Stealth is impossible. \\
    12 & Your vocal cords are paralyzed and you cannot speak. \\
}

\newpage



\mysubsection{Diseases}{table-diseases}

Only Leeches can purge a disease with \mylink{Medicinals}{research-medicinals} during a Vacation, or slow its contagion using \mylink{Delay Infection}{leechcraft-delay-infection}.  Each Session, anyone who has come Close to the infected must \RS: \VIG; if you fail, you become infected with the disease as well.

\myital{These are pretty much verbatim from Logan Knight's amazing \href{https://www.lastgaspgrimoire.com/does-this-look-infected/}{Does This Look Infected?}}

A handful of Diseases have an effect that should (probably) be cured over a number of Sessions.  Wherever that's mentioned, it needs to be cured by the end of the Session indicated i.e.  if it says "after 4 Sessions, you suffocate", that means you have until the end of the 4th Session to get treatment, or ... you know, suffocate.


  \mytable{l X} {  
  } {
    1 &  Your skin grows raw and red and sprouts enormous blood blisters that swell to the size of a small apple before popping in arcs of putrid plasma, over and over again like boiling mud baths.\\
    2 &  Pus weeps from your throat and crusts into barnacle-like lesions on your neck, causing intense pain if you speak anything but lies.  \\
    3 &  A crater-like pox mars the flesh around the wound and creeps up your neck. The vinegary stench grows when you are under stress or heightened excitement and puffs of yellow vapour vent from the pox. Save vs. Toxins whenever you enter Combat or do something strenuous.  If you fail, you are Befuddled for d8 Markovian \\
    4 &  The wound will not heal properly; rather than closing, small bunches of fleshy tendrils emerge from the cloven flesh, like the fingers of babies.  You are unable to restore Grit \\
    5 &  Thick black tears leak from your eyes, clouding your vision, and you find that after you have wiped them away, when your fingers are stained black with oil, your eyelids cling together every time you blink, your hands stiffen, like fingertrap lockjaw.  You are permanently Blind within Days.  \\
    6 &  The skin around the wound hardens and crusts in blackening shards like a burning tree, then begins its creeping spread. You have a Soak of 1 for two Sessions - after that, your joints begin to stiffen, walking becomes a chore, you'd rather lay down in the dirt, bury your fingers and breathe in the muck. Every Session afterwards your \MD drops \DCDOWN.  If your \MD becomes exhausted, you become a tree.  \\
    7 &  Your organs grind and groan like a wounded animal. You spend every Bivouac in agony while you pass a grotesque opalescent kidney stone. You are unable to heal Grit during this time.  A Philosopher could use this stone as a spell component.  \\
    8 &  Every Combat, \RS on a d10.  On a Failure you disgorge a surging mass of green bile that continues to bubble and churn after it has left your throat.  This incapacitates you for the rest of the fight.  \\
    9 &  Gob Rot. Your gums fester and peel back, you swallow parts of your tongue as it begins to putrefy, teeth drool out of your mouth while you speak.  After 4 Sessions, you can no longer speak.  \\
    10 &  Swollen boils sprout from your skin, oddly puckered like an anus. After the 3rd Session, the next time you are amongst a large group of people they unfurl like glistening mucus-coated blossoms of skin, violently jettisoning flesh spores into the air.  Everyone Close to you is automatically infected with the disease (no Save).  The explosion doesn't kill you - the cycle now repeats itself \\
    11 &  Fibrous purple fronds curl out from your skin, interwoven and fragile, ever-growing. It would be beautiful if they weren't siphoning off your blood supply.  At the start of the next Session, lose 1 \MAX Flesh.  At the start of the second Session lost 2 \MAX Flesh, etc.   \\
  }

   \mytable{l X} {  
  } { 
    12 &  The flesh around the wound becomes spongy, pliant, it exudes the scent of fuchsia. Synaesthesia ravages your psyche, and pulling away clumps of your deteriorating body makes the most deliriously beautiful music.  You are overcome and essentially Paralyzed (your friends can carry you).  If you are not cured within 2 Sessions, the effect is permanent.  \\
    13 &  Your flesh sloughs, a bicep one moment and a sack of atrophied muscle hanging from bone in a skin bag the next. But that's not what bothers you, it's when it comes back. Creeping up the bone, tendons attaching, muscle re-adhering, the sucking sounds within your skin. It never rebuilds the same way and your skin is starting to smell of rot.  Happens once every Session; whenever it happens, your \MAX \VIG moves \DCDOWN.  If you ever exhaust your \VIG, you die.  \\
    14 &  Your skin is pocked with holes like the back of a pregnant frog. Fleshy nodules emerge to squirt thin streams of noxious green fluid before retreating back inside your skin. It isn't an infestation, it is your own flesh, and it is growing larger.  After 3 Sessions, you explode in a massive blast of acidic green bile. Everyone Close to you is automatically infected with the disease (no Save).  The explosion kills you.  \\
    15 &  Resinous Influenza. It's not the bleary leaking eyes that bother you, nor the deep-bone ache or even the delirious shakes. It's the absurd amount of mucus that you expel every time you sneeze and the fact that it sets like resin almost as soon as it touches your exposed skin. Your face begins to look like a grotesque melted mask and that is not a good look for anyone.  You can't chip the mucous off.  You begin asphyxiating in your own mucous.  After 2 Sessions you will start having difficulty breathing; after 4 Sessions, you suffocate. \\
    16 &  Polychromous Decay. It starts with a dry itch, dustings of dead flakes falling from your skin as you scratch like chronic dandruff, turning strangely polychromatic as it settles. After Hours the disease makes its way into your flesh, and your skin has almost entirely itched away and you're scratching canals into the muscle beneath. It doesn't even look like flesh and blood anymore, just polychromatic granularity like a bathbomb.  After 2 Sessions your hands have been ground away so you rub your itching limbs together as best you can, grinding biceps over your torso, crushing your chin against your chest.  Finally, after 4 Sessions, without anything left to scratch it with, you find that your flesh slowly regrows, but the moment your limbs build back into moveable stumps... The Polychromous Decay is a powerful spell component and many of those who contract its disease end up as limbless torsos in a Philosopher's basement, unable to scream through dust-filled lungs, forever regenerating porous dusty flesh only to have it scraped away.  \\

}


\newpage


\mysubsection{Grimoire Traps}{grimoire-traps}

Roll once for each \mylink{Wizard's Sigil}{research-sigil-wizard} you fail to disarm.  

\myital{Once again, thanks be to Logan Knight for \href{https://www.lastgaspgrimoire.com/cunning-linguists/}{Cunning Linguists?}}


  \mytable{l X} {  
  } {
    1 &  You birth a wriggling pink rat with a young version of your own face out of your mouth. It scrambles away and out of sight. It will grow to about the size of a pug, it develops translucent flaps of skin to glide on, it keeps showing up to foil your plans. \\
    2 &  Tiny hideous mouths split open over the surface of the object and begin to scream and never stop. \\
    3 &  Cold pink mist swells up from the object and wafts out Nearby, Save or lie down to sleep in a blanket of fog for Years (unless slapped awake). \\
    4 &  The object bearing the writing bursts into flame like a pile of magnesium. \\
    5 &  Heat emanates from the page and you absent-mindedly place your hand against it to feel the warmth. The ink burns into your skin like a tattoo. The first lie you tell will become true, and the writing on your hand will change to remind you of that for all time. \\
    6 &  The book's cover grows course and hairy, legs sprout from the spine and it leaps from your hands, running across the room and up the wall. It points a strange cloaca at you from the base of its spine and expels clumps of bright green mildew at you that burns the skin, flapping away to the other side of the room if you get too close. \\
    7 &  The edges of the book slice your fingers open before it drops to the floor, leaving tiny rows of perfect bloodless papercuts. They will never heal, and from this moment forth you will bleed prose. It is not for me to know what secrets may be found in your blood. \\
    8 &  Tendrils snap out from the crease of the book, penetrating your chest and belly, churning as some drain and others pump. Your organs liquefy and drain out with your blood, and in its place your body fills with fluid like liquid golden light. You glow like a pinkish-gold beacon, and take a -3 penalty to your Save vs. Doom, but you are immune to Toxins and gain 1 Blood Die. \\
    9 &  Violet light flashes from the pages, in your temporary blindness you can hear the resonance of your own thoughts. When you look back at the book you are staring at your own placid face, when you cry out it is the face in the book that opens its mouth and screams, not the featureless mess of words plastered around your swollen eyes. \\
    10 &  The pages of the book begin to flip back, growing faster, pulling at the air around you, the flurry of paper flipping between the covers of the book consists of more pages than the book could possibly have contained. The pull at the air around you grows stronger, small objects begin to lift from the floor and disappear between  the pages, your feet begin to shift.. \\
    11 &  Bronze threads burst from the walls, roof, even the object, and sew into your flesh. If you move more than a few inches parts of your body start to tear away. If anyone touches you or the threads, even more threads appear to knit them in place. \\
    12 &  The words seem to drive themselves through your pupils, expanding from within and showering your companions with optic fluid, in place of your eyes remain two rolling black orbs, words and phrases wafting from them like smoke. Somehow you remain able to see, and much hidden knowledge can be learned by anyone studying your eyes. However, if you spend time looking at your own reflection you must roll your Sanity every Minute.  \\
  }

  \mytable{l X} {  
  } {
    13 &  Even if you never glimpse your reflection, there is a 5\% chance every week that the words of the orb will waft back into your brain, subtly changing who you are. Roll on a personality or character quirk table. \\
    14 &  Vines emerge from the surface of the object, growing lush and dense as leaves and fleshy flowers sprout from them. There are enough vines to fill a 10m room, and the flowers bloom to reveal a glistening red interior filled with shivering barbs. Anyone shot by the barbs immediately is immediately Befuddled (Save to resist) for d20 Markovian. \\
    15 &  Shadows thicken behind you, whispering as they gain density, reaching out, grasping at your heels. The room swells with vicious shadow, breathing limbs reach into your body and twist your veins, the door is shut and covered in a thick layer of quiet loathing. \\
    16 &  Fragrant mud pools within the letters and begins to spill down the object, crabs with voices like angels emerge from the pooled muck and beseech to be allowed within you. They're actually quite persuading. Save or allow the angelcrabs inside your mouth, and eyes, and various other orifices. They eat their fill and excrete muddy gold in their wake to excavate a home, causing d12 damage directly to Flesh. If you survive the experience the angelcrabs will live in symbiotic harmony within your body, imparting alien wisdom when they deem it appropriate. \\
    17 &  Beads of amber sweat begin to swell and glisten over the object's surface, it begins to look more pliant, more organic, its bulk starts to heave in laboured breaths, sections split away in mockery of limbs, pools of flesh swirl inwards forming gaping circular mouths, their inner surface full of quivering jelly-like teeth. The hunt begins. \\
    18 &  The words on the page begin to quiver, the ink contracts and swells and forms drops of dark rain which fall up from the book. Soon the paper itself is raining away, while the book's cover becomes ever more heavy in your hands. After the rain the inner cover clears to reveal a glimmering night sky, full of constellations you've never known. They swirl and dance and you step into the vastness of their glory, held by their cosmic light in an eternity of tormenting discovery. The rain falls back down in a torrent, replacing pages and letters and phrases until the book slams shut. If the book is opened you will return, but you will not return the same as you once were. Save or gain insanities equal to your failure, save vs. Poison or gain mutations equal to your failure. Regardless of your saves, you do not return alone, the star spawn's seed rests in your belly and in your mind, waiting. \\
    19 &  The words snake off of the page and across your skin, circling around your limbs and across your chest until your entire body bears the contents of the book. You fall to the floor in agony as the tiny circlets of writing brand into your flesh. The deathless librarians of the Mausoleum de Lettres cannot help but seek and catalogue the Living Word, and they always know when a new one has been created. \\
    20 &  After you shut the book, the cover creaks back open and oily dripping creatures begin to pull themselves from a portal within. Their form is myriad and shifting, they merge and split and far-off tittering fills the air. To close the portal you have only to shut the book again, but the floor is crawling with flesh like oil.
  }

 \newpage

  
  \mysection{Appendix B}{appendix-b}

  \mysubsection{Random Spell Tables}{table-random-spells}

  \small

  \mytable{l X l X} {
    \thead{d50}  & \thead{Spell} & \thead{d50}  & \thead{Spell} \\
  }{
    1 &  \mylink{Acid Arrow}{wizardry-acid-arrow} &
    26 &  \mylink{Knife Trick}{wizardry-knife-trick} \\
    2 &  \mylink{Arcadia's Bulwark}{wizardry-arcadias-bulwark}  &
    27 &  \mylink{Knock}{wizardry-knock} \\
    3 &  \mylink{Balthazar's Breathtaking Blast}{wizardry-balthazars-breathtaking-blast}  &
    28 &  \mylink{Levitating Disc}{wizardry-levitating-disc} \\
    4 &  \mylink{Bastogne's Glamping Charm}{wizardry-bastognes-glamping-charm}  &
    29 &  \mylink{Lipby Chonk's Viscous Form}{wizardry-lipby-chonks-viscous-form} \\
    5 &  \mylink{Battering Beam}{wizardry-battering-beam}  &
    30 &  \mylink{Lock}{wizardry-lock} \\
    6 &  \mylink{Cacaphony}{wizardry-cacaphony}  &
    31 &  \mylink{Meat Shield}{wizardry-meat-shield} \\
    7 &  \mylink{Charm}{wizardry-charm}  &
    32 &  \mylink{Mighty Lungs}{wizardry-mighty-lungs} \\
    8 &  \mylink{Color Spray}{wizardry-color-spray}  &
    33 &  \mylink{Mirror Image}{wizardry-mirror-image} \\
    9 &  \mylink{Commanding Presence}{wizardry-commanding-presence}  &
    34 &  \mylink{Morass}{wizardry-morass} \\
    10 &  \mylink{Ego Weapon}{wizardry-ego-weapon}  &
    35 &  \mylink{Negasonic Bomb}{wizardry-negasonic-bomb} \\
    11 &  \mylink{Enervate}{wizardry-enervate}  &
    36 &  \mylink{Prismatic Ray}{wizardry-prismatic-ray} \\
    12 &  \mylink{Fireball}{wizardry-fireball}  &
    37 &  \mylink{Pritchard's Gusty Belch}{wizardry-pritchards-gusty-belch} \\
    13 &  \mylink{Fogbank}{wizardry-fogbank}  &
    38 &  \mylink{Protection from Element}{wizardry-protection-from-element} \\
    14 &  \mylink{Fool's Fire}{wizardry-fools-fire}  &
    39 &  \mylink{Rhea's Efficacious Plow}{wizardry-rheas-efficacious-plow} \\
    15 &  \mylink{Greaseball}{wizardry-greaseball}  &
    40 &  \mylink{Sandstorm}{wizardry-sandstorm} \\
    16 &  \mylink{Grimm's Electric Fingers}{wizardry-grimms-electric-fingers}  &
    41 &  \mylink{Sanguine Mail}{wizardry-sanguine-mail} \\
    17 &  \mylink{Hammerspace Mule}{wizardry-hammerspace-mule}  &
    42 &  \mylink{Scuttle}{wizardry-scuttle} \\
    18 &  \mylink{Helping Hand}{wizardry-helping-hand}  &
    43 &  \mylink{Scything Disc of Nog}{wizardry-scything-disc-of-nog} \\
    19 &  \mylink{Heroic Leap}{wizardry-heroic-leap}  &
    44 &  \mylink{Sleep}{wizardry-sleep} \\
    20 &  \mylink{Hollow Head}{wizardry-hollow-head}  &
    45 &  \mylink{Summon Candles}{wizardry-summon-candles} \\
    21 &  \mylink{Ice Bridge Step}{wizardry-ice-bridge-step}  &
    46 &  \mylink{Suspend Objects}{wizardry-suspend-objects} \\
    22 &  \mylink{Icebolt}{wizardry-icebolt}  &
    47 &  \mylink{Tempestuous Chariot}{wizardry-tempestuous-chariot} \\
    23 &  \mylink{Illusion}{wizardry-illusion}  &
    48 &  \mylink{Vertigo}{wizardry-vertigo} \\
    24 &  \mylink{Invisibility}{wizardry-invisibility}  &
    49 &  \mylink{Web}{wizardry-web} \\
    25 &  \mylink{Kelsier's Swarm of Irritating Vermin}{wizardry-kelsiers-swarm-of-irritating-vermin}  &
    50 &  \mylink{Whirling Blades}{wizardry-whirling-blades} \\    
  }

\begin{multicols}{2}

\mybold{BIOMANCY}
\mynumlist {
    \item \mylink{Balthazar's Breathtaking Blast}{wizardry-balthazars-breathtaking-blast}

    \item \mylink{Helping Hand}{wizardry-helping-hand}

    \item \mylink{Heroic Leap}{wizardry-heroic-leap}

    \item \mylink{Hollow Head}{wizardry-hollow-head}

    \item \mylink{Lipby Chonk's Viscous Form}{wizardry-lipby-chonks-viscous-form}

    \item \mylink{Meat Shield}{wizardry-meat-shield}

    \item \mylink{Mighty Lungs}{wizardry-mighty-lungs}

    \item \mylink{Pritchard's Gusty Belch}{wizardry-pritchards-gusty-belch}

    \item \mylink{Sanguine Mail}{wizardry-sanguine-mail}

    \item \mylink{Scuttle}{wizardry-scuttle}
}

\cbreak

\mybold{ELEMENTS}
\mynumlist {
    \item \mylink{Acid Arrow}{wizardry-acid-arrow}

    \item \mylink{Fireball}{wizardry-fireball}

    \item \mylink{Fogbank}{wizardry-fogbank}

    \item \mylink{Grimm's Electric Fingers}{wizardry-grimms-electric-fingers}

    \item \mylink{Ice Bridge Step}{wizardry-ice-bridge-step}

    \item \mylink{Icebolt}{wizardry-icebolt}

    \item \mylink{Morass}{wizardry-morass}

    \item \mylink{Protection from Element}{wizardry-protection-from-element}

    \item \mylink{Sandstorm}{wizardry-sandstorm}

    \item \mylink{Tempestuous Chariot}{wizardry-tempestuous-chariot}
}

\newpage

\mybold{ENTROPY} \\

\mynumlist {
    \item \mylink{Cacaphony}{wizardry-cacaphony}

    \item \mylink{Enervate}{wizardry-enervate}

    \item \mylink{Fool's Fire}{wizardry-fools-fire}

    \item \mylink{Greaseball}{wizardry-greaseball}

    \item \mylink{Invisibility}{wizardry-invisibility}

    \item \mylink{Knock}{wizardry-knock}

    \item \mylink{Mirror Image}{wizardry-mirror-image}

    \item \mylink{Prismatic Ray}{wizardry-prismatic-ray}

    \item \mylink{Web}{wizardry-web}

    \item \mylink{Whirling Blades}{wizardry-whirling-blades}
}

\mybold{FORCE} \\
\mynumlist {
    \item \mylink{Bastogne's Glamping Charm}{wizardry-bastognes-glamping-charm}

    \item \mylink{Battering Beam}{wizardry-battering-beam}

    \item \mylink{Hammerspace Mule}{wizardry-hammerspace-mule}

    \item \mylink{Kelsier's Swarm of Irritating Vermin}{wizardry-kelsiers-swarm-of-irritating-vermin}

    \item \mylink{Knife Trick}{wizardry-knife-trick}

    \item \mylink{Levitating Disc}{wizardry-levitating-disc}

    \item \mylink{Rhea's Efficacious Plow}{wizardry-rheas-efficacious-plow}

    \item \mylink{Scything Disc of Nog}{wizardry-scything-disc-of-nog}

    \item \mylink{Summon Candles}{wizardry-summon-candles}

    \item \mylink{Suspend Objects}{wizardry-suspend-objects}
}

\mybold{MIND} \\
\mynumlist {

    \item \mylink{Arcadia's Bulwark}{wizardry-arcadias-bulwark}

    \item \mylink{Charm}{wizardry-charm}

    \item \mylink{Color Spray}{wizardry-color-spray}

    \item \mylink{Commanding Presence}{wizardry-commanding-presence}

    \item \mylink{Ego Weapon}{wizardry-ego-weapon}

    \item \mylink{Illusion}{wizardry-illusion}

    \item \mylink{Lock}{wizardry-lock}

    \item \mylink{Negasonic Bomb}{wizardry-negasonic-bomb}

    \item \mylink{Sleep}{wizardry-sleep}

    \item \mylink{Vertigo}{wizardry-vertigo}
}  

\end{multicols}
} %end
