% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons
% Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggMarvels}{%
  \mychapter{Marvels}{marvels}
}

\renewcommand{\yggMarvelsText}{%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% MIRACLE WORKING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\mysection{Miracle Working}{marvels-miracle-working}

\mybold{Use Faith Dice to perform Miracles.  No Miracles can take place on Unhallowed Earth}



\mysubsection{Ambrosia}{miracle-ambrosia}

You can create \DICE d4 \UD of Provisions.  These \UD can be combined into a single \UD (so 3 d4 \UD could be combined into a \UD of d12) up to a d24 \UD.  These Provisions can be stored for use later, but it also particularly nourishes the faithful.  During the working of the Miracle, up to \DICE Disciples of the Small God can partake of the Ambrosia and gain +1 Faith Die (the miracle worker cannot gain this benefit). Disciples partaking of the meal do not affect the \UD produced in any way.

\mysubsection{Covenant}{miracle-covenant}


The Mystic seals a bargain between themselves (referred to as the Suzerain) and another (referred to as the Vassal) by awarding temporary control over both of their *noumenon* to their Small God (this means that Fae cannot be held to a Covenant).  Free assent is required, but it can be compelled by other factors (like a dagger to the throat or other threats).

The Suzerain must use a number of \DICE equal to the \LVL of the Vassal, and this Miracle must take place in a shrine of their Small God.  Once complete:

\mylist { 
  \item The Suzerain can give Faith and take Faith from the Vassal, as if they were a Disciple
\item The Suzerain always knows where the Vassal is and (roughly) what they're generally feeling - strong emotions (lust, hatred, etc) or  physical extremes ("he's somewhere very, very cold")
\item The Suzerain is completely unable to harm the Vassal (though they can command others to do so); the Vassal does not have the same constraint.
\item The Vassal is immediately converted to the worship of the Small God
\item The Vassal barely needs sleep, and eats and drinks sparingly (roll Provisions \UD twice and take the higher roll).
\item The Vassal is affected as if they were under the effects of Tongues of Fire at all times
\item The Vassal gains +\SUMDICE points of "holy armor".  Damage is subtracted from this total first before it is applied to Armor, Grit, etc.  It can't be healed, but it is restored if the Vassal is able to visit a Shrine to their Small God during a Sojourn or Sabbatical.  
}

There can only be a single Covenant between the Suzerain and the Vassal - neither is allowed to strike a Covenant with anyone else while the Covenant is in effect.  The Covenant can only broken by: the Suzerain or the Vassal suffering a Crisis of Faith; the Suzerain and the Vassal agreeing to end the Covenant (both must agree); or the death of the Suzerain or the Vassal.



\mysubsection{Crusade}{miracle-crusade}

Can be performed by a Suzerain on their Vassal (see Covenant).  By invoking the Crusade, the Suzerain transforms the Vassal into a Paladin of the Faith.  

The Suzerain must use a number of \DICE equal to the \LVL of the Vassal, and this Miracle must take place in a shrine of the Small God.  In addition to the abilities they had before, Paladins can use Faith Die given to them by their Suzerain as Deed Dice in the same way as Sellswords (if the Paladin is a Sellsword, these Deed Dice are in addition to their regular Deed Dice, and can be rolled separately).  The Paladin is also capable of gaining Faith themselves, separately from their Suzerain.  Finally, the Paladin may cast any of the Seven Sacraments using their Faith Dice

This power does not come without cost.  The Suzerain must name a Crusade important to the Small God they worship: "wipe out the infidels of the Crawling Chaos", for example, or "bring the fingerbone of St. Sebastien to the reliquary in the Howling Wastes".  Similar to a Geas, any day not spent in the furtherance of the cause of the Crusade will lose the Paladin a single Faith die.  Note that if the Paladin should lose all their Faith and suffer a Crisis of Faith, the Crusade has failed, and the Covenant is broken.

\mysubsection{Golem}{miracle-golem}

A golem is a mortal-like figure, brought to life through magic.  Creating a golem requires gold for materials and effort, as well as a certain number of Ritual dice:

\mytable{X c c} {
  \thead{Type} & \thead{\COST} & \thead{Ritual Dice} \\
} {
  Paper  & 100au  & 10 \\
  Glass  & 500au  & 12 \\
  Wood  & 1,000au  & 14 \\
  Clay  & 5,000au  & 16 \\
}



Golems requires a *shem* - a slip of paper with a magical rune written on it through the miracle of the Holy Writ.

Golems are completely obedient to their Maker and respectful of any other follower of the Small God.  Presenting a holy symbol is enough to keep a Golem at bay, but only their Maker can give them commands.  If their Maker should perish, the golem will continue on in perpetuity, doing the last task given to it by its Maker.

\mybold{Golems are immune to magic of any kind - including being struck by magical weapons.}

\myhighlight{Paper Golem}{miracle-paper-golem}

Paper golems are small (less than 100cm tall) creatures created for menial work to fetch and carry for their Maker.  They can carry a single Significant Item provided it doesn't weight more than 5kg (or a number of Insignificant Items up to 5kg).  Paper golems can "fly" on gusts of wind (similar to how a chicken can "fly") and walk and run as fast as a small child.  Paper golems record everything they see.  At any time, their Maker can ask them a single question ("what was it you saw when you were in the Baron's chamber?", for example) and the golem will flatten itself into a scroll upon which is written what it "saw" (the Golem remains a scroll forever more, with the symbol of the Small God embossed on the bottom of the scroll.  These embossed scrolls are very, very difficult to counterfeit, and if you were to do so and get caught, it would bring about the wrath of the church of the Small God). 

Paper Golems are immediately destroyed by (non-magical) fire

\myhighlight{Glass Golem}{miracle-glass-golem}

Glass golems are mortal sized (2m tall) automatons filled with pungeant herbs and combustibles called "smokes".  The type of smoke is determined at the moment of their creation by their Maker. Glass golems immediately explode when dealt a forcible blow - a hit with a weapon, a fall from a height greater than 3m, etc.  The effect of exploding a Glass Golem deals d6 damage to everything Nearby (Save negates) as well as the following effects:

1. Smoke of Lies:  every creature Nearby is Befuddled and Enraged (1-3 on a d6) or Afraid (4-6 on a d6), unless they make a Save
2. Smoke of Heroes:  every creature Nearby receives a Blessing, and are immune to fear of any kind - but they cannot retreat.  Unwilling recipients get a Save
3. Smoke of the Holy: creates Hallowed ground everywhere Close to the point of explosion, or automatically dispels Unhallowed Earth somewhere Close.  Unhallowed creatures are thrown 10m Nearby (treat as Falling Damage).
4. Smoke of Medicines: every creature Nearby heals to their full Flesh, and restores 3d6 Grit up to their Max.

the smoke persists for Minutes, but can be dispersed by wind.  The Maker is not limited to these options; they should discuss with the Arbiter if they wish to go a different way.



\myhighlight{Wood Golem}{miracle-wood-golem}

Wood golems are large (3m tall) docile, hulking, tree-like creatures possessing great strength. They are able to carry up to 50 Significant Items in their branches, weighing up to 1,000kg total.  They can successfully break down non-magical doors, bend iron bars, and perform other feats of strength on a 4-in-6 (this number can be adjusted at the Arbiter's discretion).  They walk at a slow, shuffling gate (d4 \MD)

Wood golems will never attempt to defend themselves.  They can take up to 50 points of damage - Chopping weapons deal double-damage, and fire deals triple-damage.  They will glad and mindlessly stand wherever their Maker demands: in front of a doorway, in the middle of a fire, or charging dumbly into a group of Monsters.

\myhighlight{Clay Golem}{miracle-clay-golem}
Clay golems are giant (4m tall) faceless creatures created to protect or guard an area.  They must be told what they must guard at the moment of their creation, and they cannot stray further than 100m from that spot.  The spot they guard must be Hallowed, and if this ever ceases to be they will immediately crumble to dust.

Clay golems house the *noumenon* of a Vassal or Paladin of their Maker (see \mylink{Covenant}{miracle-covenant}) and \mylink{Crusade}{miracle-crusade}.  The Vassal or Paladin is ritually slain, and their blood given to the Maker, who combines it with sacred earth and fire to create the clay giant (the Vassal or Paladin does not need to be a willing sacrifice, though remember Mystics cannot directly harm their Vassals).  The golem has all of the memories, skills, saves, and abilities of their Mortal form (including Deed Dice, spell casting, etc.) and Grit, Flesh, etc.  They have a Soak: 2 and do 2d8 damage (2 Close).  They are immune to spells of the Mind paradigm, backstab, surprise, and toxins. They cannot speak and are unswervingly obedient to their Master.

Clay golems can be bestowed with the spirits of willing heroes (paladins who wish to protect the temple forever) or with those of unwilling enemies (forced to guard a forgotten hallway, or the temple of a heretic Small God).  When slain, the *noumenon* of the deceased do not travel to the Isle of the Dead.  None know what happens to their souls. 


\mysubsection{Hallowed Ground}{miracle-hallowed-ground}

The miracle is used to permanently consecrate Unhallowed Earth (see the Occult ritual for details), or to permanently create Hallowed ground for performing miracles.  The range is a circle \DICE meters in radius.  In order to consecrate Unhallowed Earth, this radius must equal or exceed the Unhallowed Earth the Mystic is trying to consecrate.  The ground to be consecrated must be within \DICE km of the Mystic.



Hallowed Ground has the following effects:

\mylist {
\item no Fae or Unhallowed creature may enter Hallowed Ground without making a Save.
\item any Mortal inside the radius of the Hallowed Ground can make a Save to end a Markovian effect (in addition to rolling the Markovian die)
\item any Mystics on Hallowed Ground may ignore the negative effect of a Failure when using  their Grace (that is, they may keep their Grace die even if they roll a 1 or a 2).
}

This Ritual is the only one that does *not* require Hallowed Ground to perform.


\mysubsection{Holy Relic}{miracle-holy-relic}

A repository for Faith.  By creating a Holy Relic with \DICE Ritual dice, you can place up to \DICE Faith dice into the relic.  You must place this Faith into the relic at the time of its creation.  This Faith can be used by other Mystics of your Small God (as well as yourself).  The relic itself must be something "special" - a fingerbone of a Saint, a shroud, etc.  (Arbiter's discretion).  The more powerful the relic, the more Faith can be placed inside of it.

The Miracle of the Holy Relic is used to create \mylink{Holy Symbols}{mystic-holy-symbol}.  The symbol must be what is indicated under your Small God.  A Holy Symbol only requires a single Ritual \DICE


\mysubsection{Holy Water}{miracle-holy-water}

You can create \DICE d4 \UD of Holy Water.  These \UD can be combined into a single \UD (so 3 d4 \UD could be combined into a \UD of d12) up to a d24 \UD.  For each Faith Die spent, you must spend an additional 25 coins in materials.

\mysubsection{Holy Writ}{miracle-holy-writ}

The word and the law of your Small God, written as seven sacred words known only to the faithful.  Only you and other members of your faith can see the words; to others, they look like random squiggles, strange designs, or "primitive" carvings.  Contained in the seven words is the performer of the Miracle, but you will need to make a successful Skill: Lore check to identify them unless you know them personally.   The Holy Writ only requires a single Faith.



\mysubsection{Incorruptibility}{miracle-incorruptibility}

Can only be performed on a corpse / someone who is already dead.  Incorruptibility stops a body from rotting.  The length of time depends on the number of Faith dice invested:  1 [die]: \SUMDICE Days; 2-5 \DICE: \SUMDICE Weeks; 6-9 \DICE: \SUMDICE Years; 10+ dice: \SUMDICE Centuries.  So long as the body remains on Hallowed ground, it does not decay in any way and cannot be targeted with any spells from the Necromancy paradigm.  If the body is removed from Hallowed ground, it will begin to decay as normal.

\mysubsection{Proselytize}{miracle-proselytize}

By invoking Proselytize, you can attempt to convert others to the faith of your Small God, or give willing congregants instruction in the ways of your religion.  

You can distribute no more than 1 of your Faith die to as many Mortals as you choose, provided they are not Mystics who follow a different Small God.  For each Mortal you transfer this Faith to, you must spend 1 Ritual die.

The effects vary depending on whether the congregant is willing, apathetic, or unwilling

\mylist {

\item Willing:  you give one of your Faith Die to the worshiper
\item Apathetic:  roll the Ritual Die; on a failure, the die is lost.  On success you have converted them - instead of giving your Faith Die to them, they gain one of their own
\item Unwilling:  the congregant gets a Save.  If they succeed, you lose 2 Faith Die (the original you tried to give them, plus one other).  If they fail, roll as "Apathetic" above - if you succeed in converting them, you gain +1 Faith
}

Worshipers who have a Faith Die from you become your Disciple (see the Core Rules for details).

\mysubsection{Sacred Mass}{miracle-sacred-mass}

You can perform a sacred ceremony for \SUMDICE others (excluding yourself).  Non-Mystics who indulge in a Sacred Mass are Blessed for the next Session.  If you are a Mysic of a different Small God then the miracle worker and partake in the Mass, you lose 2 Faith Die.  If you are the miracle worker, or a Mystic of the same Small God, you gain 1 Faith Die for every 10 people participating up to your \LVL.




\mysubsection{Sin Eating}{miracle-sin-eating}

You can heal up to \DICE Spirit Wounds on yourself or others Nearby.



\mysubsection{Tongues of Fire}{miracle-tongues-of-fire}

Up to \SUMDICE people other than the Miracle Worker are affected.  Recipients of Tongues of Fire can speak (but not read) any Language they choose at will, and can command a single creature once per Session (see below).  The recipient can never lie while under the effects of Tongues of Flame.  Unwilling creatures get a Save.  This miracle lasts only for the Session (unless provided by Covenant)



\LITURGY [
  Name= Command,
  Link=miracle-command,
  Paradigm=Mind,
  Save=Y,
  Duration=0 ,
  Counter= n/a  ,
  Keywords=None ,
  Target=Nearby creature
]

You shout a \DICE word command to the target, who must then carry it out if the fail a Save.  If the command would last more than a single Moment, the target gets a new Save at the beginning of each Moment.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% OCCULTISM
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\mysection{Occultism}{marvels-occultism}

Occultism require a certain number of successes using Cunning Dice as specified in the section on Cunning at the start of the section on Witches.  If "Widdershins" is indicated, this is the number of times you must traverse the Wheel if you fail the Occultism before you can try it again.

\OCCULT[
  Name=Barghest,
  Link=occultism-barghest,
  Success=4,
  Cost=See below,
  Widdershins=1
]

Through this ritual, the Witch summons a spectral black dog (a harbinger of death and misfortune) to torment a single foe for \LVL days.  The Witch must whisper the birth name of the victim to the spectre; upon hearing it, the black dog will seek the victim out, traveling up to \LVL x100km a night to find them.  The barghest can only travel at night, and disappears at the first light of the rising sun.  The dog can see invisible or hidden creatures and will unerringly find the target provided they are within distance of the casting of the ritual.

Once found, the barghest will appear to the victim once every night for the duration of the spell.  The victim is permitted a Save when they encounter the barghest - failure means they will suffer the curse of the barghest until sundown the following day, when (if within the duration) the dog will appear again (prompting another Save).  If the victim is in the presence of a Pooka when they encounter the barghest, they are permitted two Saves against the effect.

If the Save is failed, the victim suffers the following maledictions:
- they will fail every Luck check they attempt
- they will be unable to heal Grit from resting
- all of their \RO and \RB attempts are at \DCDOWN
- when rolling their Death Die, they must roll it twice

The ritual requires a dog (your familiar is fine) and an item belonging to the victim.  No harm comes to the dog, but the spectral figure will resemble them if examined closely


\OCCULT[
  Name=Bind Familiar,
  Link=occultism-bind-familiar,
  Success=1,
  Cost=666,
  Widdershins=1
]


A familiar is a supernatural creature that helps you practice magic.  Familiars can be summoned and dismissed at will: they'll appear from a shadow (cat) or sewer grate (rat) or fly in through a window (raven), and they'll leave roughly the same way.  Familiars are Unhallowed.

A familiar earns you an extra Cunning Die at the start of any Sabbatical.  The can be sent on missions up to \LVL km away.  You can see what they see as if you were gazing through their eyes for as long as you Concentrate. You also can remember things your familiar remembers (so you could send them on a spying mission and later "remember" what they saw). You can cast any Charm through your familiar, though you still have to roll your Mojo when you do.  

If your familiar is Close or Nearby, you can communicate verbally with them, though you cannot use words greater than 1 syllable.  You communicate in a language all your own that no one else understands.  They can follow simple instructions ("get the key on the desk", "chew through these ropes", "spy on that man") but not more complex ones ("pick the lock").  Your familiar can't talk.

Familiars have a Health equal to your Flesh.  They can only be shielded by your Mojo in the same way as Armor, but you can roll your Mojo as many times as you want (while you have it, anyway) to protect them.  If they're attacked and they survive, they immediately dismiss themselves and won't return for the rest of the Session. If your Familiar dies, you must travel Widdershins before you can summon another.  

Familiars are themselves immune to spells from the Mind paradigm, but if a Mind spell is cast on them you need to Save or be affected as if the spell targeted you.

Finally,  you can place a Malison on your familiar (see the ritual below).  In the event of your death, the familiar will stay with your body until someone attempts to disturb your corpse.  At that point, it will deliver the malison etched upon its skin, and dismiss itself for good.

When you summon your familiar, roll below (or discuss with the Arbiter if you want to choose), or make something up.  You can only have 1 familiar at a time.



\myhighlight{Familiars}{occultism-familiars}

  \mytable{X c}{
    \thead{d6} & \thead{Familiar}\\
  }{
    1 & Cat \\
    2 & Dog \\
    3 & Rat \\
    4 & Toad \\
    5 & Raven \\
    6 & Exotic (roll below) \\
  }  

  \mytable{l X}{
    \thead{d6} & \thead{Familiar}\\
  }{
    1 & The severed hands of a condemned man  \\
    2 &  A pet rock \\
    3 & A floating Fist-Sized Crystal Tesseract  \\
    4 & A doll made of rags and straw \\
    5 &  Miniature, horribly deformed homunculus resembling you \\
    6 & An intelligent moss \\
  }  

\OCCULT[
  Name=Create Juju,
  Link=occultism-create-juju,
  Success=varies,
  Cost=See below,
  Widdershins=0
]


Juju are minor magical items created by Witches using their Mojo.  The Juju must be placed on an item OK'd by the Arbiter and should be something "special".  For example:
\mybullet {
  \item A carved branch of a tree that only grows in the cold stone ruins of Carcosa
  \item 3 jeweled eggs stolen from a Roc's nest when the Eye of Tartarus is full
  \item The carved fingerbones of St. Sacrastine, which reside in the sacristy of the Temple of Gomorrah in Lakhmar
  \item etc.
}

Juju can do pretty much anything you and the Arbiter agree on, but here are some ground rules for what it \mybold{cannot} do:

\mybullet {
  \item It cannot be used to deal direct damage, or be an item that causes damage directly (knives, swords, etc)
  \item It cannot be used to increase any Tangible Stat, \RS chance, Flesh, or Grit.  Saves, Skills and Intangible Stats are OK
  \item It cannot duplicate the effect of any Wizardry, Liturgy, or Sacrament
  \item It cannot provide more than +2 to a Save, +4 to a \RO or \RS attempt, or x2 \DCUP
}

Each piece of Juju must have a Witch Mark on it for every unique power that it has (at the Arbiter's discretion).

\mybold{Examples}

\mybold{2 Successes; ~500 coins}

\mybullet {

\item \mybold{Coin Beetle:} A normal looking coin. However, at night it comes to life and eats one other coin it can find, before disguising itself as a coin once again.
\item \mybold{Frog Box:} If this box is left open near to a frog it will be compelled to hop in and sit there happily. The frog will stay in the box without needing food, air or water, until instructed to hop out.
\item \mybold{Kingsblood Weed:} Boiling this weed produces tea that will taste delicious to anyone of royal blood but foul to anyone that isn't
\item \mybold{Lucky Rabbit's Foot:}  Gives you a +1 on any Luck Contest \RB you make
}


\mybold{4 Successes; ~1,000 coins}

\mybullet {

\item  \mybold{Dogpack Tooth:} If this tooth is pressed into someone's gums it will take root and allow the owner to speak with dogs and wolves.
\item \mybold{Firey Ring:} If a container of food or liquid is held in the hand bearing this ring it will slowly heat up. Within a minute it will be boiling, but the container will still be safe to hold.
\item \mybold{Magic Mirror:}  When you gaze into this mirror, you can increase your Max Presence \DCUP for the Session
\item \mybold{Cornicello:} Gives you +1 on your Save vs. Doom
}


\mybold{6 Successes; ~5,000 coins}
\mybullet {
\item \mybold{Crystal Ship:} This miniature ship is beautifully crafted and valuable, but if it is ever taken on board a ship that ship will sink before its voyage is completed.
\item \mybold{Money Belt:} Any amount of money may be pressed into a small slot on the front of this belt.  The money enters Hammerspace. The money can be retrieved by tapping it three times and announcing how much is required. This will even cause larger coins to be converted into change for specific amounts.
\item \mybold{Logic Cube:} A cube of interlocking cubes that, when played with for Minutes, gives you inhuman clarity. You only fail Sanity checks on a 1 for the rest of the Session
\item \mybold{Bezoar Necklace:}  When worn around the throat, grants +2 to Saves vs. Toxin.
\item \mybold{Phylactery:} A receptacle appropriate for the ritual of Lichdom
}

\mybold{8 Successes; ~10,000 coins}
\mybullet {
\item \mybold{Ether Flute:} Playing this flute causes any Incorporeal Monster to freeze, mesmerised, so long as the user continues to play.
\item \mybold{Golden Mule:} A tiny golden statue of a mule. Anyone carrying this doubles the number of Significant Items they can carry
\item \mybold{Master's Ring:} This ring causes a faint tingling sensation whenever one of the wearer's employees, servants or hirelings is planning to betray them in some way.
\item \mybold{The Displacement Doll:} Anyone attempting any Mind spell on the possessor of the Displacement Doll kind will affect only the mind of the doll. If they try to read her mind, they will read the mind of a woman trapped in a dark leather chamber, bouncing around on the body of a giant. If they try to charm her they will successfully charm the doll. 
}

\OCCULT[
  Name=Damning,
  Link=occultism-damning,
  Success=5,
  Cost=6666,
  Widdershins=0
]

When you perform this ritual on a Mortal corpse no more than 7 days dead, you prevent them from departing the Isle of the Dead.  The soul is trapped in Hell permanently (though their spirit can still be lead back to the Mortal plane through \mylink{Katabasis}{occultism-katabasis}.  The corpse is consumed when this ritual is performed.


\OCCULT[
  Name=Descry,
  Link=occultism-descry,
  Success=2,
  Cost=500+,
  Widdershins=0
]

You can see events transpiring within \LVL x100km of you by gazing into a silver bowl, censer, crystal ball, mirror, or other mystical item.  You only need to describe what you want to see and it will appear, but the vision is misty and it's hard to make out details.  You can't see things that you might not normally be able to see, so if you said you wanted to "see the body of Sir Tremalane on the northern battlefield", and the body was invisible, you might only see a bare patch of ground.  

The scrying doesn't have to only show events of the present; you can look up to \LVL centuries into the past.  You'd have to have a rough idea of what you'd want to see - "show me the temples of Syrinx before they were cast down" would work, but "show me the secret entrance to the Caverns of Chaos" wouldn't.  The more detailed the description of what you want to see, the better you see it.

Scrying requires that the silver bowl, censer, crystal ball, etc cost at least 500 coins.  For every additional 500 coins spent, you increase your range by 100km and 100 years.

\OCCULT[
  Name=Devil's Counsel,
  Link=occultism-devils-counsel,
  Success=4,
  Cost=See below,
  Widdershins=2
]

You summon a Fiend to deliver legal advice on your behalf.  The Fiend is a fully trained and highly expert lawyer in every known legal system. The Fiend will serve in a legal capacity only and will do nothing illegal (though there are, of course, "gray" areas). They will never engage in combat of any kind, excepting verbal combat. They will serve as long as they are fed one pint of blood a day and there is legal work to do. Other creatures will react exactly as if a Fiend had suddenly appeared in their midst. However, if they examine their records, they will find the Fiend is a registered member of the bar in that polity and is qualified to represent you and your allies in court. People have been arrested for casting Devil's Counsel, but never convicted

This spell requires two close friends to spill each other's blood upon Unhallowed Earth

\OCCULT[
  Name=Geas,
  Link=occultism-geas,
  Success=9,
  Cost=See below,
  Widdershins=3
]

You ensorcel someone with a Geas, a terrible malison that enforces an inescapable command. The command can be long and difficult, like "kill Razor the Monk" or "complete the sevenfold pilgrimage" or "bring me the Globe of the Wonder-Working King from the hoard of the Caliph Vathek" or "go away". The victim must win a \RB : \FOC contest against you with a -\LVL penalty.  From then on, any day that is not spent fulfilling the Geas will have one of the following effects (roll each day):

\mynumlist {
  \item Inflicted with a Curse (roll on the Curse table, re-roll any duplicates)
  \item Inflicted with a Disease (roll on the Diseases table, re-roll any duplicates)
  \item Inflicted with a Wound (roll on the Wounds table as if the target had survived a brush with Death's Door)
  \item Inflicted with Stat damage (d6, distributed any way the target wishes)
  \item Inability to "heal" in any way - no Blood dice, no Faith, no Grit, no Flesh, no Stat damage can be restored
  \item Roll again - the result of the roll is inflicted on the target's loved one / parent / child / friend / etc. instead.  If the target loves nothing, the Arbiter gets to choose
}

The Geas must be doable, even if it is way above the means and possibility of the victim.  Should it become impossible (following the examples above: if Razor should die in other ways, or one of the Seven Shrines be destroyed, or the Orb suddenly explode and release the 1001 demons bound inside), then the Geas is lifted.  Should you or the victim die, the Geas remains in effect, even if you are brought back from the dead or turned into undead. This spell cannot be cast on someone more than once in their lifetime.

A side effect of the Geas is that the victim can be empowered by the Geas if the Arbiter so desires it (for example, they might see in the dark, breathe water, etc. to help them complete their Geas).

The target of the Geas needs to be conscious and near you when you invoke the ritual.

\OCCULT[
  Name=Haunt,
  Link=occultism-haunt,
  Success=3,
  Cost=666,
  Widdershins=0
]

You summon a number of poltergeists to haunt an Unhallowed place up to \LVL km away.  The poltergeists will do their best to harass and torment any Mortals who enter their domain. They can't talk and are insubstantial, but you can direct them to laugh insanely, become visible as ghostly menaces, howl discordantly, and cause telekinetic mischief, which may include the hurling of heavy or sharp objects.  The degree of the haunting depends on the number of successes rolled, and final decision is up to the Arbiter.

\OCCULT[
  Name=Hekaphage,
  Link=occultism-hekaphage,
  Success=2,
  Cost=varies,
  Widdershins=0
]

You can destroy a curse by feeding it to a Hekaphage, ethereal creatures that eat magic and curses. In addition to the successes, you must also roll on the Breaking Curses table and pay its cost. Once the actions are taken as specified on the result of the roll, the curse is lifted.

\end{multicols}

\OCCULT[
  Name=Katabasis,
  Link=occultism-katabasis,
  Success=9,
  Cost=10000\AU,
  Widdershins=3
]

You open a way to the Isle of the Dead, where the spirits of the Hallowed dad reside for 7 days before they move on to sit at the feet of the Authority (see "Damning" for keeping a spirit longer than 7 days).  The ritual must take place in a room with a single door and no windows that rests on Unhallowed Earth (or is itself Unhallowed).

By combining certain writs, components, offal, and rare ingredients, you produce \LVL draughts of a potent toxin. The toxin must be ingested by willing Mortals and has no effect on unwilling participants, or the Unhallowed.  Those that ingest the poison appear to die as their noumenon steps from their corpses.  They are now the Shikari, Hunters of the Dead

The Shikari have all of their abilities and equipment that they had at the moment they died; additionally, they will find two gold coins in their mouth when they awaken in front of the door in the room. The Shikari cannot see into the Mortal plane or interact with it in any way - there is only the door in front of them, and everything else is nothingness.

Through the door lies the Isle of the Dead.  Going through the door costs nothing, but coming back through the door costs two golden coins - they do not have to be *your* coins, but you have to have two of them.  The Shikari can never be in possession of more than 2 coins at any time.

The Shikari can travel freely through the Isle of the Dead.  They can lead any Soul they find there back to the doorway (a doorway only they can see) and take them back through to the lands of the living.  They have a rough idea of where a particular Soul might be, if the Soul was known to them in the living lands. If a Shikari dies in the Isle of the Dead, their Soul immediately departs to the feet of the Authority, and they are dead forever.  

As stated earlier, in order to pass back through the doorway, you must have two coins in your possession when you exit.  Any spirit you find in the Isle of the Dead has between 0-2 coins in their possession, depending on how they were interred by friends, family, or foes (roll a d6.  1-3: 0 coins, 4-5: 1 coins, 6: 2 coins).  There are many creatures and spirits on the Isle of the Dead (particularly crows and ravens) who try to separate the recently deceased from their coins.

If a Mortal spirit successfully exits the doorway to the Isle of the Dead, and their corpse is within the confines of the room, they may inhabit the body at no penalty (save for the likely loss of Sanity from their journey).  If the corpse is absent, the Mortal will be reincarnated - each of their Tangible Stats moves \DCDOWN (to a minimum of d3), they move to the lowest XP for their level (so if they were Level 7, they would move down to 32,000xp), and their appearance is completely different. 

Any who journey to the Isle of the Dead and return are forever more Unhallowed. 

\newpage

\OCCULT[
  Name=Lichdom,
  Link=occultism-lichdom,
  Success=13,
  Cost=10000\AU,
  Widdershins=5
]

This dangerous and depraved rite binds a Mortal's *noumenon* to a phylactery, allowing them to live on as a lich with life everlasting.  The material components are:

\mylist{

\item a phylactery (see \mylink{Create Juju}{occultism-create-juju})
\item a dagger or knife enchanted with Bleeding (see \mylink{Sword Magic}{spriggan-sword-magic})
}


The instructions are thus:
\mynumlist {
\item The participants must be in a room suitable for the ritual of \mylink{Katabasis}{occultism-katabasis}.
\item The phylactery is given to the Mortal who wishes to become a lich.  The Mortal is then stabbed with the enchanted dagger, and their blood used to wash the relic. 
\item A Leech must use Mend to keep the Mortal alive as long as possible.
\item Once the Mortal dies, the ritual of \mylink{Damning}{occultism-damning} must be performed, which will consume the corpse.
\item The ritual of \mylink{Katabasis}{occultism-katabasis} must then be performed; however, the Witch produces \LVL draughts of poison and  \mybold{no coins}, as the magic used to create the coins must instead be used to profane the phylactery so that it might be carried by the dead who have drunk the poison.  Anyone who wants to come back will need to find some coins on the other side, including 2 for the Mortal attempting to become a Lich
\item Trusted minions must now carry the phylactery into the Isle of the Dead, find the soul of the lich, and coax it into the phylactery.  The *noumenon* of the lich will now be inside of the phylactery forever more.  They cannot die so long as the phylactery remains intact.
}

Once the Shikari and the lich return, the lich is reincarnated in a vessel that is in all ways their original self, with no loss of power or skill, though they will appear cadaverous. Despite this, they now only age 1 year for every 1,000 years that pass; they are immune to iron weapons, toxins, and spells of the Mind paradigm; they may commit as many spells as they desire to be inscribed inside their skulls (making Lich skulls extremely potent magical books in their own right); and they are able to read and speak all languages

\newpage

\begin{multicols}{2}

\OCCULT[
  Name=Malison,
  Link=occultism-malison,
  Success=varies,
  Cost=66,
  Widdershins=0
]

You can invoke one of the curses on the Curse table and place it: 
\mylist {
  \item on a person within \LVL km; 
  \item on an item; or 
  \item on a familiar.  
}

If the curse is chosen randomly, the number of successes is 3. If you want to chose, you'll need 5 successes.

You can break any of your own curses at will. Malisons survive the death of the Witch that casts them.

\OCCULT[
  Name=Stormspeech,  
  Link=occultism-stormspeech,
  Success=5,
  Cost=500+,
  Widdershins=1
]

You can command the weather for the rest of the Session, though only in generalities like summoning powerful winds, occluding the sun with dark storm clouds, or causing a downpour. Messing with the weather will result in threefold retribution as the skies become enraged by mortal interference and reassert dominance in the days to come. Stormspeech can also be used to rain blood, toads, etc.  up to a range is \LVL km.

Stormspeech requires a silver bowl, crystal ball, or mirror costing (at minimum) 500 coins. 

\OCCULT[
  Name=Unhallowed Earth,
  Link=occultism-unhallowed-earth,
  Success=1,
  Cost=66,
  Widdershins=0
]

You can either desecrate Hallowed Ground, or create Unhallowed Earth for the casting of rituals, somewhere within \LVL km of you.  You create / desecrate an area \LVL meters in radius.  If you're attempting to desecrate Hallowed Ground, the radius must be equal to or exceed the area of the Hallowed Ground.

Mortals cannot enter Unhallowed Ground you've created unless you accompany them, or unless they make a Save vs. Hexes.  Fae and other Unhallowed are unaffected.

This ritual is the only one that does \mybold{not} require Unhallowed Earth to perform.


\OCCULT[
  Name=Witch Mark,
  Link=occultism-witch-mark,
  Success=1,
  Cost=66,
  Widdershins=0
]

A personal mark of power placed on any non-living item.  The mark is only visible to other Witches, though it would require a Skill: Lore check to recognize who a mark belongs to, unless you knew them personally.  The mark itself is not magical, but requires the \mylink{Third Eye}{charm-third-eye} to see.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% SWORD MAGIC
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\mysection{Sword Magic}{spriggan-sword-magic}



\flavor{
  As the green flames, stung by her runes, leaped up, and the heat of the fire grew intenser, she stepped backwards further and further, and merely uttered her runes a little louder the further she got from the fire. She bade Alveric pile on logs, dark logs of oak that lay there cumbering the heath; and at once, as he dropped them on, the heat licked them up; and the witch went on pronouncing her louder runes, and the flames danced wild and green; and down in the embers the seventeen, whose paths had once crossed Earth's when they wandered free, knew heat again as great as they had known, even on that desperate ride that had brought them here. And when Alveric could no longer come near the fire, and the witch was some yards from it shouting her runes, the magical flames burned all the ashes away and that portent that flared on the hill as suddenly ceased, leaving only a circle that sullenly glowed on the ground, like the evil pool that glares where thermite has burst. And flat in the glow, all liquid still, lay the sword. \Tilde The King of Elfland's Daughter
}



The Rom who have turned their backs on Elfland still have some skill in writing the runes and glyphs of the Abandoned onto Mortal weapons: longswords, shortswords, daggers, and spears. 

\mysubsection{Magic Weapons}{spriggan-magic-weapons}

Enchanted weapons can all strike creatures that require magical weapons to hit, and can emit a small circle of bluish or greenish light at will (similar to the light cast by a few candles).

Weapons are often named after their wielder or maker, and the powers of the runes on the blade.  Some examples:

\mybullet {
  \item The Hallowed and Indestructible Spear of Yoon-Suin
  \item The Thrice Deadly Dagger of Kos
  \item The Flaming and Twice Accurate Sword of Magnuss
}

\mysubsection{The Runes of Elfland}{spriggan-elfland-runes}

\mylist {

  \item Because Spriggan cannot handle iron, the material of the weapon must be exotic (silver, gold, etc) or otherworldly (adamantium, meteorite).  The material needs to be available and should be worked out with the Arbiter.  Only daggers, swords (long and short), and spears can be enchanted

  \item In order to accept an enchantment, the weapon must have a Mortal sigil, mark, or writ etched onto the blade, once for each Elfland Rune.  Archaic runes require a \mylink{Wizard Sigil}{sigil-wizard}, Fiendish runes require a \mylink{Witch Mark}{occultism-witch-mark}, and Seraphic runes require a \mylink{Holy Writ}{miracle-holy-writ}.

  \item The weapons is enchanted with the help of the Abandoned.  You must use 4 Remembrance Die to summon one of the Abandoned whose True Name you know.  Each Abandoned can write a single Elfland Rune on the weapon.  The Abandoned can only write in the language that they know:  Archons can only write Archaic Runes, Fiends can only write Fiendish Runes, and Seraphs can only write Seraphic Runes.

  \item  Aside from the cost of the weapon itself, you must pay for the materials necessary to perform the magic.  The 
  The first Rune costs 5,000fe in materials.  The second Rune costs 5,000ag in materials.  The third (or more) Rune(s) cost 5,000au in materials.


}
 
The runes on the next page will get you started.  Feel free to work with the Arbiter for additional powers.  



\mysubsection{Archaic Runes}{spriggan-archaic-runes}

\mybold{ Cleaving}

The weapon has the Weapon Trait: Cleave

\mybold{ Dazing}

The weapon has the Weapon Trait: Daze

\mybold{ Hefty}

The weapon has the Weapon Trait: Hefty

\mybold{ Rending}

The weapon has the Weapon Trait: Rend

\mybold{ Brutal}

The weapon has the Weapon Trait: Brutal

\mybold{ Lucky}

When in your hands, the weapon has a d4 \UD that can be used to add to any \RO attempt you're making. You can use this \UD to add to any \RO attempt you're making (including Fight and Guard).  The \UD is restored at the start of the next Session.

\mysubsection{Fiendish Runes}{spriggan-fiendish-runes}


\mybold{ Accurate}


Adds +1 to your Fight \RO when using this weapon.  This Rune can be written more than once.

\mybold{ Shielding}


Add +1 to your Guard \RO when using this weapon.  This Rune can be written more than once

\mybold{ Deadly}


The weapon's damage is \DCUP.  This Rune can be written more than once.

\mybold{ Flaming}


In addition to its normal damage, the weapon deals +d4 fire damage.  On a Crit, the victim must make a Save vs. Doom or be lit on fire for d4 Markovian (+d3 damage at the start of every Moment).

\mybold{ Icy}


In addition to its normal damage, the weapon deals +d4 ice damage.  On a Crit, the victim must make a Save vs. Doom or be paralyzed for d4 Markovian.

\mybold{ Bloodletting}


In addition to its normal damage, the weapon inflicts Bleeding when it hits Flesh.




\mysubsection{Seraphic Runes}{spriggan-seraphic-runes}


\mybold{ Hallowed}


In addition to its normal damage, the weapon deals +d6 extra damage to the Unhallowed.  This Rune can be written more than once.

\mybold{ Indestructible}


The weapon cannot be destroyed by non-magical means (acid, rust, etc.), and it gets a 6-in-6 Save against being destroyed by magical means (if it would normally not get a Save).

\mybold{ Tenacious}

When in your hands, the weapon cannot be dropped unless you will it so.  If you are struck down, there is no way to remove the weapon from your hand short of cutting the hand off (which breaks the enchantment)


\mybold{ Infamous}

When you deal a killing blow with this weapon, the victim's noumenon is briefly revealed (for most creatures, it appears as a small, vaporous homunculus which vanishes after a few moments).  This immediately forces a morale check for all enemies that are Close.

\mybold{ Vigilant}


When in your hands, you can see invisible creatures, and you have both Day Vision and Dark Vision (and you can switch between them at will).  You cannot be surprised while the weapon is in your hands.

\mybold{ Rallying}


When you deal a killing blow with this weapon, your allies automatically win Init in the next Moment.




}%end
