 \mysection{The Myrkálfar}{species-murk}

  \flavor{Once the gods walked upon Earth as men walk and spake with their mouths like Men. That was in Wornath-Mavai ... a garden fairer than all the gardens upon Earth. Kib was propitious, and Mung raised not his hand against it, neither did Sish assail it with his hours... \Tilde Lord Dunsany}


  \mysubsection{Appearance}{murk-appearance}

  Wornath-Mavai. Svartalfheim. The Glorious Undergarden, beauty beyond measure, Paradise beneath the Mountains, Home to the Myrkálfar, the people beyond Time, who live only for the now.

  Like your brothers and sisters the Spriggan, you were cursed with curiosity, and wondered what was outside of Svartalfheim.  Further and further did you adventure beyond the borders of Svartalfheim until, one day, you were unable to find your way back.  You are now one of the Nomadic People, the Rom.

  Outside of Svartalfheim you were almost immediately enslaved by one of the underworld Empires, for they take great delight in subjugating gods to work for them.  But the burning desire to be free never left you. Almost all Myrkálfar attempt to escape their masters.  Most are killed trying to escape, ending their torment, but some make it out and make their way to the surface.  

  Myrkálfar often act as guides in the Veins, and as such many Mortal races feel that "Murks" are desperate to find their way back again. But the truth is that you can't go back to the point before you knew of the world outside of Svartalfheim.  You have eaten from the tree of knowledge and have been cast out of Eden.  You can never go home again.

  You are tall and thin - like your overworld brethren the Spriggan - but a little shorter, standing less than 2m tall.  Your face resembles Mortals though your eyes and pupils are of the same color: usually cobalt, white, or ruby.  You seem to care little for fashion, yet you are always effortlessly well-dressed in black, white, or gray.  Masks are common among Murks - their captors often heavily scar their faces and bodies out of envy of their beauty - as are broken manacles and collars.


  \mysubsection{The Veins of the Earth}{murk-veins-of-the-earth}

  According to those who have dared to set foot beneath the skin of the planets of the Totality, the deep places of the moons are beyond description.  They are realms of wondrous colors, breathtaking landscapes, powerful magic, and staggering plenty.  It is a paradise beneath our feet.  The Empires that dwell within stagger the breadth and depth of the surface realms; they shape the caverns and tunnels according to their will, blessed by a deity some heretics say is older than \TheAuthority.  They are truly the gods' people.  You, however, will never meet one - the denizens do not leave their home, save for the unlucky and foolish Myrkálfar.  Why would they?  There is nothing in the world without that the depths cannot provide. Those fortunate explorers who are able to discover an entrance to the depths never return - only a fool turns his back on paradise.\footnotemark[\value{footnote}]

  \footnotetext{The Veins of the Earth, as they are collectively known, have adventures and rules all their own.  Patrick Stuart's excellent \href{http://www.lotfp.com/store/index.php?route=product/product&product_id=262}{"Veins of the Earth"} is the sourcebook used by The Totality of Ygg, and is the world that the \mylink{The Myrkálfar}{species-murk} come from.}


  \setcounter{footnote}{0}  

  \mysubsection{The Basics}{murk-basics}

  \myhighlight{Hale}{murks-flesh}

  Myrkálfar have a d8 \FLESH

  \myhighlight{Emancipated}{murk-emancipated}

  You are an escaped slave from one of the Empires of the Veins of the Earth.  You care for nothing but freedom.  

  Many Mortals find you alien, cold, and uncaring.  This is because \TheAuthority has stolen their freedom from them - the freedom to ask questions, the freedom to go where you desire and do what you wish.  You will never allow your freedom to be taken again, and you will kill to defend both your freedom and the freedom of others.

  Roll a d4 on the \mylink{Imperial Masters}{murk-imperial-masters} table below to see which Empire you escaped from.

  \myhighlight{Emotionless}{murk-emotionless}

  You add your \LVL to any \RO or \RB attempt that includes your Sanity.  The \UD still moves \DCDOWN on a natural 1 or 2.


  \mysubsection{Creation}{murk-creation}

  \callout{
    \mynumlist {
      \item Move any of the core Skills \DCUP.
      \item Gain the Skill "Veins Lore" at a Trained (d8,+1) level
      \item Move \mybold{all} of your core Saves \DCUP
      \item Move your Sanity \DCUP (it should now be a d8)
      \item Roll a d4 on the \mylink{Imperial Masters}{murk-imperial-masters} table below to see which Empire you escaped from. Write down any benefit from that.
      \item Write down your remaining Virtues, Complications, and Starting Gear
    }
  }

  \cbreak

  \mysubsection{Imperial Masters}{murk-imperial-masters}
  
  Roll a d4 to see which Empire you have escaped from:
  
  \mytable{X l}{
    \thead{d4} & \thead{Culture} \\
  }{
    1 & The Deep Janeen \\
    2 & The Ælf-Adal \\
    3 & The Dvargir \\
    4 & the dErO \\
  }

  \dashedbox {
    \mylist {
      \item \mybold{Deep Janeen:}   You've worked the mazes and artworks of the Janeen.  You can never get lost when traveling in the \mylink{Veins}{murk-veins-of-the-earth}. The Janeen only want the most beautiful to work their art - your Presence starts \DCUP (d8).  You know the difference between Lithic and Umbral architecture.
      \\~
      \item \mybold{Ælf-Adal:}   The never ending hate of the Ælf-Adal has burned out your empathy.  You are immune to rage, hate, and fury.  Your starting Sanity is an additional \DCUP (meaning your starting Sanity is a d10)
      \\~
      \item \mybold{Dvargir:}   You have participated in The Work, and now The Work is part of you.  Your Talent starts \DCUP (d8), and you can carry +4 Significant Items.
      \\~
      \item \mybold{dErO:}   You possess a partial congruity knot in your skull.  You are immune to Charm and Sleep.  You got really good at dealing with dErO "machines" - you are Trained (d8,+1) in the Tinkering Skill
    }
  }

  \newpage

  \mysubsection{Virtues}{murk-virtues}

  \myhighlight{Cat's Eyes}{murk-virtue-cats-eyes}

  You have both Dark and Day Vision; you can swap between them instantly.  Your Dark Vision pierces even magical Darkness.

  \myhighlight{Fate's Hand}{murk-virtue-fates-hand}

  All of your Saves start at Preserved (d8,+1)

  \myhighlight{The Hound of Sish}{murk-virtue-hound-of-sish}

  You are untouched by Time, the last remnants of godhood.  You are immune to aging, and your \DEATH starts at \mybold{Tough} (d12)  

  \myhighlight{Metal Empathy}{murk-virtue-metal-empathy}

  You can smell any metal you choose (gold, silver, iron, etc) up to 1m away.  Metal weapons do -2 damage per die (minimum 1) to you.  

  \myhighlight{Silent Speech}{murk-virtue-silent-speech}

  You know the Silent Speech, the language of stones and rocks and the trade speech of the \mylink{Veins of the Earth}{murk-veins-of-the-earth}.  You can use this language to speak with stones. They can tell you what has touched them and what is under or behind them.  This makes it almost impossible to get lost underground. They're not great with time though ...





  \mysubsection{Complications}{murk-complications}


  \myhighlight{Logical}{murk-complication-logical}

  You are devoid of any emotion.  People call you cold, distant, or calculating.  When faced with a decision or dilemma, you will always opt for the logical, unemotional response.  Mortals in particular find you eerie and alien, and react with fear or loathing.


  \myhighlight{Sun Allergy}{murk-complication-sun-allergy}

  Prolonged exposure to direct sunlight causes severe burns and painful blisters.  You seek out shade and shadow whenever you can, and you are most comfortable in subterranean settings.  You can travel well enough through wooded or hilly areas, but wide exposure (deserts, plains) can be problematic if you don't take precautions.


  \myhighlight{Unhallowed}{murk-complication-unhallowed}
    
  You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"


  \mysubsection{Starting Gear}{murk-starting-gear}

  \mybullet {
    \item a suit of Light armor (describe it to the Arbiter) and a shield;
    \item an insect mandible (longsword) or Knotsman war-axe;
    \item 2 pet rocks (you can speak to them);
    \item a journal filled with names and locations that lead nowhere;
    \item a leather folio of maps that lead nowhere;
    \item a pouch of 5 gems (roll on the \mylink{Gems table}{appendixb-random-treasure} in Appendix B);
    \item a pouch of tokens used by the slaves in the culture you've escaped from
  }


