 \mysection{The Pooka}{species-pooka}

  \flavor{In the mists before the Beginning, Fate and Chance cast lots to decide whose the game should be; and he that won strode through the mists to \TheAuthority and said: "Now make Gods for Me, for I have won the cast and the Game is to be Mine."  Who it was that won the cast, and whether it was Fate or whether Chance that went through the mists before the Beginning to \TheAuthority - none knoweth. \Tilde Lord Dunsany}

  \mysubsection{Appearance}{pooka-appearance}
    
  You do not believe in Fate - it's a made up idea, created by people who are terrified that we are plunging headlong through the void with no rhyme or reason.  Chance and Chaos govern the Totality.  This is reprehensible to \TheAuthority, who seeks to keep the secret of the game of lots from us.  But you are proof that it is Chance that was victorious, and for this you are cursed, and marked Unhallowed.

  You stand scarcely 1m tall, with the head and feet of a rabbit, pig, goat, or toad.  You are gregarious, sly, and always at the point of laughing.  Pooka love to be around people, and it's not uncommon to find them on ships (where they're thought to be good luck), tending bars (if they don't drink away their profits), or with gypsy troupes.  You excel at dancing and singing, and take every opportunity to do both.

  \cbreak

  \mysubsection{The Basics}{pooka-basics}


 \myhighlight{Squishy}{pooka-flesh}

Pooka have a d4 \FLESH

  \myhighlight{Good Time Guys}{pooka-good-time}

  You add your \LVL to any \RO or \RB attempt that includes your Presence.  The \UD still moves \DCDOWN on a natural 1 or 2.

  \myhighlight{Luck Dice}{pooka-luck-die}

  Pooka have a Luck Die - a unique \UD similar to \mylink{Knaves}{trope-knave} - that you can use to help other Allies (but not yourself).  You can roll this Luck \UD at any time to affect someone's \RO or \RB attempt. You can wait until after they roll to use this ability, but you can only roll once per \RO or \RB attempt.

 \mysubsection{Creation}{pooka-creation}

  \callout{
    \mynumlist {
      \item Start one of the core Skills at \mybold{Trained (d8+1)}
      \item Start one of your Saves at \mybold{Preserved (d8+1)}
      \item Move your Presence \DCUP (it should now be a d8)
      \item You start with a d4 Luck Die
      \item Write down your Virtues, Complications, and Starting Gear
    }
  }

    \mysubsection{Virtues}{pooka-virtues}

    \myhighlight{Apotropaic}{pooka-virtue-apotropaic}
  
    Your presence in a party nullifies any effects of the \mylink{Jinx Charm}{charm-jinx}. Buildings where you are sleeping are warded from casual attack (meaning the building would be spared in a riot, for example).  When you're taking a \mylink{Bivouac}{combat-resting-bivouac}, the Arbiter has a -4 penalty on her roll for \mylink{Wandering Monsters}{monster-wandering}. 

    \myhighlight{Best. Night. EVAR!!}{pooka-virtue-best-night}
  
    People who hang out with you have a pretty great time.  You increase everyone's \mylink{Carousing}{advancement-carousing} die by \DCUP (and earn 10\% of the total Carousing Glory of whoever you party with as well). Anyone who doesn't carouse with you has to hear about how awesome the night was the entire next day.    

    \myhighlight{Hype Man}{pooka-virtue-hype-man}
  
    During a \mylink{Breather}{combat-resting}, you can roll a number of d6 equal to your \LVL and heal \SUM Grit to you or your Allies divvied up any way you want.  Additionally, if you \mylink{help out}{skills-helping-out} someone with a Skill, you don't count towards the "only one person can help" rule.

    \myhighlight{Bro, Hit This}{pooka-virtue-hit-this}

    For any narcotics you take, (a) the \UD only moves \DCDOWN if you roll a 1, (b) you add your \LVL to your \mylink{Addiction}{gear-narcotics-addiction} roll, and (c) if you \mylink{Overdose}{gear-narcotics-overdose}, you don't have to roll a \mylink{Save vs. Toxins}{saves} (nothing happens except you wasted some drugs).  When you take a \mylink{Vacation}{civilization-vacation}, \RS using your Luck die; if you don't Fail, you can obtain 1 \UD of \myital{any} \mylink{Common Narcotic}{gear-narcotics} for free (even Narcotics that would normally not be available, like Black Lotus in a Small town)

    \myhighlight{Wired}{pooka-virtue-wired}
  
    You cannot be \mylink{Surprised}{combat-surprise} (including the Drop) and you always win \mylink{Init}{combat-init}.  You are immune to Sleep.


    \mysubsection{Complications}{pooka-complications}

    \myhighlight{Tiny}{pooka-complication-tiny}

  You stand only 1m tall to start.  You can only carry a number of Significant Items equal to your \MAX \VIG (you don't get the +2 bonus). If you wear armor, you can only wear armor for "little people" (child-sized).  You cannot wield 2-handed weapons.

    \myhighlight{Unhallowed}{pooka-complication-unhallowed}
    
    You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"


    \cbreak

    \myhighlight{You My Boy Blue!}{pooka-complication-you-my-boy}

    Your love for people causes you to "bond" with people that you party with.  After you go \mylink{Carousing}{advancement-carousing} with others, pick one of the people you caroused with randomly. You are now "bonded" to that person.  Until the next time you go Carousing, you'll favor that person over the others. If there's any extra \mylink{Grit}{combat-flesh-grit} left to distribute, you'll pick them; if there's an extra share of treasure, you'll argue for that person to get it; if you have extra narcotics, you'll give them to that person.  Next time you go Carousing, pick another person randomly ...

    \mysubsection{Starting Gear}{pooka-starting-gear}

    \mybullet {
      \item d4 \UD of any Narcotic (your choice); 
      \item a pair of daggers or hand axes;
      \item 5 rolls on the Random Item table;
      \item 1 gold piece;
      \item playing cards or dice
    }

 


