% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggMonsters}{%
  \mychapter{Monsters}{monsters}
}

\renewcommand{\yggMonstersText}{%

\mysection{Monsters Stats}{monster-stats}


\mysubsection{Monster Morale}{monster-morale}

Morale is broken into 3 general types:  Cowardly, Orderly, and Fanatical.  Roll Morale by rolling 2d6 - if the number is greater than the basic roll (but not equal to!), they will attempt to flee or surrender.

\mybullet {
  \item \mybold{Cowardly} Basic roll is 3.  If the Monsters are in a group, roll a) when the first Monster dies (but only if the Monsters are outnumbered; b) when half the Monsters are down; or c) whenever a "leader" dies.  If the Monster is by itself, roll a) when it first takes damage and b) when it's at half Health or less.

  \item \mybold{Orderly} Basic roll is 7.  If the Monsters are in a group, roll a) when half the Monsters are down; or b) if \mybold{all}  the leaders are dead.  If the Monster is by itself, roll when it's at half Health or less.

  \item \mybold{Fanatical}  Basic roll is 11.  If the Monsters are in a group, roll when half the Monsters are down AND all the leaders are dead.  If the Monster is by itself, it will automatically pass a morale check.
}

\mysubsection{Monster Modifiers}{monster-modifiers}

\myhighlight{Monster Speed}{monster-speed}

  \mytable{l X X X}{
    \thead{} & \thead{Slow} & \thead{Base} & \thead{Fast}  \\
  }{
    Speed & d20 & d16 & d12 \\
    \DEX \RB & d6 & d10 & d16 \\
    Actions & 1 & 2 & 3 \\
  }

  \mybullet {
    \item Monster Speed is used when rolling Init
    \item Monster \RB is used if a \DEX \RB is required
    \item Monster Actions are the number of Actions they can take in a Moment. Like the Adventurers, the Monster's Moment ends when they take a Combat Action.
  }

\myhighlight{Monster Power}{monster-power}

  \mytable{l X X X}{
    \thead{} & \thead{Weak} & \thead{Average} & \thead{Strong}  \\
  }{
    Health & 3 per \HD & 5 per \HD & 7 per \HD \\
    \VIG \RB & d6 & d10 & d16 \\
  }

  \mybullet {
    \item Monster Power is used to determine Health (3, 5, or 7 Health per \HD)
    \item Monster \RB is used if a \VIG \RB is required
  }

\mysubsection{Monster Soak}{monster-soak}

Soak is a general term to represent a damage threshold because of armor, thick scales or carapaces, or tough or rubbery bodies.  The amount of damage from a \mybold{physical attack}  is reduced by the amount of the Soak.  For example, a Monster with a Soak of 3 would ignore 3 points of damage from a physical attack (so if you roll a 4 for damage, the Monster will only take 1 point of damage).  Certain Monsters have a Soak against specific types of weapons (for example, Skeletons can Soak 1 point of Stabbing damage).  Murder bypasses Soak, and Rend reduces Soak by 1. 

  \mytable{l X}{
    \thead{Rating} & \thead{Examples}  \\
  }{
    1 & Armored troops, Giant Toads, Skeletons (bashing only), etc \\
    2 & Knights, Giant Beetles, etc \\
    3 & Automatons, Powerful Demons etc \\
    4 & Dragons, Titans, etc   \\
  }

 \mysubsection{Basic Monster Stats}{monster-basic-stats} 

  \mytable{X c c c}{
  \thead{\HD} & \thead{Damage} & \thead{Weakness} & \thead{Base Save (x-in-6)} \\ 
   0\footnote{0 \HD means the Monster has 1 Health} & d3 &  d24 & 1 \\
   1 & d4 &  d24 & 1 \\
   2 & d6 &  d20 & 2 \\
   3 & 2d4 &  d20 & 2 \\
   4 & d10 &  d16 & 3 \\
   5 & d12 &  d16 & 3 \\
   6 & d6+d8 &  d12 & 4 \\
   7 & 2d8 &  d10 & 4 \\
   8 & 2d10 &  d6 & 5 \\
   9 & d10+d12 &  d3 & 6 \\
 }


\MONSTERBLOCK[
  Name=Basic Monster,
  Link=monster-basic-monster,
  MV=\myital{Speed},
  WK=\myital{Weakness},
  DMG=\myital{Damage Targets},
  HD=\myital{HD},
  Power=\myital{Power},
  Soak=\myital{Soak},
  Morale=\myital{Morale},
  Save=\myital{Save},
  Extras={\myital{Attributes}}
]

\myital{Description and extra information}

\mysubsection{Monster Classification}{monster-classification}


\myhighlight{Aberrations}{monster-type-aberrations}

\example{ Aberrations take no damage from Biomancy spells or Toxins}

\myhighlight{Amphibians}{monster-type-amphibians}

\example{ Zoological. Amphibians are Beasts for purposes of summoning, etc. They are Slippery (first Fight \RO misses, you can roll again).}

\myhighlight{Arthropods}{monster-type-arthropods}

\example{ Zoological. Arthropods are Beasts for purposes of summoning, etc.}

\myhighlight{Automatons}{monster-type-automatons}

\example{ All Automaton are Mindless (immune to spells from the Mind paradigm, no morale) and Unhallowed.}


\myhighlight{Demons}{monster-type-demons}

\example{ All Demons are Unhallowed. They take no damage from iron weapons or from spells \mybold{not}  of the Entropy paradigm. Seeing a Demon prompts a Sanity check (including for Allies if summoned by a Spriggan)}


\myhighlight{Dinosaurs}{monster-type-dinosaurs}

\example{ Zoological. Dinosaurs are Beasts for purposes of summoning, etc.}


\myhighlight{Dire Beasts}{monster-type-dire-beasts}

\example{ Zoological. Dire Beasts are Beasts for purposes of summoning, etc.}


\myhighlight{Giantkin}{monster-type-giantkin}

All Giantkin automatically win any for \RB : \VIG tries.

\myhighlight{Goblinoids}{monster-type-goblinoids}

\example{ All Goblinoids are Nocturnal (have Darksight), and are smart enough to use tactics where applicable.}


\myhighlight{Horrors}{monster-type-horrors}

\example{ All Horrors are Unhallowed. Seeing a Horror immediately prompts a Sanity roll.}

\myhighlight{Plantlife}{monster-type-plantlife}

\myhighlight{Reptiles}{monster-type-reptiles}

\example{ Zoological. Reptiles are Beasts for purposes of summoning, etc.}


\myhighlight{Shades}{monster-type-shades}

\example{ All Shades are Unhallowed. They are Incorporeal and take no damage from weapons made from iron, or from spells of the Force or Mind paradigm. They take no damage from Toxins. Seeing a Shade immediately prompts a Sanity roll.}

\myhighlight{Swarms}{monster-type-swarms}

\example{All Nearby swarming Monsters share their Health equally as one "pool", and take double damage from attacks that affect multiple targets.  Swarms deal damage equal to their \HD times 2 i.e. a 3\HD swarm would deal 6 damage to all Close targets}

\myhighlight{Walking Dead}{monster-type-walking-dead}

\example{ All Walking Dead are Mindless (immune to spells from Mind paradigm, no morale) and Unhallowed. They take no damage from Toxins.}

\myhighlight{Elementals}{monster-type-elementals}

\example{ All Elementals take no damage from iron weapons, and no damage from spells \mybold{unless}  they are from the Elemental paradigm }

\myhighlight{Dragons}{monster-type-dragons}

\example{ Dragons are immune to the Mind paradigm, and to Elemental Damage that corresponds to their breath weapon.  They can only be struck by magical weapons.  They automatically win any \RB tries. }


 \newpage



 \mysection{Monster Attributes}{monster-attributes}

 \myital{These are all taken from The Black Hack}

\mysubsection{Acidic}{monster-attribute-acidic}

Armor cannot be used to block damage from this monster

\mysubsection{Amorphous}{monster-attribute-amorphous}

The Monster has no easily definable anatomy - Murder tries don't work on them.

\mysubsection{Berserk}{monster-attribute-berserk}

When reduced to 0 Health, the Monster lives until the bottom of the \myital{next} Moment.

\mysubsection{Bloodthirsty}{monster-attribute-bloodthirsty}

The Monster deals double damage against targets with 0 Grit

\mysubsection{Frenzied}{monster-attribute-frenzied}

Every time the Monster misses, it gains an additional Action in the next Moment.  The Actions "reset" once the creature deals damage. A Fight \RO still ends their Moment.

\mysubsection{Graceful}{monster-attribute-graceful}

Roll a d6 at the start of every Moment - on a 1 or 2, the Monster gets an additional Action

\mysubsection{Grudge}{monster-attribute-grudge}

Add the number of Moments since the first Moment of Combat to the damage the monster deals

\mysubsection{Keen}{monster-attribute-keen}

Keen Monsters can't be Surprised at the \mybold{start}  of Combat, and can detect Invisible creatures. Knaves are unable to get the Drop on these creatures

\mysubsection{Leaper}{monster-attribute-leaper}

Once per combat the monster can move to a Faraway place

\mysubsection{Mindless}{monster-attribute-mindless}

Mindless creatures are immune to spells from the Mind paradigm, and have no morale (they fight until they die)

\mysubsection{Nocturnal}{monster-attribute-nocturnal}

Nocturnal Monsters have Darksight

\mysubsection{Pack}{monster-attribute-pack}

The Monster gets +1 Damage for every Nearby ally

\mysubsection{Slippery}{monster-attribute-slippery}

Every Moment, the first Fight \RO that succeeds against the Monster misses.  The character that made the successful Fight \RO can attack again.

\mysubsection{Splitting}{monster-attribute-splitting}

Whenever the creature is hit by an attack, it splits in half, sharing the pool of HP between the "split" parts of itself.

\mysubsection{Sprightly}{monster-attribute-sprightly}

When fighting this Monster, Init rolls are tried with a -4 modifier.

\mysubsection{Supportive}{monster-attribute-supportive}

The monster can heal another Nearby Monster for \HD Health.  They can do this \HD number of times.

\mysubsection{Swarming}{monster-attribute-swarming}

All Nearby swarming Monsters share their Health equally as one "pool".  Swarms take double damage from Attacks that affect multiple targets.

\mysubsection{Swift}{monster-attribute-swift}

If the monster is hit by an Attack it may immediately Move

\mysubsection{Vulnerable}{monster-attribute-vulnerable}

The monster takes double damage from a certain source (fire, ice, etc)


} %end
