% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggSpells}{%
  \mychapter{Spells}{spells}
}

\renewcommand{\yggSpellsText}{%
  \mysection{Spell Coversions}{spell-conversions}

  \mysubsection{Beneath the Missing Sea}{conversion-beneath-the-missing-sea}


  \mysubsection{The Gnomes of Levnec}{conversion-gnomes-levnec}

  
  \mysubsection{The Stygian Library}{conversion-stygian-library}


Blind:  Save vs. Hex or Blinded for d6 Markovian
Charm: As Wizard spell, floor([level]/2) Blood Dice
Command Unhallowed: As Charm, [level] Blood Dice.  Unhallowed only
Create Stone:  Create a stone block from nothing 1m cubed.  Stone must rest on floor.
Deafen: Save vs. Hex or Deafened for d6 Markovian
Detect Thief:  Anyone Nearby who has stolen from the Library will glow a bright red
Detect Unhallowed: Any Unhallowed Nearby glow bright green
Enervate: As Wizard spell, floor([level]/2)  Blood Dice
Hold Person: Save-vs-Hex or Paralyzed for d6 Markovian
Invisibility: As Wizard spell, self only
Knock: As Wizard spell, floor([level]/2) Blood Dice
Levitate: As Levitating Disc, but self only
Lock: As Wizard spell, floor([level]/2) Blood Dice
Mending: Repair a single break or tear
Message: Send a missive to any other librarian in the library. Takes Minutes.
Reduce to Phantom:  If a Nearby creature is on Death's Door, slays them and turns them into a Phantom.
Shape Stone:  As 5th level Murk ability
Shape Wood: As 5th level Murk ability, but with wood
Shelf Step: If unseen, can step from one bookshelf to any other in the library that they know
Spider Climb:  Move up, down, and across vertical surfaces and upside down along ceilings
Turn Mortal: As curse the Unhallowed, but Mortals





  \newpage




} %end
