% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggAdvancement}{%
  \mychapter{Advancement}{advancement}
}

\renewcommand{\yggAdvancementText}{%


  Advancing your adventurer (also known as "leveling") allows you to become more powerful.  To gain levels, you need Experiences (XP).  When you get a certain amount of XP, you go up a level.


  \mytable{X c c }{
    \thead{Level} & \thead{Min XP} & \thead{Coin Type} \\
  }{
    1 & 0 & Iron \\
    2 & 1,000 & Iron \\
    3 & 3,000 & Silver \\
    4 & 6,000 & Silver \\
    5 & 11,000 & Silver \\
    6 & 19,000 & Gold \\
    7 & 32,000 & Gold \\
    8 & 53,000 & Gold \\
    9 (max) & 87,000 & - \\    
}

There are 3 main ways to gain XP: Adventuring, Looting, and Carousing


\mysection{Adventuring}{advancement-adventuring}

Think about the Savage Sword of Conan.  He's out there killing pteranodons and slaying an average of 3 men with one blow, but those feats of strength are all encounters in a chapter of his greater adventures.  They fit nicely in a handful of comic books ("part 3 of 3 - Escape from the Necromancer's Lair)".  The Arbiter is there to help you narrate the chapters of \mybold{your}Adventure, just like R.E.H. did for Conan.

At the end of an Adventure, when you return to Civilization to eat and drink your fill, the Arbiter can award you XP.  It's completely up to her how much this is!  A good rule of thumb is if the Adventure would close a comic series or end a TV arc or finish a section of a novel, that's a good time to assign some XP (Thundarr breaks the werewolf curse; Conan escapes the Demons of the Summit; Fafhrd and the Grey Mouser return to Lankhmar with Ohmphal's fingertips, etc.)

\mysection{Looting and Spending}{advancement-looting-spending}

\flavor{
  There comes a time, thief, when the jewels cease to sparkle, when the gold loses its luster, when the throne room becomes a prison, and all that is left is a father's love for his child. ~King Osric
}

Every bit of treasure you're able to loot on the adventure can potentially count towards your advancement ("potentially" because it's useless if you don't spend it).  Note that money you obtain and spend outside of an Adventure doesn't count towards this total (so if you pickpocket some rube or setup an opium trade or steal from the King it doesn't count, unless the chapter of your Adventure is entitled "Steal Shit from the King").  This is up to the Arbiter's discretion.

\mylist {
  \item Levels 1 and 2 are the \mybold{Iron levels}.  You get 1xp for every iron piece you loot AND spend in Civilization.  These don't have to be Iron pieces per se -  if you were to loot and spend a single \AU, you would gain 100xp (but you would need to be in a larger civilization to spend it!)

  \item Levels 3-5 are the \mybold{Silver levels}.  You get 1xp for every silver piece you loot AND spend in Civilization 

  \item Levels 6+ are the gold levels.  You get 1xp for for every gold piece you loot AND spend in Civilization
}

Any coins you spend in Civilization are converted to XP on a 1-to-1 basis, including:

\mybullet {
  \item The amount of money you have to spend to Sojourn or Sabbatical
  \item Any gear, narcotics, mounts, etc. you buy while in Civilization
  \item Any money you spend on Occultism, Chymistry, Miracles, Medicinals, Staff Magic, Sword Magic, or Inscription
  \item Any money you spend on a Carousing
}

Keep in mind the size of the Civilization you're in - you can't spend gold in Small hamlets!

You'll note that it gets harder and harder to get XP with money as you go up in level.  This is by design - legendary heroes aren't getting experience taking money from orc babies, but by doing epic shit i.e. writing chapters in their Adventure.  In time, the jewels cease to sparkle...


\mysection{Carousing}{advancement-carousing}
If you've spent all the money you can, Carousing is a way to convert any extra coins you've got lying around into XP on a 1-for-1 basis. Say how much money you're going to burn and roll a d20 on the chart below.  You get a +1 for every 100 coins you spend (rounded down)

If you decide to go Carousing with a Pooka, you roll a d24 instead.  If a Pooka goes Carousing with you, \myital{they} get 10\% of any XP you make (this is in addition to your XP, they don't take from your XP).  They also have to roll a 20 on the table below, though.

\end{multicols}   

\mytable{l X}{
  \thead{} & \thead{While Carousing you ...} \\
}{
  1  & Accidentally set the town aflame. Roll d6 twice. 1-2 burn down where you're staying; 3-4 some other house burns down; 5-6 a big chunk of town goes up in smoke. 1-2 no one knows it was you; 3-4 your fellow carousers know you did it; 5 someone else knows, perhaps a blackmailer; 6 everybody knows. \\
  2  &  Were robbed whilst unawares. Was it that saucy wench that you swear came to your room? You lose everything of value that you are carrying (Arbiter's discretion) \\
  3 & Talk shit and get called out. You get the XP for this Carousing, but you can't get any more until you do something really awesome designated by the Arbiter, like killing a legendary monster or stealing a legendary treasure. \\
  4 & Get in a fight, lose d3 teeth, get a black eye, or break your nose and you'll be sore (-d3 Grit, min 0) at the start of the next dungeon or fight. \\
  5 & Get alcohol poisoning. Roll a Save vs. Toxins. If you succeed, take 1 damage to Grit.  If you fail, take d6 damage to Grit \\
  6 & Are inducted into a cult. It takes your friends the rest of the Sojourn to deprogram you.  Carousing earned you  -10\% XP \\
  7 &   Break some knuckles punching a dude. No two-handed weapons/shields until you Sojourn again \\
  8 & Hangover from Hell. Roll twice on the Hang Over effect and take \mybold{both}  effects \\
  9 & Are mistaken for someone else, and charged with their tab. Pay 30\% more money (no xp for it) or wake up in the slammer. \\
  10  & Wake up in stocks. Authorities let you out after a day. \\
  11 & Gain reputation as a lecherous lush. Social interactions in this town are \myital{awkward.}  \\
 12 & Adapt to all the partying. Your Save vs. Toxins goes up by 1 until the next Sojourn \\
 13 &Gain 3 rumors about the next adventure  \\
  14  &Totally see through the Snail Knight's disguise, but are cool about it, and he will show up when you need him most. \\
  15 & Dice are hot. Get d100 coins  \\
  16 &Have an epic night and end up with a sweet scar.  \MAX Presence goes up \DCUP  \\
  17  & Win a bar bet and gain the services of two henchmen with low morale for a month. They may stay on if you pay them  \\
  18 & Run into a long-lost relative. Maybe they want to go adventuring with you?! (henchman - high morale)  \\
  19 &  Are mistaken for an important figure and the party gets really going. +25\% XP.  \\
  20+ & Have a lot of fun and get plenty of relaxation \\  
}

\example {
    Mad Tom (a Soldier), Aelfirth (a Mystic), and Stump Beefknob (a Pooka) are all level 1, returning from their first adventure laden with loot.  They make their way back to Lankhmar and elect to take a Sojourn. The Arbiter awards them all 500 xp right off the bat for surviving and killing the Thing Beneath the Stair (completing a Chapter in the Arbiter's story).  They each spend 100\FE to Sojourn and spend an additional 100\FE each on equipment. After selling a carpet and armoire they managed to secure, they each have 400\FE left.  They all decide to go Carousing together and spend their remaining iron pieces.  

    Because they're Carousing with a Pooka, Mad Tom and Aelfirth both roll a d24 - Stump rolls a d20.  Tom rolls a 14 (10 + 4 for the 400\FE) and sees through the Snail Knight's disguise; now he has an ally that he notes on his character sheet.  Aelfirth rolls a 7 (3+4, bad luck!) and gets alcohol poisoning.  Stump rolls a 15 - looks like he won 43\FE gambling.  

    Tom and Aelfirth get 1,100 xp (500 from the Arbiter, 100 from the Sojourn, 100 from equipment, and 400 from going Carousing).  Stump earns 1,180xp (500 from the Arbiter, 100 from the Sojourn, 100 from the equipment, 400 from Carousing, plus an extra 10\% of the 800 Tom and Aelfirth collectively earned from their Carousing).
  }


  \begin{multicols}{2}

  \mysection{Gaining a Level}{advancement-leveling}

  You made it to the next level!  Congratulations.  You can do the following:
  
  \mynumlist {
    \item Roll your \FLESH twice and add the best result to your Grit.  If you're a Soldier, also add your \LVL to this roll.
    \item Increase the \MAX of your Primary Stat \DCUP
    \item Choose an addition (non Primary) stat and increase its \MAX \DCUP.  This can be a \mylink{Tangible}{tangible-stats} or \mylink{Intangible}{intangible-stats} Stat, but not your Primary one.
    \item If it's an even numbered level (2,4,6, or 8) - increase your Edge or Ordinary \mylink{Save}{saves} by 1.  If it's an odd numbered level (3, 5, 7, or 9) - you can increase any Save by 1 (\mylink{Murks}{species-murk} can increase any Save at any level).
    \item If you're a Barbarian, roll your \VIG.  If it's greater than your \MAX Flesh, your \MAX Flesh is this new value.
    \item Check your Trope, Flavor, or Species and update your character sheet with any new abilities 
  }

  \example {
    Example: Mad Tom (Soldier), Aelfirth (Mystic), and Stump (Pooka) all reach level 3.  Mad Tom has a Grit of 11, Aelfirth has a Grit of 3, and Stump has a Grit of 2.  Mad Tom has a \FLESH of d10, so he rolls 2d10 for his Grit and takes the highest. He gets a 4 and a 7.  Because he's a Soldier he adds his \myital{current} level to the highest die and ends up with a 9.  His new Grit is 20 (11+9). Tom increases his \VIG \DCUP and decides to increase his Presence \DCUP.  He moves his Save vs. Doom up by 1 and updates his sheet with his new \DEED.

    ~\\
    Aelfirth has a \FLESH of d4, so she rolls 2d4 and gets a 2 and a 1.  Her Grit goes from 3 to 5.  She increases her \FOC \DCUP and decides to increase her \DEX \DCUP to counteract her low Flesh.  She decides to move her Save vs. Hexes \DCUP, and updates her sheet with her new Grace (and adds 2 Faith Die).

    ~\\
    Stump has a \FLESH of d6, so he rolls 2d6 and gets a 4 and a 5.  His Grit is now 7. His Presence moves \DCUP, and he decides to move his Talent \DCUP as well.  He moves his Save vs. Doom up 1 also, and updates his sheet with his new Luck Die
  }

}%