% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggAppendix}{%
  \mychapter{Appendices}{appendices}
}

\renewcommand{\yggAppendixText}{%


\mysection{Appendix A: Combat Tables}{appendixa-combat-tables}


\mysubsection{Fumbles}{appendixa-combat-tables-fumbles}

If you fumble, roll on the following table depending on your armor:

  \mytable{X c }{
    \thead{Weight} & \thead{Die}  \\
  }{
    None & d2  \\
    Light & d4  \\
    Medium & d8 \\
    Heavy & d12 \\  
    Shield & +1 to roll \\
    Helmet & +1 to roll \\
  }


If something doesn't apply, move up the chart (that is, things get worse) to the next available effect that works.

\mynumlist {
  \item  You miss spectacularly and everyone laughs at you and now no one will invite you to prom.  Lose 1 Grit on account of the shame.
  \item You miss and lose your grip on your weapon and you're holding it all awkward and things feel weird.  Your next Fight roll is -4
  \item You'll tell everyone that your opponent dodged but really you got all turned around.  Your next Guard roll is -4
  \item You Trip and Fall - you are now Prone.
  \item You Disarm yourself. If it's a Shoot weapon, the bowstring breaks and it'll take Minutes to fix, so let's hope you have an Option B.
  \item If you're wearing a backpack you sever the straps, it splits open, and all the contents spill onto the ground.  Backpack is now useless and everyone can see your weird collection of things you've been stealing
  \item You really overextend yourself, pull a hammy, and mess up your Armor (if you're wearing any).  Make an Armor \UD roll.
  \item (or more) Stop hitting yourself!  Roll damage against Armor (if you've got it) or Flesh.
}


\mysubsection{Wounds}{appendixa-combat-tables-wounds}

A brush with death is not without its cost.  Roll a d3 to determine what kind of wound  you receive:  1) a Physical Wound; 2) a Mental Wound; 3) a Spiritual Wound.  The effects of Wounds are healed by taking a Bivouac unless the damage is permanent (a Beating, Madness, or Life Drain).  Those can only be healed during a \mylink{Vacation}{civilization-vacation}.

Roll a d10 on the appropriate table below


\mysubsection{Physical Wounds}{physical-wounds}

\mynumlist {
  \item  Permanent superficial scar, you say where.
  \item  Broken nose, you can't smell anything and your \MAX Presence is \DCDOWN until fixed
  \item  Ringing ears, Listen checks are at -1
  \item  Crushed your hand, -2 to any \RO tries requiring fine motor coordination
  \item  Pulled a shoulder muscle, -1 Damage (minimum 1)
  \item  Got your bell rung. No effect if you were wearing a helmet. You can't do anything requiring Concentration (including casting some spells).  Your \MAX Awareness is \DCDOWN until fixed.
  \item  Twisted your knee or ankle.  Your \MD is \DCDOWN
  \item  Knocked d3 teeth out. Your \MAX Presence is \DCDOWN permanently.
  \item  Feeling your age.  You are unable to heal Grit.
  \item  Serious Wound. Roll on the \mylink{Beatings}{appendixa-beatings-table} table
}

  \mysubsection{Mental Wounds}{mental-wounds}

  \mynumlist {
    \item Develop a permanent nervous tic, you say what it is
    \item  Brush with insanity - roll your Sanity die.
    \item  You forget how to use one of your Skills (determined randomly)
    \item  Ennui.  \MD is \DCDOWN
    \item  Hysterical Blindness.  You can only see things Close or Nearby.  Shoot and Throw Fight \RO is at -2
    \item  Distracted.  You can't do anything requiring Concentration (including casting some spells).  Your \MAX Awareness is \DCDOWN until fixed.
    \item  Badly shaken. -2 to any \RO tries requiring fine motor coordination
    \item  Susceptible to suggestion - Sleep and Charm Person work on you automatically, and you'll tend to believe anything someone says
    \item  Confidence shaken.  You are unable to heal Grit
    \item  Serious Wound. Roll on the \mylink{Madness! table}{other-stuff-terror-horror-madness}
  }


  \mysubsection{Spiritual Wounds}{spiritual-wounds}

  \mynumlist{
    \item Your brush with death turns your hair permanently white (can't be healed)
    \item  A random Insignificant Item (Arbiter rolls) rolls off somewhere and is permanently lost (can't be found)
    \item  Only saved by luck.  Your \MAX Talent is \DCDOWN until dealt with.
    \item  Marked for death.  Monsters will target you first in Combat
    \item  Empty luck battery.  Automatically take a 1 in any Luck Contests.
    \item  Winds of Doom.  You've only postponed the inevitable.  Your Saves vs. Doom have a -4 penalty
    \item  Arcane target.  Your Save vs. Hexes have a -4 penalty
    \item  Karma extracts a toll - your \MAX Talent is \DCDOWN permanently.
    \item  Unquiet thoughts.  You are unable to heal Grit.
    \item  Serious Wound. Roll on the \mylink{Life Drain}{appendixa-life-drain-table} table
  }


  \cbreak

  \myhighlight{Beatings}{appendixa-beatings-table} 

  \mytable{X c}{
    \thead{} & \thead{}  \\
  }{
    1 & Arm  \\
    2 & Leg \\
    3 & Face \\
    4 & Groin / Genitals \\  
    5 & Back \\
    6 & Neck  \\
    7 & Chest  \\
    8 & Abdomen \\
    9 & Spine \\  
    10 & Head \\
  }

  \mylist {
    \item \mybold{Arm} You've injured your [1-3 left, 4-6 right] 1) Hand; 2) Forearm; 3) Elbow; 4) Bicep; 5) Tricep; 6) Underarm.  Whichever arm got hit is useless - you can't hold anything with it. You can't use 2h weapons.  If it's your "main hand", make your Fight \RO checks at -4.  If you don't know which one is your "main" hand, roll a d6: 1-4 it's your right, 5-6 it's your left.

    \item \mybold{Legs} You've injured your [1-3 left, 4-6 right]  1) Foot; 2) Shin; 3) Calf; 4) Knee; 5) Thigh; 6) Hip  You can't run and can only walk with a limp.  Your \MD drops \DCDOWN x2 (meaning you're immobile if you're wearing heavy armor)
    
    \item \mybold{Face} You've injured your 1) Cheek; 2) Ear; 3) Mouth; 4) Nose; 5) Eye; 6) Jaw.  That's pretty rough to look at.  If you're wearing a helmet, no effect but the helmet is destroyed.  Otherwise, your \MAX Presence drops \DCDOWN x2 permanently. If it was an eye injury, also take -4 to Fight \RO with Throw or Shoot weapons. 

    \item \mybold{Groin / Genitals}  Everyone winces, you drop to the foetal position for Minutes and can't move.  Kids are probably out of the question.  You can't heal any Grit until the Wound is taken care of.

    \item \mybold{Back} You've injured your 1) left upper; 2) right upper; 3) left lower; 4) right lower back!  You can't carry any Significant Items (including armor and weapons)

    \item \mybold{Neck}  You've injured your 1) throat; 2) back of neck; 3) left side of neck; 4) right side of neck; 5) left shoulder; 6) right shoulder. If it's your shoulder, same as "Arm" above.  If it's your throat or neck, you are unable to speak (including cast spells) until the Wound is taken care of.
    
    \item \mybold{Chest}  You've injured your [1-3 left, 4-6 right] chest and ribcage. Any time you do anything strenuous (like Fighting, Guarding, or running away), make a \RS : \VIG try. If you Fail, you take \mylink{The Vapors}{effect-the-vapors}.

    \item \mybold{Abdomen} Take Minutes to stuff your intestine back inside your body.  Any time you do anything strenuous (like Fighting, Guarding, or running away), make a \RS : \VIG try. If you Fail, you immediately begin \mylink{Bleeding}{effect-bleeding}.

    \item \mybold{Spine} You're partially paralyzed and can only crawl.  Treat as if you were permanently \mylink{Prone}{effect-prone}.

    \item \mybold{Head} Helmets save lives - destroy your helmet if you  have one and take no effect.  Otherwise you fall comatose.  Treat as if you had a permanent case of \mylink{The Vapors}{effect-the-vapors}
  }

  \myhighlight{Life Drain}{appendixa-life-drain-table} 

  \mytable{X c }{
    \thead{} & \thead{}  \\
  }{
    1 & Language  \\
    2 & Civilization \\
    3 & Skill \\
    4 & Passion \\  
    5 & Humanity \\
    6 & Allies \\
  }

\mylist {
  \item \mybold{Language} You can on longer speak, read, or write any language.  You can still moan and holler unintelligibly if desired.

  \item \mybold{Civilization} You can no longer use any tools or weapons; you have to perform all actions directly (with the body)

  \item \mybold{Skill}  You've forgotten how to do anything not related to eating, fighting, and sleeping. All of your Skills drop to Untrained.


  \item \mybold{Passion} You become depressed and lethargic, unable to perform any actions during a Vacation (including going Carousing).  During play, any action that would take Minutes or longer of continuous concentration requires a Sanity roll to complete (remember, a Failure requires a roll on the \mylink{Terrifying Tables}{misc-terrifying-tables})

  \item \mybold{Humanity} You become perceptibly but indescribably inhuman.  Animals growl or otherwise act hostile in your presence, and hirelings won't follow you. 

  \item \mybold{Allies} An attendant spirit was stolen from you. Familiars, intelligent weapons, the ability to remember the Forgotten, and relationships with \TheAuthority or Small Gods are all at risk.
}

\newpage


\end{multicols}

\mysection{Appendix B: Random Tables}{appendixb-random-tables}



\mysubsection{Miracle Working}{appendixb-miracle-working-table}

\myital{These are pretty much verbatim from Logan Knight's delightful \href{https://www.lastgaspgrimoire.com/does-this-look-infected/}{Does This Look Infected?}}

If you don't have a Mystic in your party who can feed your Curse to a Hekaphage, then you'll have to make do with cursebreakers, witchfinders, and cunning folk.  The cost is 100 coins and a roll on the table below (feel free to improvise, too!)

  \mytable{l X} {  
  } {

    1 &  While breathing in the fragrant smoke of burning Govora pollen, ingest a pint of pig urine to induce vomiting. Drown a nightingale in the spilled contents of your stomach within the waiting iron urn, then keep the drowned body beneath your bed for three days before throwing it out the East window \\
    2 &  A pregnant rat, teeth pulled and pups moving beneath fat-smeared fur, must be swallowed alive. When it gives birth to its young the affliction will pass onto them before they die and pass through your digestion.\\
    3 &  Your face must be smothered with a duck-down pillow soaked in vinegar and hyena urine. When you finally struggle for breath at the point of collapse the pillow will be removed so that you may be slapped full in the face with a stillborn hound. This will be repeated as many times as necessary. \\
    4 &  Hold six blessed sparrow eggs in your mouth and descend into the Corpusmilch Canal, do not swallow them until you touch the bottom.\\
    5 &  Your body will be smeared with the putrescent black mud of the Nameless Bog. Ingest a small amount, be cautious not to consume too much, and do not bathe until two days have passed.\\
    6 &  Submerge yourself in a copper bath of goat's milk while suckling at the teat of a wetnurse until the malady has passed.\\
    7 &  Swallow a river stone wrapped in maiden's hair. The hair will absorb the affliction and pass from you along with the stone. \\
    8 &  The affliction must be drawn out through the skin. Cupping using the severed horns of a tribe of black goats sacrificed beneath the full moon. \\
    9 &  The afflicted area must be wrapped in dried kelp that was once soaked in the urine of an unfaithful man. The smouldering ashes of a sapling will then be laid upon it until they have burnt through and touched flesh. \\
    10 & Inhale a pinch of blue moss from the silver-gilded goat's head snuff mull and seek the Divine Polycerate Goat in your dream wanderings. Supplicate before him and he may gnaw the affliction from your being. \\
    11 & A candle made from the fat of a drowned man and scented with Spring's first bloom must be sat upon the forehead and allowed to burn down to hard streams of yellow nothing \\
    12 & You must lie within a circle of blessed yellowed candles, with the ashy pollen of the Widow's Blossom dusted upon your face. Throughout the night the affliction will call to you from beyond the waxen circle in voices myriad and sweet. If you resist their call until morning, it will pass. \\
}


\newpage

\begin{multicols}{2}



\mysubsection{Random Treasure}{appendixb-random-treasure}

\mybold{Basic Treasure Table}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Nothing \\
 2 & Mundane Treasure I \\
 3 & Mundane Treasure II \\
 4 & d6 coins \\
 5 & d6x10 coins \\
 6 & Roll on \mybold{Better Treasure Table}
}


\mybold{Better Treasure Table}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Roll on \mybold{Gems} \\
 2 & Roll on \mybold{Jewelry} \\
 3 & Roll on \mybold{Drugs} \\
 4 & Roll on \mybold{Chymistry} \\
 5 & Roll on \mybold{Fetishes} \\
 6 & Roll twice
}

\cbreak\bump


\mybold{Mundane Treasure I} \\~
\myital{Roll 2d6}

\mytable{l X} {
    \thead{} & \thead{} \\
}{
    11 & False Teeth \\
    12 & Obscure treasure map \\
    13 & Love Letter \\
    14 & Small silver knife \\
    15 & Set of rusty keys \\
    16 & Matches \\
    21 & Copper hand mirror \\
    22 & Spikes and a hammer \\
    23 & Syringe (empty) \\
    24 & Leather work gloves \\
    25 & Flask of oil \\
    26 & Flask of liquor \\
    31 & Chalk \\
    32 & 3 beans \\
    33 & Mousetrap \\
    34 & A few wooden puzzle pieces \\
    35 & A carved pipe \\
    36 & A rabbit's foot \\
    41 & A set of dice \\
    42 & Brass ring \\
    43 & 3 playing cards (Aces) \\
    44 & A children's toy top \\
    45 & Small bone statues \\
    46 & Blue quartz crystal \\
    51 & A pair of purple ladies gloves \\
    52 & A bag of teeth \\
    53 & A few bones \\
    54 & A comb \\
    55 & A hankerchief \\
    56 & Small petrified head \\
    61 & A few round stones \\
    62 & A wool cap \\
    63 & A pair of undarned socks \\
    64 & Small bottle of urine \\
    65 & A duck bill \\
    66 & A morbid shopping list (body parts) \\
}

\newpage


\mybold{Mundane Treasure II} \\~
\myital{Roll 2d6}

\mytable{l X} {
    \thead{} & \thead{} \\
}{
    11 & A sash with a skull embroidered on it \\
    12 & A small glowing stone (candlelight) \\
    13 & A box of moss \\
    14 & A severed finger \\
    15 & A fishing hook and some line \\
    16 & A belt buckle \\
    21 & A recipe for mead \\
    22 & A hand paper fan \\
    23 & A pair of rose colored glasses \\
    24 & A map to an area of the Veins \\
    25 & A small metal sundial \\
    26 & A hand drawn picture of a cave entrance \\
    31 & A candle \\
    32 & A lumb of obsidian \\
    33 & A magnet \\
    34 & A bit of lace \\
    35 & A list of names \\
    36 & A silk shift \\
    41 & An erotic drawing \\
    42 & A bottle of regular glue \\
    43 & A chess piece \\
    44 & Fake ID \\
    45 & A women's shift \\
    46 & A handful of seeds \\
    51 & A pouch of salt \\
    52 & A polished glass eyeball \\
    53 & Wooden carving of an elephant \\
    54 & Penknife \\
    55 & A bottle of honey in the shape of a bear \\
    56 & An oily rag \\
    61 & A padlock and key \\
    62 & An empty leather wallet \\
    63 & A razor \\
    64 & Sea glass \\
    65 & Long rainbow scarf \\
    66 & Heart shaped iron locket \\
}

\cbreak


\mybold{Gems}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Roll on \mybold{Poor Gems} \\
 2 & Roll on \mybold{Valuable Gems} \\
 3 & Roll on \mybold{Costly Gems} \\
 4 & Roll on \mybold{Poor Gems} d6 times \\
 5 & Roll on \mybold{Valuable Gems} d6 times \\
 6 & Roll on \mybold{Costly Gems} d6 times
}


\mybold{Poor Gems (d6x10 Iron)}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Amber \\
 2 & Amethyst \\
 3 & Coral \\
 4 & Garnet \\
 5 & Jade \\
 6 & Pearl
}


\mybold{Valuable Gems (d6x10 Silver)}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Aquamarine \\
 2 & Garnet \\
 3 & Black Pearl \\
 4 & Topaz \\
 5 & Alexandrite \\
 6 & Spinel
}

\mybold{Costly Gems (d6x10 Gold)}

\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1 & Diamond \\
 2 & Emerald \\
 3 & Ruby \\
 4 & Sapphire \\
 5 & Opal \\
 6 & Jacinth
}

\newpage 

\mybold{Jewelry}


\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1 & Necklace \\
 2 & Ring \\
 3 & Earring \\
 4 & Brooch \\
 5 & Bracelet \\
 6 & Circlet \\
}



\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1 & Roll on \mybold{Poor Jewelry} \\
 2 & Roll on \mybold{Valuable Jewelry} \\
 3 & Roll on \mybold{Costly Jewelry} \\
 4 & Incorporates a \mybold{Poor Gem}. Roll on that table. Roll again on this table. \\
 5 & Incorporates a \mybold{Valuable Gem}. Roll on that table.  Roll again on this table. \\
 6 & Incorporates a \mybold{Costly Gem}. Roll on that table.  Roll again on this table. \\
}

\mybold{Poor Jewelry (d6x10 Iron)}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Bronze \\
 2 & Tin \\
 3 & Copper \\
 4 & Iron  \\
 5 & Bone \\
 6 & Glass
}

\mybold{Valuable Jewelry (d6x10 Silver)}

\mytable{l X}{
 \thead{d6} & \thead{}  \\
}{
 1 & Steel \\
 2 &  Ivory \\
 3 &  Stoneshape \\
 4 &  Shroomfoil \\
 5 &  Silver \\
 6 &  Brass
}

\mybold{Costly Jewelry (d6x10 Gold)}

\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1 &  Gold \\
 2 &  Platinum \\
 3 &  Orichalcum \\
 4 &  Occultum \\
 5 &  Moon-bronze \\
 6 & Mithril
}

\mybold{Fetishes}

Roll randomly on Wizardry Arcana in Bell, Book, and Candle.  d4 \UD


\mybold{Drugs}

\mytable{l X X}{
 \thead{d6} & \thead{} & \thead{\UD}  \\
}{
 1 &  Pipeweed & d10  \\
 2 &  Smokes & d10  \\
 3 &  Weed of Hasheeshian & d10  \\
 4 &  Woad & d8  \\
 5 &  Blackthroat & d4  \\
 6 & Locus & d4
}


\mybold{Chymicals}

\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1 &  Roll on \mybold{Toxins} \\
 2 &  Roll on \mybold{Acids} \\
 3 &  Random Tonic \\
 4 &  Random Powder \\
 5 &  Random Sera \\
 6 & Random Ungeant 
}

\myital{See Bell, Book, and Candle for details on Chymistry}

\mybold{Toxins}

\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1-3 &  1 Dose Iron Toxin \\
 4-5 &  1 Dose Silver Toxin \\
 6 &  1 Dose Gold Toxin \\
}

\mybold{Acids}

\mytable{l X }{
 \thead{d6} & \thead{}  \\
}{
 1-3 &  1 Dose Iron Acid \\
 4-5 &  1 Dose Silver Acid \\
 6 &  1 Dose Gold Acid \\
}





\newpage



\end{multicols}

\mysubsection{Adventurer Occupations}{appendixb-occupations}

\myital{d6:  1-3 Country; 4-5 Village; 6 City}

  \mytable{X X X X}{
    \thead{d30} & \thead{Country} & \thead{Village} &  \thead{City} \\
  }{
    1 & Hobo & Hobo & Hobo\\
    2 & Drunkard / Addict & Drunkard /Addict & Drunkard /Addict\\
    3 & Orphan & Orphan & Orphan\\
    4 & Gypsy & Farmhand & Pickpocket\\
    5 & Ditchdigger & Farmer & Beggar\\
    6 & Serf & Miner & Mudlark\\
    7 & Poacher & Miller & Sewerjack\\
    8 & Herder & Smith & Gongfarmer\\
    9 & Mushroom Farmer & Grocer & Chimneysweep\\
    10 & Gatherer & Fishmonger & Prostitute\\
    11 & Hunter/Trapper & Baker & Bawd\\
    12 & Fisherman &Alewife /Barkeep & Servingwench\\
    13 & Woodcutter & Porter & Alewife /Barkeep\\
    14 & Butcher & Hayward & Ostler\\
    15 & Prospector & Weaver & Porter\\
    16 & Molecatcher & Tanner & Apprentice\\
    17 & Guide & Cobbler & Caravan Guard\\
    18 & Linkboy & Tailor & Nightwatchman\\
    19 & Alewife/Barkeep & Wainwright & Sailor/Dockhand\\
    20 & Prostitute & Servingwench & Crimp\\
    21 & Servingwench & Prostitute & Cultist\\
    22 & Escaped Criminal/Slave & Brewer & Executioner\\
    23 & Cultist & Cheesemaker & Gambler\\
    24 & Midwife/Medicine Man & Ranchero & Haberdasher\\
    25 & Ferryman & Cultist & Goliard\\
    26 & Graverobber & Mummer & Teamster\\
    27 & Village Elder & Guard & Cartographer\\
    28 & Mad Scientist & Trader & Esoteric Scholar\\
    29 & Retired Explorer & Fence & Retired Explorer\\
    30 & Incognito Nobility & Retired Explorer & Minor Nobility\\
  }


  \newpage

\mysubsection{Random Items}{appendixb-random-items}

\mytable{l X}{
 \thead{d100} & \thead{Loot}  \\
}{
   1 & a crumpled pack of Smokes \\
   2 & a wooden toy soldier \\
   3 & a dented locket \\
   4 & some kind of jerky \\
   5 & a mummified finger \\
   6 & a weird looking rock \\
   7 & a small leather bag of dust you found \\
   8 & a small wooden carving of a weird humanoid \\
   9 & a stone that looks like an eye \\
   10 & 2 lobster claws made from basalt \\
   11 & a corn-cob pipe \\
   12 & just enough whiskey for a half-sip \\
   13 & a wooden leg (you have both your legs) \\
   14 & 8 really fancy buttons \\
   15 & a wedding dress \\
   16 & a small folding knife \\
   17 & a silver spoon (1ag) \\
   18 & a broken syringe \\
   19 & 2 small steel balls in a box \\
   20 & a set of pins \\
   21 & an embroidered hankerchief \\
   22 & a shred of blanket (your "binky") \\
   23 & a small guitar \\
   24 & a small bag of molars (human) \\
   25 & a wooden checkers set \\
   26 & a pack of cards \\
   27 & a pack of marked cards \\
   28 & a pair of bone dice \\
   29 & a pair of loaded dice \\
   30 & a 10cm square piece of shiny metal (unknown) \\
   31 & an empty bottle of perfume \\
   32 & a single white glove \\
   33 & a top hat \\
   34 & 5 dead snakes \\
   35 & a copper bowl \\
   36 & 4 squirrel pelts \\
   37 & a cane topped with a duck head carving \\
   38 & a monocle \\
   39 & a broken pocketwatch \\
   40 & a dehydrated tentacle \\

  }


  \mytable{l X}{
   \thead{d100} & \thead{Loot}  \\
  }{  

   41 & a map printed on skin \\
   42 & a package of pink salt crystals \\
   43 & a pair of black smoked goggles \\
   44 & a human femur painted red \\
   45 & a nose ring worth d6 fe \\
   46 & 300 grams of bee's wax \\
   47 & a ream of vellum sheets \\
   48 & 6 pieces of chalk \\
   49 & a silk shift \\
   50 & a glowing moth in a tiny cage \\  
   51 & a tube of chapstick \\
   52 & a goblin key that will lock any door once \\
   53 & a set of agate prayer beads \\
   54 & a needle and thread \\
   55 & a piece of smoked fish \\
   56 & a comb and hair wax \\
   57 & a pillbox containing 4 unidentified white pills \\
   58 & a small prayer book to a Small God you've never heard of \\
   59 & a foil packet with a circular buldge in it \\
   60 & a corkscrew \\
   61 & a postcard from your mother or father, asking you to come home \\
   62 & half a copper key \\
   63 & a roll of twine \\
   64 & d6 purses, emptied of anything valuable \\
   65 & 10 dried ears threaded on a string \\
   66 & 8 pieces of candy \\
   67 & a miniature flail with five heads that you can only wield with two fingers \\
   68 & a braid of blond human hair \\
   69 & an eyepatch \\
   70 & a pewter beer stein \\
   71 & a taxidermied bat stuffed with lavendar \\
   72 & 6 losing betting tickets for a terrier ratkilling arena \\
   73 & an uncomfortably large bottle of human blood \\
   74 & d6 silver arrowheads \\
   75 & a ninja star \\
   76 & a crystal prism \\
   77 & 3 links of chain \\
   78 & a glass eye that blinks \\
   79 & the \myital{perfect} skipping stone \\
   80 & a folded piece of parchment warning citizens of pick pockets. \\
   81 & a sky blue baby's bow \\
   82 & a tiny nugget of fool's gold, worthless \\
   83 & an invitation to somewhere \\
   84 & 1m of rope \\
   85 & a "one year sober!" chip \\
   86 & a big pouch of fingernail clippings \\
   87 & so much lint \\
   88 & a chipped "world's best boss" mug \\
   89 & an incomprehensible book about toadstools \\
   }
  \mytable{l X}{
   \thead{d100} & \thead{Loot}  \\
  }{  
   90 & a fur hat \\
   91 & d8 shrunken heads \\
   92 & a rulebook for a game you've never heard of \\
   93 & a urinal cake, but you don't know it's a urinal cake \\
   94 & a jar of cherries in brandy (flammable) \\
   95 & a pair of chopsticks \\
   96 & a totally sweet small painting of a wizard \\
   97 & a clay ashtray made by a child \\
   98 & a lace veil \\
   99 & a really great pair of socks \\
   100 & you pick (run it past the Arbiter) \\
}



\mysection{Appendix C: The Math}{appendixc-the-math}

\begin{multicols}{2}\raggedbottom

\mysubsection{Weird Dice}{the-math-weird-dice}

There are some additional dice that ToY uses (the d24, the d16 and the d3) that you might not have.
\mybullet {
  \item d24 - roll a d6.  On a 1-3 roll a d12.  On a 4-6 roll a d12+12
  \item d16 - roll a d6. On a 1-3 roll a d8. On a 4-6, roll a d8+8.
  \item d3 - roll a  d6.  A 1-2 is a 1, a 3-4 is a 2, and a 5-6 is a 3
}


\mysubsection{Static Dice Odds}{static-dice-odds}

\myital{n.b. For every +1 you add to your roll, you increase your odds by an average of 4\%}

\cbreak


  \mytable{l X}{
   \thead{Dice} & \thead{\RO Odds}  \\
  }{  
    d24+d24  & A little better than 2-in-3\\
    d24+d20& A little worse than 2-in-3 \\
    d24+d16  & Better than 50/50 \\
    d24+d12  & A little worse than 50/50 \\
    d24+d10  & Worse than 50/50 \\
    d24+d8  & Better than 1-in-3\\
    d24+d6& A little better than 1-in-3 \\
    d24+d4  & A little worse than 1-in-3 \\
    d24+d3  & Worse than 1-in-3 \\
    d24+d2  & A little better than 1-in-4 \\
    d20+d20  & Better than 50/50\\
    d20+d16  &   A little worse than 50/50\\
    d20+d12  &A little better than 1-in-3 \\
    d20+d10  & A little worse than 1-in-3     \\
    d20+d8  & A little better than 1-in-4\\
    d20+d6& A little worse than 1-in-4 \\
    d20+d4  & A little better than 1-in-6\\
    d20+d3  & A little worse than 1-in-6 \\
    d20+d2  & 1-in-8 \\
    d16+d16  & A little better than 1-in-3\\
    d16+d12  & A little worse than 1-in-4\\
    d16+d10  & A little better than 1-in-6  \\
    d16+d8  & A little better than 1-in-10 \\
    d16+d6  & A little better than 1-in-20\\
    d16+d4  & About 1\%\\
    d12+d12&  1-in-10 \\
    d12+d10  & 1-in-20  \\
    d12+d8  & About 1\%\\
    d10+d10  & About 1\% \\
  }

\mysubsection{Mishap, Calamity, and Ruin Odds}{mishap-calamity-ruin-odds}
  \mytable{X l l l }{
   \thead{Dice} & \thead{Mishap (3)} & \thead{Calamity (4)} & \thead{Ruin (5+)}  \\
  }{
     3 & 1/36 & x & x \\
     4 & 1-in-10 & <1\% & x \\
     5 & 1-in-5& 1-in-50 & <1\% \\
     6 & 2-in-6 & 1-in-20 & <1\% \\
     7 & 3-in-6 & 1-in-10 & <1\% \\
     8 & 3-in-6 & 1-in-6 & approx. 3\% \\
     9 & 3-in-6 & 1-in-4 & approx. 5\% \\
     10 & 3-in-6 & 2-in-6 & approx. 8\% \\
  }


\mysubsection{Usage Die Averages}{dice-average-ud}
  \mytable{X l l}{
   \thead{Die} & \thead{Avg Uses} & \thead{Progression}  \\
  }{ 
    d3&1&1\\
    d4&2&2\\
    d6&5&3\\
    d8&9&4\\
    d10&14&5\\
    d12&20&6\\
    d16&28&8\\
    d20&38&10\\
  }

  \cbreak

\mysubsection{Exploding Dice Mean Damage}{dice-exploding-mean-damage}
  \mytable{X l l l}{
   \thead{Die} & \thead{Normal} & \thead{Exploding} & \thead{\% Diff} \\
  }{ 
    d4&2.5&3.335492&+25\% \\
    d6&3.5&4.205907&+17\% \\
    d8&4.5&5.137152&+12\% \\
    d10&5.5&6.108062&+10\% \\
  }


} %end
