% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggFae}{%
  \mychapter{Fae}{fae}
}

\renewcommand{\yggFaeText}{%
  
  \flavor{And within the dark circle in which the Freer stood making his curses were no unhallowed things, nor were there strangenesses such as come of night, nor whispers from unknown voices, nor sounds of any music blowing here from no haunts of men; but all was orderly and seemly there and no mysteries troubled the quiet except such as have been justly allowed to man.  And beyond that circle whence so much was beaten back by the bright vehemence of the good man's curses, the will-o'-the-wisps rioted, and many a strangeness that poured in that night from Elfland, and goblins held high holiday. For word was gone forth in Elfland that pleasant folk had now their dwelling in Erl; and many a thing of fable, many a monster of myth, had crept through that border of twilight and had come into Erl to see. And the light and false but friendly will-o'-the-wisps danced in the haunted air and made them welcome.  \Tilde Lord Dunsany }

  The non-mortal Fae races are \myital{phenomenal} - they lack an undefinable essence, since they are born of Magick and Chaos (though they stand outside of it in the same way a fish swimming in a stream is both a part of and separate from the water). The Fae exist so long as Magick exists. 

  The existence of the Fae defies the doctrine of the The Authority \TheAuthority followed by the Mortal races; for this reason the Fae are considered unholy, anathema - Unhallowed. By the Grace of the The Authority \TheAuthority, Mortal \mylink{Mystics}{flavor-mystic} can banish the Unhallowed from their midst.

  \mysubsection{Fae Adventurers}{fae-adventurers}

  Game-wise, Fae adventurers in the story you're creating with the Arbiter are of a distinct Species separate from "human".  Unlike Mortals, the Fae are governed by \mylink{Intangible Stats}{intangible-stats}.  There are thousands of species on the moons of Tartarus, but the four major Species are:
  
  \cbreak

  \mylist {
    \item \mybold{\mylink{The Pooka}{species-pooka}}  Members of the Unseelie Court, these drug-crazed rabbit creatures are widely sought as adventuring partners for their uncanny abilities in bringing good fortune to any endeavor.  Pooka have a Luck Die, similar to Knaves, but can use this \UD to affect their Ally's rolls as well their own.  They are governed by \mylink{Presence}{intangible-stats-presence}.

    \item \mybold{\mylink{The Myrkálfar}{species-murk}}  One of the Rom, the "Murks" (as they are more commonly known) are the escaped slaves of the violent and hateful races of the Veins of the Earth.  The Myrkálfar are fallen gods who are forced to walk among Mortals, forever searching for the way home.  They are governed by \mylink{Sanity}{intangible-stats-sanity}.

    \item \mybold{\mylink{The Spriggan}{species-spriggan}} Another of the Rom, ex-vassals of the King of Elfland, wandering the Mortal lands trying to find the bright line of Elfland again.  They are able to summon and control The Forgotten - animals, demons, and forgotten gods - and forge legendary magical blades.  They are governed by \mylink{Awareness}{intangible-stats-awareness}.
    
    \item \mybold{\mylink{The Night Children}{species-night-child}}   Member of the Unseelie Court, Night Children are Unhallowed Fae and raw chaos incarnate, taking dozens if not hundreds of different forms.  Creating a Night Child is an entirely random affair, with interesting and powerful results. They are governed by \mylink{Talent}{intangible-stats-talent}.
  }


  \mysubsection{Fae Origins}{fae-origins}

  \myital{Note:  These are just suggestions - feel free to buck the rules!}

  \mybullet {
    \item If you are a \mylink{Pooka}{species-pooka}, you can hail from any \mylink{Small, Medium, or Large}{settlements} in Acheron.  Pooka are commonly sailors (they bring good luck), jesters, scouts, and tavern keepers - and rarely gamblers, since no one will play with them
    \item If you are a \mylink{Spriggan}{species-spriggan}, you originally hailed from Elfland - but can live in or near any town or city bordering the Great Wood.
    \item If you are a \mylink{Murk}{species-murk}, you originally hailed from the \mylink{Veins of the Earth}{murk-veins-of-the-earth} - but you can live in any town or city on the frontiers.
    \item If you are a \mylink{Night Child}{species-night-child}, you hail from any \mylink{Medium or Large}{settlements} in Acheron, or somewhere far away from \myital{any} civilization
  }



  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  POOKA %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  

  \mysection{Species: Pooka}{species-pooka}

  \mysubsection{Base Stats}{pooka-base-stats}
  \FLESH d4 \hfill Primary Stat: Presence
  
  \mytable{X r}{
    \thead{Level} & \thead{Luck Die} \\
  }{
    1 & d3 \UD \\
    2-3 & d4 \UD \\
    4-5 & d6 \UD \\
    6-7 & d8 \UD \\
    8 & d10 \UD \\
    9 & d12 \UD \\
  }

  \flavor{In the mists before the Beginning, Fate and Chance cast lots to decide whose the game should be; and he that won strode through the mists to \TheAuthority and said: "Now make Gods for Me, for I have won the cast and the Game is to be Mine."  Who it was that won the cast, and whether it was Fate or whether Chance that went through the mists before the Beginning to \TheAuthority - none knoweth. \Tilde Lord Dunsany}

  You do not believe in Fate - it's a made up idea, created by people who are afraid of their tiny planet plunging through the Void with no rhyme or reason, only raw, horrible, gorgeous Chaos.  Chance governs the Totality - Chance and no other. This is reprehensible to the Authority, who seeks to keep the secret of the game of lots for himself.  But you are proof that it is Chance that was victorious, and for this you are cursed, and marked Unhallowed.  

  \example{
    Pooka stand scarcely 1m tall, with the head and feet of a rabbit, pig, goat, or toad.  They are gregarious, sly, and always at the point of laughing.  Pooka love to be around people, and it's not uncommon to find them on ships (where they're thought to be good luck), tending bars (if they don't drink away their profits), or with gypsy troupes.  They excel at dancing and singing, and take every opportunity they can to do both. \href{https://www.pinterest.com/gadhra/the-totality-of-ygg-beta-rules/pooka}{Visual reference}
  }

  \mysubsection{Modifications}{pooka-modifications}

  \mybold{Small Size}
  You stand only 1m tall.  The number of Significant Items you can carry is -2. If you wear armor, you can only wear armor for "little people" (child-sized).  You cannot wield 2-handed weapons.

  \mybold{Unhallowed}
  You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"

  \mybold{Life of the Party}\
  Your Presence starts at \DCUP x2.  Add your \LVL to any rolls involving Presence (though the \UD still moves \DCDOWN on a natural 1 or 2)


  \mysubsection{Enhancements}{pooka-enhancements}

  \mybold{Party Hearty}
  For any narcotics you take, (a) the \UD only moves \DCDOWN if you roll a 1, (b) you add your \LVL to your \mylink{Addiction}{gear-narcotics-addiction} roll, and (c) if you \mylink{Overdose}{gear-narcotics-overdose}, you don't have to roll a \mylink{Save vs. Toxins}{saves} (nothing happens except you wasted some drugs).  When you take a Sojourn or Sabbatical, you have a 2-in-6 chance of obtaining \myital{any} \mylink{Common Narcotic}{gear-narcotics} for free (even Narcotics that would normally not be available, like Black Lotus in a Small town)

  \mybold{Apotropaic}
  Your presence in a party nullifies any effects of a Witch's Jinx\footnote{See Bell, Book, and Candle}.  If you're taking a \mylink{Bivouac}{combat-resting}, there is no chance of wandering Monsters. Buildings where you are sleeping are warded from casual attack (meaning the building would be spared in a riot, for example). 

  \mybold{Hype Man}
  During a \mylink{Breather}{combat-resting}, you can roll a number of d6 equal to your \LVL and heal \SUM Grit to you or your Allies divvied up any way you want.  

  \mybold{Wired}
  You cannot be \mylink{Surprised}{combat-surprise} (including the Drop) and you always win \mylink{Init}{combat-init}.  You are immune to Sleep.

  \mybold{Luck Battery}
  You have a Luck \UD, similar to \mylink{Knaves}{trope-knave}, and you can use it to help other Allies (but not yourself).  You can roll this Luck \UD at any time to affect someone's \RO or \RB attempt, or to give them a 6-in-6 on a single Save roll.  You can wait until after they roll to use this ability, but you can only roll once per \RO or \RB attempt.

  \mybold{Best. Night. EVAR!!}
  People who hang out with you have a pretty great time.  You increase everyone's \mylink{Carousing}{misc-carousing} die by \DCUP (and earn 10\% of the Carousing xp of whoever you party with as well). Anyone who doesn't carouse with you has to hear about how awesome the night was the entire next day.

  \mybold{Optional: You My Boy Blue!}
  Pooka love people, and it's not uncommon for them to "bond" with a person they party with.  After you go \mylink{Carousing}{misc-carousing} with others, pick one of the people you caroused with. You are now "bonded" to that person.  Until the next time you go Carousing, you'll favor that person over the others. If there's any extra \mylink{Grit}{combat-flesh-grit} left to distribute, you'll pick them; if there's an extra share of treasure, you'll argue for that person to get it; if you have extra narcotics, you'll give them to that person.  Next time you go Carousing, pick another person randomly ...

  \mysubsection{Level Bonus}{pooka-bonus}
  \mybullet {
    \item \mybold{Level 3:}   Once per \mylink{Session}{time-session}, you can do 1 of the following:  (a) win any Luck contest; (b) win any game of chance; (c) find extra narcotics just lying around (d3 \UD of any narcotic you want - if you don't use it before the next Session, it gets lost or evaporates or whatever); (d) regain 1 Flesh (enough to bring you off Death's Door)
    \item \mybold{Level 5:}   Three times per \mylink{Adventure}{time-adventure}, you can host a Rager during a \mylink{Bivouac}{combat-resting}.  Every person who participates gets all of the benefits of taking a Sojourn (though they can't go Carousing). The next day everyone has make an \RS : \VIG. If they fail they are \mylink{Hung Over}{effect-hung-over}.
    \item \mybold{Level 7:}   You are immune to Toxins, Curses, and Diseases of all sorts.

  }

  \mysubsection{Professional Gear}{pooka-gear}
  In addition to your \mylink{Starting Gear}{starting-gear}, you start with a full \UD of any narcotic they choose and either (a) or (b):

  \mybullet {
    \item \mybold{(A)}  a dagger, a tiki mug, a pair of silk underwear, a parasol, a mirror, a deck of cards, and a straw
    \item \mybold{(B)}  a hand axe, a book of instructions for making mixed drinks, a pair of sunglasses, a deflated ball, two dice, and a small jar of lubricant
  }  

  \newpage
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  SPRIGGAN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  


  \mysection{Species: Spriggan}{species-spriggan}

  \mysubsection{Base Stats}{spriggan-base-stats}
  \FLESH d6 \hfill Primary Stat: Awareness
  
  \mytable{X r}{
    \thead{Level} & \thead{Remembrance Die} \\
  }{
    1 & 1d6 \POOL \\
    2-3 & 3d6 \POOL \\
    4-5 & 5d6 \POOL \\
    6-7 & 7d6 \POOL \\
    8 & 9d6 \POOL \\
    9 & 12d6 \POOL \\
  }


  \flavor{"Is it not enough?" he said in his strange rich magical voice, and pointed across his wide lands with the fingers that summoned wonder. ~\\ ~\\ She sighed: it was not enough. \Tilde Lord Dunsany}

  You hail from Elfland, beyond the reach of the Hound of Sish.  Like your brothers and sisters the Myrkálfar you are the Nomadic People, the Rom - cursed with curiosity and infected with the fire that burns in the hearts of the Hallowed to know more, to see the passage of time, and to breathe the air of decay.  All it cost was your soul.  

  You cannot find your way home again, for the bright line between this world and Elfland ebbs forever before you.  Wherever you are is where Elfland cannot be.

  Occasionally you might find a Spriggan who did not leave Elfland voluntarily - cast out by the King for crimes against Himself or His kingdom.  These Spriggan are dangerous to the extreme, for they have had their very soul stripped from them - sentenced to death, but only by their own hand.  

  Your bloodline allows you to strike bargains with the lowest of the Small Gods, the Forgotten who stand at the threshold of the Void.  The fear of oblivion dominates every desire and scheme of these sanguinary spirits.  You steal them away from the doorway of Nothingness and by Remembering them, allow them to touch reality once again.  In Remembering, you allow their souls to mingle inside of you, and sing through you - so that in the never-ending ache of Acheron you might, for a moment, remember the feel of the heat of Elfin hearths and the smell of the lavender fields you dream of.  

  But you never do.   

  \example{
    Tall and lithe, often standing over 2m, the Spriggan are ethereal in appearance, with leaf-shaped ears, long fingers, and gaunt faces vaguely reminiscent of deer or goats.  Older Spriggan often appear cadaverous - while they cannot die from old age, their bodies begin to rot outside of the realm of Elfland (though this has no appreciable effect on their physical power).  Their skin and eye color is as varied as the Mortal races, and from a distance they might pass for human - were it not for the horns.  Some sport small, barely noticeable stubs while others sprout deer antlers, curling ram's horns, or tree branches.  It is not uncommon for birds to roost in a Spriggan's horns if they are well developed enough \href{https://www.pinterest.com/gadhra/the-totality-of-ygg-beta-rules/spriggan/}{Visual reference}
  }

  \mysubsection{Modifications}{spriggan-modifications}

  \mybold{Iron allergy}
  You are allergic to iron.  If you touch iron it will deal 1 Flesh damage to you every Moment.  Iron weapons do an extra 2 points of damage if they strike Flesh

  \mybold{Second Sight}
  Your Awareness starts at \DCUP x2. You cannot be Surprised (including the Drop) and you can see hidden and Invisible creatures.  Add your \LVL to any rolls involving Awareness (though the \UD still moves \DCDOWN on a natural 1 or 2)

  \mybold{The Fields We Know}
  You have left Elfland, but you still have some memory of green things and fell beasts.  Your Skill: Bushcraft and Skill: Lore start at 2-in-6.

  \mybold{Tongues of the Forgotten}
  You know how to speak Archaic, Fiendish, OR Seraphic (your choice), in addition to any other languages you might know.

  \mysubsection{Enhancements}{spriggan-enhancements}

  \mybold{The Hound of Sish}
  You are untouched by time, the last remnants of godhood.  You are immune to aging.

  \mybold{Remember the Forgotten}
  Spriggan are able to summon and command the Forgotten - the Obliterated and the Abandoned.  Every level (including the first) they may automatically learn the True Name of one of the Abandoned (this is in addition to learning True Names with the help of a Sorcerer's Etymologia). 

  \mybold{THIS you can trust}
  Spriggan are able to create Magic Swords (and other weapons).  They know if something is magical by touch.

  \mybold{Optional: Antlers}
  Tree branches like antlers grow from your head.  Birds often roost there - and if they do, you can speak with them.  You can't wear helmets or use a bow.  You can't attack with your antlers, but you can sacrifice them for the same effect as wearing a helmet. Antlers will regrow in Weeks.

  \mysubsection{Level Bonus}{spriggan-bonus}
  \mybullet {
    \item \mybold{Level 3:}   Through constant training and study, you can now speak \mybold{all}  of the Languages of the Forgotten (Archaic, Fiendish, and Seraphic)
    \item \mybold{Level 5:}    Once per Session, you can touch as many iron weapons you wish and make them magical for 1 Minute.  Each weapon you touch will deal 1 Flesh damage to you.  The weapon will stay enchanted for Hours.  The weapon has no additional characteristics, but can hit Monsters only affected by Magic.
    \item \mybold{Level 7:}   Choose one of the Forgotten whose True Name you know.  They are now bound to you permanently, as if they were a henchman or hireling. They will never be unsummoned or summoned by another, cost no Remembrance dice to keep or control, and are unswervingly loyal and treat you as a Small God.  When you reach level 9, you can choose to sacrifice them - through this haruspexy, you can divine the paths that will lead you back to Elfland (but will retire your character).
  }

  \mysubsection{Professional Gear}{spriggan-gear}
  In addition to your \mylink{Starting Gear}{starting-gear}, you start with the True Name of one of the Forgotten and either (a) or (b):

  \mybullet {
    \item \mybold{(A)}  a longsword, frayed white robes, a small block of salt (for licking), a pouch of birdseed, and a candle with one of the Forgotten painted on the side
    \item \mybold{(B)}  stitched hides (Light armor), a spear, a pouch of tobacco, a wallet of dried tobacco leaves, matches, and a pouch with 3 dead mice
  }  

  \newpage
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  MURKS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \mysection{Species: Myrkálfar}{species-murk}

  \mysubsection{Base Stats}{murks-base-stats}
  \FLESH d8 \hfill Primary Stat: Sanity

  \myital{The Murks are escaped convicts from one of the Empires of the Veins of the Earth.  Roll a d4 to see which Empire you have escaped from:}
  \mytable{X l}{
    \thead{d4} & \thead{Culture} \\
  }{
    1 & The Deep Janeen \\
    2 & The Ælf-Adal \\
    3 & The Dvargir \\
    4 & the dErO \\
  }

  \flavor{Once the gods walked upon Earth as men walk and spake with their mouths like Men. That was in Wornath-Mavai ... a garden fairer than all the gardens upon Earth. Kib was propitious, and Mung raised not his hand against it, neither did Sish assail it with his hours... \Tilde Lord Dunsany}

  Wornath-Mavai. Svartalfheim. The Glorious Undergarden, beauty beyond measure, Paradise beneath the Mountains, Home to the Myrkálfar, the people beyond Time, who live only for the now.

  Like your brothers and sisters the Spriggan, you were cursed with curiosity, and wondered what was outside of Svartalfheim.  Further and further did you adventure beyond the borders of Svartalfheim until, one day, you were unable to find your way back.  You are now one of the Nomadic People, the Rom.

  Outside of Svartalfheim you were almost immediately enslaved by one of the underworld Empires, for they take great delight in subjugating gods to work for them.  But the burning desire to be free never left you. Almost all Myrkálfar attempt to escape their masters.  Most are killed trying to escape, ending their torment, but some make it out and make their way to the surface.  

  Myrkálfar often act as guides in the Veins, and as such many Mortal races feel that "Murks" are desperate to find their way back again. But the truth is that you can't go back to the point before you knew of the world outside of Svartalfheim.  You have eaten from the tree of knowledge and have been cast out of Eden.  You can never go home again

  \example{
    Murks are tall and thin - like their overworld brethren the Spriggan - but a little shorter, standing less than 2m tall.  Their faces are human-like and their eyes and pupils are white, but glow golden or red in the dark.  Though they seem to care little for fashion, they are always effortlessly well-dressed in black, white, or gray.  Their captors often heavily scar their faces and bodies; they sometimes wear masks in addition to broken manacles or collars. \\ They care nothing for the things that bring joy in life, care nothing for wine or song or money.  They care only about their freedom.  It is the thing that the Authority steals from the Mortal races - the right to ask questions, to go where you desire and do what you want.  They will not allow their freedom to be willingly taken away by anyone, and they will kill to defend both their freedom and the freedom of others. \href{https://www.pinterest.com/gadhra/the-totality-of-ygg-beta-rules/murk}{Visual reference}
  }

  \mysubsection{Modifications}{murk-modifications}

  \mybold{Unafraid}  
  You've seen enough shit that it doesn't affect you anymore.  You're immune to Fear effects (including the Rapture), and your Sanity starts at \DCUP x2.  Add your \LVL to any rolls involving Sanity (though the \UD still moves \DCDOWN on a natural 1 or 2)

  \mybold{Dark Sight}
  You have Dark Sight, giving you normal vision in darkness (but a penalty in sunlight)

  \mybold{Silent Speech}
  You know the Silent Speech, the language of stones and rocks and the trade speech of the \mylink{Veins of the Earth}{murk-veins-of-the-earth}.  You can use this language to speak with stones. They can tell you what has touched them and what is under or behind them.  This makes it almost impossible to get lost underground. They're not great with time though ...

  \mybold{Metal Empathy}
  You can smell any metal you choose (gold, silver, iron, etc) up to 1m away.  Metal weapons do -2 damage per die (minimum 1) to you.  

  \mybold{Veins Lore}
  You have an additional skill of "Veins Lore" that starts at 1-in-6. 


  \mysubsection{Enhancements}{murk-enhancements}

  \mybold{Mountaineer}
  When climbing anything made of stone, you know the \mylink{Whisper:Monkeys' Paws}{knave-whisper-monkeys-paws} as if you had a \KNAVE of d8 (you can speak to the stones to find the best handholds, etc)

  \mybold{The Hound of Sish}
  You are untouched by Time, the last remnants of godhood.  You are immune to aging.

  \mybold{Fate's Hand}
  You can improve your Flawed Save instead of your Ordinary or Edge Save by 1 every level (instead of every other level)

  \mybold{Escaped Convict}
  Depending on which culture you have escaped from, you gain the following enhancements:
  \mybullet {
    \item \mybold{Deep Janeen:}   You've worked the mazes and artworks of the Janeen.  You can never get lost when traveling in the \mylink{Veins}{murk-veins-of-the-earth}. The Janeen only want the most beautiful to work their art - your starting Presence is \DCUP.  You know the difference between Lithic and Umbral architecture.
    \item \mybold{Ælf-Adal:}   The never ending hate of the Ælf-Adal has burned out your empathy.  You are immune to rage, hate, and fury.  Your starting Sanity is an additional \DCUP (meaning your starting Sanity is a d10)
    \item \mybold{Dvargir:}   You have participated in The Work, and now The Work is part of you.  Your starting Talent is \DCUP, and your Encumbrance is +4
    \item \mybold{dErO:}   You possess a partial congruity knot in your skull.  You are immune to Charm and Sleep.  You got really good at dealing with dErO "machines" - you have the Tinkering skill at 2-in-6
  }

  \mybold{Optional: Hideous Visage}
  You wear a mask to hide the truly horrible things done to you in the \mylink{Veins}{murk-veins-of-the-earth}. If you remove this mask, any human Mortal who looks at you for the first time (including allies) must immediately \RS Sanity or become Disgusted


  \mysubsection{Level Bonus}{murk-bonus}
  \mybullet {
    \item \mybold{Level 3:} Your Dark Vision becomes "voluntary" - that is, you can activate it at any time - and more powerful. While "inactive" you have "normal" Day Vision.  You can swap between these two instantly.  Your Dark Vision can now pierce even magical Darkness.
    \item \mybold{Level 5:}    Once per Session, you can speak to stones and have them reshape themselves.  The stones can't be bigger than 1m in any dimension.  The stone will reshape itself into anything you desire - a large rock could be shaped into a idol, a passage could be made through a wall (provided the wall was less than 1m thick).  The object created is rough hewn - fine detail isn't possible (Arbiter's discretion)
    \item \mybold{Level 7:}   Three times per Adventure, you can travel through stone or earth up 10km away.  You need to have visited the destination and there must be uninterrupted stone or ground between yourself and the destination.  You can travel this distance in Minutes.   When you reach level 9,  you can use this ability to return to Svartalfheim if you choose (retiring your character)
  }

  \mysubsection{Professional Gear}{murk-gear}
  In addition to your \mylink{Starting Gear}{starting-gear}, you start with a climbing harness, 2 carabiners, 25m of \myital{Looserope}, and either (a) or (b):

  \mybullet {
    \item \mybold{(A)}  a black leather pauldrons and breastplate (Light armor), black clothing, insect mandible (short sword), 2 daggers, a book of poetry, a mask (optional), a journal filled with names and locations that lead nowhere
    \item \mybold{(B)}  a Knotsman war-axe and shield, 2 pet rocks (you can speak to them), black breeches and a grey silk shirt, 5 tokens used by slaves in the culture you've escaped from, a mask (optional), and a leather folio of maps that lead nowhere
  }  

  \mysubsection{The Veins of the Earth}{murk-veins-of-the-earth}

  According to those who have dared to set foot beneath the skin of the planets of the Totality, the deep places of the moons are beyond description.  They are realms of wondrous colors, breathtaking landscapes, powerful magic, and staggering plenty.  It is a paradise beneath our feet.  The Empires that dwell within stagger the breadth and depth of the surface realms; they shape the caverns and tunnels according to their will, blessed by a deity some heretics say is older than the Authority itself.  They are truly the gods' people.  You, however, will never meet one - the denizens do not leave their home, save for the unlucky and foolish \mylink{Myrkálfar}{species-murk}.  Why would they?  There is nothing in the world without that the depths cannot provide.  The depths are a greater land than any of you will ever experience - it is grander, larger, and free of the petty squabbles and despair which plague our own world.  Those fortunate explorers who are able to discover an extrance to the depths never return -- only a fool turns his back on paradise.

  The Veins of the Earth, as they are collectively known, have adventures and rules all their own.  Patrick Stuart's excellent "Veins of the Earth"\footnote{\url{http://www.lotfp.com/store/index.php?route=product/product&product_id=262}{}} is the sourcebook used by The Totality of Ygg, and are the world that the \mylink{The Myrkálfar}{species-murk} come from.

\newpage

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  NIGHT CHILDREN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
  \mysection{Species: Night Child}{species-night-child}

  \mysubsection{Base Stats}{night-children-base-stats}
  \FLESH d10 \hfill Primary Stat: Talent

  \flavor{\myital{
    "Lie close," Laura said, \\
    Pricking up her golden head:\\
    "We must not look at goblin men,\\
    We must not buy their fruits:\\
    Who knows upon what soil they fed\\
    Their hungry thirsty roots?"\\
    "Goblin Market", Christina Rossetti
    }
  }

  Other folks? They not smart like we are (maybe Pooka are, not sure).  They dumb, they just pretend they know.  But only we know truth - Life and Chaos are same-same.  And no one talk to Chaos the way \myital{we} do. Humans say that makes us bad. One hole owed.  But we not owe anyone anything! Plus you can't owe a hole. Hole not there! See how dumb they are? Only real way to talk to Chaos is be Chaos.  Chaos all around, like ocean. Folks build boats.  We swim.  That make us strong. That make us wise.

  \example{
    Night Children are are bipedal creatures standing about 1m tall - they vary wildly in appearance.  Bogeys tend to have thick, wiry black or red hair sprouting from their heads, faces, and shoulders; Goblins sport large ears and wide, canine smiles; Trolls are usually hairless brown or grey with warty flesh and long noses; Kappa have webbed hands and feet and wide, fish-like eyes; Gremlins have bat-like heads and wicked smiles; Boggarts appear as small shadowy figures that always look vaguely familiar to whoever is looking at them. \href{https://www.pinterest.com/gadhra/the-totality-of-ygg-beta-rules/night-child/}{Visual reference}
  }

  
  \mysubsection{Me Better!}{night-children-modifications}

  \mybold{See In Dark!}
  You have Dark Sight, giving you normal vision in darkness (but a penalty in sunlight)

  \mybold{Me Tiny!}
  You stand only 1m tall.  The number of Significant Items you can carry is -2. If you wear armor, you can only wear armor for "little people" (child-sized).  You cannot wield 2-handed weapons.

  \mybold{One Hole Owed!}
  You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"

  \mybold{That Was Close!}
  Night Children have sharp and clever eyes and ears and a "knack" for things.  Your starting Talent is \DCUP x2.  Add your \LVL to any rolls involving Talent (though the \UD still moves \DCDOWN on a natural 1 or 2)

  \mysubsection{Me Weird!}{night-children-enhancements}

  \mybold{Meat Back on Menu!}
  You can pretty much eat anything (with the Arbiter's OK).  You can regain d3 Grit if you eat flesh during a Breather, and you don't need to roll your \UD for rations during a Bivouac if there's flesh to eat (and you eat it)

  \mybold{Where That Come From?!}
  Once per Session, you can produce one of the following:  (1) a tin of fish paste (edible); (2) a small throwing knife; (3) a smoke (from a pack of smokes) with match; (4) a twist of wire; (5) a single Iron Piece (lost by next Session if not spent); or (6) a large lump of foul-smelling, flammable ear wax.  You can produce this item even if you are stripped naked and locked in a box.

  \mybold{Optional: No talk good!}
  Speak in words of 2 syllables or fewer.

  \mysubsection{Level Bonus}{night-children-bonus}
  \mybullet {
    \item \mybold{Level 3:} Roll one additional Night Child Bonus (you should have 2 total)
    \item \mybold{Level 5:} Roll two additional Night Child Bonuses (you should have 4 total)
    \item \mybold{Level 7:} Roll three additional Night Child Bonuses (you should have 7 total)
  }

  \mysubsection{Professional Gear}{night-children-gear}
  In addition to your \mylink{Starting Gear}{starting-gear}, start with a bag of gems worth 50\FE and either (a) or (b):

  \mybullet {
    \item \mybold{(A)}  half a pair of scissors (dagger), "fur" coat (light armor), a wad of used tissues, a vial of mucus, and a spoon  
    \item \mybold{(B)}  a big stick (club), mismatched hides and rags (light armor), iron pot (helmet), a taxidermied toad, and a human skull
  }    

  \mysubsection{Creating a Night Child}{night-child-creation}

  Rolling up a Night Child is entirely random. Roll once each on the tables below

  \mybold{\myanchor{Night Child Type}{table-night-child-type}} 
  ~\\
  \mytable{X l}{
    \thead{d6} & \thead{Type} \\
  }{
    1 & Bogey \\
    2 & Goblin \\
    3 & Troll \\
    4 & Kappa \\
    5 & Gremlin \\
    6 & Boggart \    
  }

  \mylist {
    \item \mybold{Bogey:}   If you get Surprise you can make a single creature Afraid of you unless they Save
    \item \mybold{Goblin:}   If you wound something that's already injured (has lost Flesh), add your \LVL to your damage.
    \item \mybold{Troll:}   Once per Session you can move somewhere Far Away as a Maneuver
    \item \mybold{Kappa:}   You can breathe underwater and you've got webbed hands and feet - you can swim really fast.
    \item \mybold{Gremlin:}   Once per Session, you can turn any die roll \myital{anyone rolls} into a natural 1 (including \RO, \RS, and \RB rolls )
    \item \mybold{Boggart:}  You can emit a foul smelling gas that causes Disgust to everyone Close except you (no Save).  This affects friends and foes alike.  The smell lasts for Minutes.
  }

  \mybold{\myanchor{Night Child Bonuses}{table-night-child-bonuses}}
  \myital{ Night Child Bonuses don't stack.  If you roll one you alreay have, roll again} 
  ~\\
  \mytable{l p{0.3\linewidth}p{0.7\linewidth}}{
    \thead{d20} & \thead{Bonus} \thead{} \\
  }{
    1 & Dodgy & \DCUP \DEX. Always win Init \\
    2 & Strong &    \DCUP\VIG.  Use 2-h weapons \\
    3 & Smrt &  \DCUP\INT.  Learn random spell (1 Blood Die)\\
    4 & Good Guts & Save vs. Toxins is 5-in-6\\
    5 & Lucky & Save vs. Doom is 5-in-6\\
    6 & Good Ears & Listen is 5-in-6.  Can't be surprised\\
    7 & Crafty &    Gain Tinker at 3-in-6\\
    8 & Sneaks &    d12 Skulk and Murder\\
    9 & Not Dead &  \DCUP on Death's Door\\
    10 & Weird &    Immune to Madness.  Roll on the Mutations! table\\
    11 & Wut? & Immune to Fear, Charm, and Sleep\\
    12 & No Squish &    If you fall, you just bounce\\
    13 & Bug Pal &  Can ride it. If dead, find new beetle the next day. Edible.\\
    14 & Small Pal &    A little kobold buddy. If he dies, you find a new friend the next day. Edible. \\
    15 & Tough &    Carry 9 Significant Items.  +4 Flesh\\
    16 & Sticky &   d12 Clamber. Won't drop things\\
    17 & More Teef &    Bite for d4 damage. Can chew rocks and sticks\\
    18 & Bug Barf & 1xSession, barf up big sack of spiders, worms. Feed up to 6 friends\\
    19 & Fat Head & Your skull is a helmet. If sundered, repaired after Bivouac\\
    20 & Ankle Biter &   If fighting something bigger than you, Fight \RO is \DCUP
  }



} %END