% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggUnseelie}{%
  \mychapter{The Unseelie Court}{unseelie}
}

\renewcommand{\yggUnseelieText}{%
  
  \flavor{And within the dark circle in which the Freer stood making his curses were no unhallowed things, nor were there strangenesses such as come of night, nor whispers from unknown voices, nor sounds of any music blowing here from no haunts of men; but all was orderly and seemly there and no mysteries troubled the quiet except such as have been justly allowed to man.  And beyond that circle whence so much was beaten back by the bright vehemence of the good man's curses, the will-o'-the-wisps rioted, and many a strangeness that poured in that night from Elfland, and goblins held high holiday. For word was gone forth in Elfland that pleasant folk had now their dwelling in Erl; and many a thing of fable, many a monster of myth, had crept through that border of twilight and had come into Erl to see. And the light and false but friendly will-o'-the-wisps danced in the haunted air and made them welcome.  \Tilde Lord Dunsany }

  The non-mortal races known as the Unseelie Court are \myital{phenomenal} - they lack a definable essence, since they are born of Magic and Chaos (though they stand outside of it in the same way a fish swimming in a stream is both a part of and separate from the water). As long as Magic exists, the Unseelie Court will exist.

  The existence of the Unseelie defies the doctrine of the \TheAuthority ; for this reason the Unseelie are considered unholy, anathema, and Unhallowed. By the Grace of  \TheAuthority, Mortal \mylink{Mystics}{trope-mystic} can banish the Unhallowed from their midst.

  The Unseelie are defined by their Species rather than a Trope; though powerful in their own right, they have much less flexibility and choice than the Tribes of \TheAuthority during character creation.  There are thousands of species on the moons of Tartarus, but the four major Species are:
  
  \cbreak\bump

  \mylist {
    \item \mybold{\mylink{The Pooka}{species-pooka}}  Drug-crazed and thought to be half-lapin, Pooka are widely sought by adventuring Bands for their uncanny good fortune.  Pooka have a Luck Die, similar to Knaves, but can use this \UD to affect their Ally's rolls (but not their own). Pooka usually hail from any \mylink{Small, Medium, or Large}{settlements} in Acheron. When they aren't adventuring, they commonly find work as sailors, jesters, scouts, and tavern keepers - but rarely gamblers, since no one will play with them.  Their Primary Stat is \mylink{Presence}{intangible-stats-presence}.

    \item \mybold{\mylink{The Myrkálfar}{species-murk}}  "Murks" (as they are more commonly known) are the escaped slaves of the violent and hateful races of the Veins of the Earth.  Fallen gods doomed to walk among Mortals, they are forever searching for their way home.  They are often grouped under an epithet "Rom", like their cousins the Spriggan. All Murks hail from the Veins of the Earth originally, but they are found throughout Acheron near entrances to the Veins.  Their Primary Stat is \mylink{Sanity}{intangible-stats-sanity}.

    \item \mybold{\mylink{The Spriggan}{species-spriggan}} Ex-vassals of the King of Elfland, wandering the Mortal lands trying to find the bright line of Elfland again.  They are able to summon and control The Forgotten - animals, demons, and forgotten gods - and forge legendary magical blades.  Like the Myrkálfar they are often called "Rom".  All Spriggan hail from Elfland originally, though they can often be found near towns and cities bordering the Great Wood. Their Primary Stat is \mylink{Awareness}{intangible-stats-awareness}.
    
    \item \mybold{\mylink{The Night Children}{species-night-child}}  Night Children are raw chaos incarnate, taking dozens if not hundreds of different forms.  Creating a Night Child is an entirely random affair, with interesting and powerful results. They are found in every climate, city, and cave throughout Acheron. Their Primary Stat is \mylink{Talent}{intangible-stats-talent}.
  }

  \newpage

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  POOKA %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  

  \mysection{The Pooka}{species-pooka}

  \flavor{In the mists before the Beginning, Fate and Chance cast lots to decide whose the game should be; and he that won strode through the mists to \TheAuthority and said: "Now make Gods for Me, for I have won the cast and the Game is to be Mine."  Who it was that won the cast, and whether it was Fate or whether Chance that went through the mists before the Beginning to \TheAuthority - none knoweth. \Tilde Lord Dunsany}

  \mysubsection{Appearance}{pooka-appearance}
    
  You do not believe in Fate - it's a made up idea, created by people who are terrified that we are plunging headlong through the void with no rhyme or reason, only raw, horrible, gorgeous Chaos.  Chance governs the Totality - Chance and no other. This is reprehensible to \TheAuthority, who seeks to keep the secret of the game of lots for himself.  But you are proof that it is Chance that was victorious, and for this you are cursed, and marked Unhallowed.

  You stand scarcely 1m tall, with the head and feet of a rabbit, pig, goat, or toad.  You are gregarious, sly, and always at the point of laughing.  Pooka love to be around people, and it's not uncommon to find them on ships (where they're thought to be good luck), tending bars (if they don't drink away their profits), or with gypsy troupes.  You excel at dancing and singing, and take every opportunity you can to do both.

  \cbreak

  \mysubsection{The Basics}{pooka-basics}

  \mybullet{ 
    \item  Pooka have a d4 \FLESH
    \item  Pooka are Good Time Guys
    \item  Pooka have a d4 Luck Die
  }


  \myhighlight{Good Time Guys}{pooka-good-time}

  You add your \LVL to any \RO or \RB attempt that includes your Presence.  The \UD still moves \DCDOWN on a natural 1 or 2.

  \myhighlight{Luck Dice}{pooka-luck-die}

  Pooka have a Luck Die - a unique \UD similar to \mylink{Knaves}{trope-knave}, and you can use it to help other Allies (but not yourself).  You can roll this Luck \UD at any time to affect someone's \RO or \RB attempt. You can wait until after they roll to use this ability, but you can only roll once per \RO or \RB attempt.

 \mysubsection{Creation}{pooka-creation}

  \callout{
    \mynumlist {
      \item Start one of the core Skills at \mybold{Trained (d8)}
      \item Start one of your Saves at \mybold{Preserved (d8)}
      \item Move your Presence \DCUP (it should now be a d8)
      \item You start with 1d4 Luck Dice
      \item Write down your Virtues, Complications, and Starting Gear
    }
  }

    \mysubsection{Virtues}{pooka-virtues}

    \myhighlight{Apotropaic}{pooka-virtue-apotropaic}
  
    Your presence in a party nullifies any effects of a Witch's Jinx\footnote{See Bell, Book, and Candle}.  If you're \mylink{Bivouac}{combat-resting-bivouac}, there is no chance of wandering Monsters. Buildings where you are sleeping are warded from casual attack (meaning the building would be spared in a riot, for example). 

    \myhighlight{Best. Night. EVAR!!}{pooka-virtue-best-night}
  
    People who hang out with you have a pretty great time.  You increase everyone's \mylink{Carousing}{advancement-carousing} die by \DCUP (and earn 10\% of the Carousing xp of whoever you party with as well). Anyone who doesn't carouse with you has to hear about how awesome the night was the entire next day.    

    \myhighlight{Hype Man}{pooka-virtue-hype-man}
  
    During a \mylink{Breather}{combat-resting}, you can roll a number of d6 equal to your \LVL and heal \SUM Grit to you or your Allies divvied up any way you want.  

    \myhighlight{Bro, Hit This}{pooka-virtue-hit-this}

    For any narcotics you take, (a) the \UD only moves \DCDOWN if you roll a 1, (b) you add your \LVL to your \mylink{Addiction}{gear-narcotics-addiction} roll, and (c) if you \mylink{Overdose}{gear-narcotics-overdose}, you don't have to roll a \mylink{Save vs. Toxins}{saves} (nothing happens except you wasted some drugs).  When you take a \mylink{Vacation}{civilization-vacation}, \RS using your Luck die; if you don't Fail, you can obtain 1 \UD of \myital{any} \mylink{Common Narcotic}{gear-narcotics} for free (even Narcotics that would normally not be available, like Black Lotus in a Small town)

    \myhighlight{Wired}{pooka-virtue-wired}
  
    You cannot be \mylink{Surprised}{combat-surprise} (including the Drop) and you always win \mylink{Init}{combat-init}.  You are immune to Sleep.


    \mysubsection{Complications}{pooka-complications}

    \myhighlight{Tiny}{pooka-complication-tiny}

    You stand only 1m tall.  The number of Significant Items you can carry is -2. If you wear armor, you can only wear armor for "little people" (child-sized).  You cannot wield 2-handed weapons.

    \myhighlight{Unhallowed}{pooka-complication-unhallowed}
    
    You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"


    \cbreak

    \myhighlight{You My Boy Blue!}{pooka-complication-you-my-boy}

    Your love for people causes you to "bond" with people that you party with.  After you go \mylink{Carousing}{advancement-carousing} with others, pick one of the people you caroused with randomly. You are now "bonded" to that person.  Until the next time you go Carousing, you'll favor that person over the others. If there's any extra \mylink{Grit}{combat-flesh-grit} left to distribute, you'll pick them; if there's an extra share of treasure, you'll argue for that person to get it; if you have extra narcotics, you'll give them to that person.  Next time you go Carousing, pick another person randomly ...

    \mysubsection{Starting Gear}{pooka-starting-gear}

    \mybullet {
      \item d4 \UD of any Narcotic (your choice); 
      \item a pair of daggers or hand axes;
      \item 5 rolls on the Random Item table;
      \item 1 gold piece;
      \item playing cards or dice
    }

 


  \newpage

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  SPRIGGAN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  


  \mysection{The Spriggan}{species-spriggan}

   \flavor{"Is it not enough?" he said in his strange rich magical voice, and pointed across his wide lands with the fingers that summoned wonder. ~\\ ~\\ She sighed: it was not enough. \Tilde Lord Dunsany} 

  \mysubsection{Appearance}{spriggan-appearance}
  
  You hail from Elfland, beyond the reach of the Hound of Sish.  Like your brothers and sisters the Myrkálfar you are the Nomadic People, the Rom - cursed with curiosity and infected with the fire that burns in the hearts of the Hallowed to know more, to see the passage of time, and to breathe the air of decay.  All it cost was your soul.  

  You cannot find your way home again, for the bright line between this world and Elfland ebbs forever before you.  Wherever you are is where Elfland cannot be.

  Your bloodline allows you to strike bargains with the lowest of the Small Gods, the Forgotten who stand at the threshold of the Void.  The fear of oblivion dominates every desire and scheme of these sanguinary spirits.  You steal them away from the doorway of Nothingness and by Remembering them, allow them to touch reality once again.  In Remembering, you allow their souls to mingle inside of you, and sing through you - so that in the never-ending ache of Acheron you might, for a moment, remember the feel of the heat of Elfin hearths and the smell of the lavender fields you dream of.  

  You are tall, lithe, and ethereal; Spriggan often stand over 2m, with leaf-shaped ears, long fingers, and gaunt faces vaguely reminiscent of deer or goats.  Older Spriggan often appear cadaverous - while you can't die from old age, your body begins to rot outside of the realm of Elfland (this has no effect on your powers).  Your skin and eye color is as varied as the Mortal races, and from a distance you might pass for human - except for the horns.  Some are small, barely noticeable stubs while other Spriggan sprout deer antlers, curling ram's horns, or tree branches.  It is not uncommon for birds to roost on your horns if they are well developed enough 


  \mysubsection{The Basics}{spriggan-basics}
  
  \mybullet{ 
    \item  Spriggan have a d6 \FLESH
    \item  Spriggan have Uncanny Sight
    \item  Spriggan can summon the Abandoned and the Obliterated - collectively known as the Forgotten - and command their obedience.
  }



  \myhighlight{Uncanny Sight}{spriggan-uncanny-sight}

  You add your \LVL to any \RO or \RB attempt that includes your Awareness.  The \UD still moves \DCDOWN on a natural 1 or 2.

  Your uncanny sight also means you cannot be Surprised (including the Drop), and you can see hidden and invisible creatures.

  \myhighlight{The Forgotten}{spriggan-forgotten}

   You use Remembrance to summon the Abandoned by calling them by name, and Sovereignty to know how many Obliterated you can summon before needing to rest.  The Forgotten (Abandoned and Obliterated) have a power equal to your Potential.

  \mysubsection{Creation}{spriggan-creation}

  \callout{
    \mynumlist {
      \item Start one of the core Skills at \mybold{Trained (d8)}
      \item Start one of your Saves at \mybold{Preserved (d8)}
      \item Move your Awareness \DCUP (it should now be a d8)
      \item Write down your Virtues, Complications, and Starting Gear
    }
  }

 \newpage

  \mysubsection{Virtues}{spriggan-virtues}

  \myhighlight{Remembrance of Elfland}{spriggan-virtues-remembrance-elfland}
    
  Elfland's memory persists and never fades - songs as you sat at your father's knee, poems woven by goblins, bark-bound books of unseelie secrets. You begin with a Remembrance, Sovereignty, and Potential of 1 each.  See Bell, Book, \& Candle for more details.

  \myhighlight{Anamnesis of the Beasts}{spriggan-virtues-anamnesis-beasts}

   You summon and control mundane animals and beastial Monsters\footnotemark[\value{footnote}]

  \myhighlight{The Hound of Sish}{spriggan-virtues-hound-of-sish}
  
  You are untouched by time, the last remnants of godhood.  You are immune to aging.  

  \myhighlight{Tongues of the Forgotten}{spriggan-virtues-tongues}

  You know how to speak Archaic, Fiendish, and Seraphic in addition to any other languages you might know.


  \mysubsection{Complications}{spriggan-complications}

  \myhighlight{Antlers}{spriggan-complication-antlers}

  Antlers or tree branches grow from your head; birds often roost there (and if they do, you can speak with them).  You can't wear helmets or use a Bow or Strongbow. You can't attack with your antlers, but you can sacrifice them for the same effect as wearing a helmet. Antlers will regrow in Weeks.

  \myhighlight{Iron allergy}{spriggan-complication-iron-allergy}

  You are allergic to iron.  If you touch iron it will deal 1 Flesh damage to you every Moment.  Iron weapons do an extra 2 points of damage if they strike Flesh

  \myhighlight{Unhallowed}{spriggan-complication-unhallowed}
    
  You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"

  \cbreak

  \mysubsection{Starting Gear}{pooka-starting-gear}

  \mybullet {
    \item a pair of workgloves;
    \item two silver daggers and a spear; 
    \item a set of prayer candles;
    \item a block of salt (for licking) and a pouch of dead mice;
    \item a pouch of 3 gems (roll on the \mylink{Gems table}{appendixb-random-treasure} in Appendix B);
  }

  \newpage

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  MURKS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \mysection{The Myrkálfar}{species-murk}

  \flavor{Once the gods walked upon Earth as men walk and spake with their mouths like Men. That was in Wornath-Mavai ... a garden fairer than all the gardens upon Earth. Kib was propitious, and Mung raised not his hand against it, neither did Sish assail it with his hours... \Tilde Lord Dunsany}


  \mysubsection{Appearance}{murk-appearance}

  Wornath-Mavai. Svartalfheim. The Glorious Undergarden, beauty beyond measure, Paradise beneath the Mountains, Home to the Myrkálfar, the people beyond Time, who live only for the now.

  Like your brothers and sisters the Spriggan, you were cursed with curiosity, and wondered what was outside of Svartalfheim.  Further and further did you adventure beyond the borders of Svartalfheim until, one day, you were unable to find your way back.  You are now one of the Nomadic People, the Rom.

  Outside of Svartalfheim you were almost immediately enslaved by one of the underworld Empires, for they take great delight in subjugating gods to work for them.  But the burning desire to be free never left you. Almost all Myrkálfar attempt to escape their masters.  Most are killed trying to escape, ending their torment, but some make it out and make their way to the surface.  

  Myrkálfar often act as guides in the Veins, and as such many Mortal races feel that "Murks" are desperate to find their way back again. But the truth is that you can't go back to the point before you knew of the world outside of Svartalfheim.  You have eaten from the tree of knowledge and have been cast out of Eden.  You can never go home again.

  You are tall and thin - like your overworld brethren the Spriggan - but a little shorter, standing less than 2m tall.  Your face resembles Mortals though your eyes and pupils are of the same color,  usually cobalt, white, or ruby.  You seem to care little for fashion, yet you are always effortlessly well-dressed in black, white, or gray.  Masks are common among Murks - their captors often heavily scar their faces and bodies out of envy of their beauty - as are broken manacles and collars.




  \mysubsection{The Veins of the Earth}{murk-veins-of-the-earth}

  According to those who have dared to set foot beneath the skin of the planets of the Totality, the deep places of the moons are beyond description.  They are realms of wondrous colors, breathtaking landscapes, powerful magic, and staggering plenty.  It is a paradise beneath our feet.  The Empires that dwell within stagger the breadth and depth of the surface realms; they shape the caverns and tunnels according to their will, blessed by a deity some heretics say is older than \TheAuthority.  They are truly the gods' people.  You, however, will never meet one - the denizens do not leave their home, save for the unlucky and foolish Myrkálfar.  Why would they?  There is nothing in the world without that the depths cannot provide.  The depths are a greater land than any of you will ever experience - it is grander, larger, and free of the petty squabbles and despair which plague our own world.  Those fortunate explorers who are able to discover an extrance to the depths never return - only a fool turns his back on paradise.\footnotemark

  \footnotetext{The Veins of the Earth, as they are collectively known, have adventures and rules all their own.  Patrick Stuart's excellent "Veins of the Earth"\footnote{\url{http://www.lotfp.com/store/index.php?route=product/product&product_id=262}{}} is the sourcebook used by The Totality of Ygg, and are the world that the \mylink{The Myrkálfar}{species-murk} come from.}

  \setcounter{footnote}{0}  

  \mysubsection{The Basics}{murk-basics}
  
  \mybullet{ 
    \item  Myrkálfar have a d8 \FLESH
    \item  Myrkálfar are Emancipated
    \item  Myrkálfar are Emotionless
  }

  \myhighlight{Emancipated}{murk-emancipated}

  You are an escaped slave from one of the Empires of the Veins of the Earth.  You care for nothing but freedom.  

  Many Mortals find you alien, cold, and uncaring.  This is because the \TheAuthority has stolen their freedom from them - the freedom to ask questions, the freedom to go where you desire and do what you wish.  You will never allow your freedom to be taken again, and you will kill to defend both your freedom and the freedom of others.

  Roll a d4 on the \mylink{Imperial Masters}{murk-imperial-masters} table below to see which Empire you escaped from.

  \myhighlight{Emotionless}{murk-emotionless}

  You add your \LVL to any \RO or \RB attempt that includes your Sanity.  The \UD still moves \DCDOWN on a natural 1 or 2.


  \mysubsection{Creation}{murk-creation}

  \callout{
    \mynumlist {
      \item Move any of the core Skills \DCUP.
      \item Gain the Skill "Veins Lore" at a Trained (d8,+1) level
      \item Move \mybold{all} of your core Saves \DCUP
      \item Move your Sanity \DCUP (it should now be a d8)
      \item Roll a d4 on the \mylink{Imperial Masters}{murk-imperial-masters} table below to see which Empire you escaped from. Write down any benefit from that.
      \item Write down your remaining Virtues, Complications, and Starting Gear
    }
  }

  \mysubsection{Imperial Masters}{murk-imperial-masters}
  
  Roll a d4 to see which Empire you have escaped from:
  
  \mytable{X l}{
    \thead{d4} & \thead{Culture} \\
  }{
    1 & The Deep Janeen \\
    2 & The Ælf-Adal \\
    3 & The Dvargir \\
    4 & the dErO \\
  }

  \dashedbox {
    \mylist {
      \item \mybold{Deep Janeen:}   You've worked the mazes and artworks of the Janeen.  You can never get lost when traveling in the \mylink{Veins}{murk-veins-of-the-earth}. The Janeen only want the most beautiful to work their art - your Presence starts \DCUP (d8).  You know the difference between Lithic and Umbral architecture.
      \\~
      \item \mybold{Ælf-Adal:}   The never ending hate of the Ælf-Adal has burned out your empathy.  You are immune to rage, hate, and fury.  Your starting Sanity is an additional \DCUP (meaning your starting Sanity is a d10)
      \\~
      \item \mybold{Dvargir:}   You have participated in The Work, and now The Work is part of you.  Your Talent starts \DCUP (d8), and your Encumbrance is +4
      \\~
      \item \mybold{dErO:}   You possess a partial congruity knot in your skull.  You are immune to Charm and Sleep.  You got really good at dealing with dErO "machines" - you are Trained (d8,+1) in the Tinkering Skill
    }
  }


  \mysubsection{Virtues}{murk-virtues}

  \myhighlight{Cat's Eyes}{murk-virtue-cats-eyes}

  You have both Dark and Day Vision; you can swap between them instantly.  Your Dark Vision pierces even magical Darkness.

  \myhighlight{Fate's Hand}{murk-virtue-fates-hand}

  All of your Saves start at Preserved (d8,+1). Your \DEATH starts at \mybold{Tough} (d6).

  \myhighlight{The Hound of Sish}{murk-virtue-hound-of-sish}

  You are untouched by Time, the last remnants of godhood.  You are immune to aging.  

  \myhighlight{Metal Empathy}{murk-virtue-metal-empathy}

  You can smell any metal you choose (gold, silver, iron, etc) up to 1m away.  Metal weapons do -2 damage per die (minimum 1) to you.  

  \myhighlight{Silent Speech}{murk-virtue-silent-speech}

  You know the Silent Speech, the language of stones and rocks and the trade speech of the \mylink{Veins of the Earth}{murk-veins-of-the-earth}.  You can use this language to speak with stones. They can tell you what has touched them and what is under or behind them.  This makes it almost impossible to get lost underground. They're not great with time though ...





  \mysubsection{Complications}{murk-complications}


  \myhighlight{Logical}{murk-complication-logical}

  You are devoid of any emotion.  People call you cold, distant, or calculating.  When faced with a decision or dilemma, you will always opt for the logical, unemotional response.  Mortals in particular find you eerie and alien, and react with fear or loathing.


  \myhighlight{Sun Allergy}{murk-complication-sun-allergy}

  Prolonged exposure to direct sunlight causes severe burns and painful blisters.  You seek out shade and shadow whenever you can, and you are most comfortable in subterranean settings.  You can travel well enough through wooded or hilly areas, but wide exposure (deserts, plains) can be problematic if you don't take precautions.


  \myhighlight{Unhallowed}{murk-complication-unhallowed}
    
  You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"

  \cbreak

  \mysubsection{Starting Gear}{murk-starting-gear}

  \mybullet {
    \item a suit of Light armor (describe it to the Arbiter) and a shield;
    \item an insect mandible (longsword) or Knotsman war-axe;
    \item 2 pet rocks (you can speak to them);
    \item a journal filled with names and locations that lead nowhere;
    \item a leather folio of maps that lead nowhere;
    \item a pouch of 5 gems (roll on the \mylink{Gems table}{appendixb-random-treasure} in Appendix B);
    \item a pouch of tokens used by the slaves in the culture you've escaped from
  }




\newpage

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  NIGHT CHILDREN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  

  \mysection{The Night Child}{species-night-child}


  \flavor{\myital{
    "Lie close," Laura said, \\
    Pricking up her golden head:\\
    "We must not look at goblin men,\\
    We must not buy their fruits:\\
    Who knows upon what soil they fed\\
    Their hungry thirsty roots?"\\
    "Goblin Market", Christina Rossetti
    }
  }


  \mysubsection{Me Handsome!}{night-child-appearance}

  Other folk? Not smart like we are (maybe Pooka, not sure).  They dumb, just pretend they know.  Only we know truth - Life and Chaos are same-same.  And no one talk to Chaos the way \myital{we} do. Humans say that make us bad. "One hole owed" they say.  But we owe nothing! Plus you can't owe a hole. Hole not there! See how dumb they are? Only real way talk to Chaos is be Chaos.  Chaos all around, like ocean. Folks build boats.  We swim.  That make us strong. That make us wise.


  \mysubsection{The Basics}{night-child-basics}
  
  \mybullet{ 
    \item  We have d10 \FLESH.  Very strong! Strongest Fae!
    \item  We Clever!
  }

  \myhighlight{Clever}{night-child-clever}

  You add your \LVL to any \RO or \RB attempt that includes your Talent.  The \UD still moves \DCDOWN on a natural 1 or 2.

  \cbreak

  \mysubsection{Bad Stuff}{night-child-complications}

    Get bad news out of the way!

  \myhighlight{Me Tiny!}{night-child-complication-tiny}
  
  You stand only 1m tall to start.  The number of Significant Items you can carry is -2. If you wear armor, you can only wear armor for "little people" (child-sized).  You cannot wield 2-handed weapons.

  \myhighlight{No talk good!}{night-child-complication-no-talk-good}

  Speak in words of 2 syllables or fewer.

  \myhighlight{One Hole Owed!}{night-child-complication-unhallowed}

  You have no "soul" and are Unhallowed. You can't enter consecrated ground and are affected by the Mystic ability "Curse the Unhallowed"


  

  \mysubsection{Creation}{night-child-creation}


  \callout{
    \mynumlist {
      \item One core Skill is \DCUP!
      \item One Save is \DCUP!
      \item Talent is \DCUP! (now a d8)
      \item Grab 3 d6 - time to see what we do!
    }
  }


  \mysubsection{Virtues}{night-child-virtues}

  Night Children have 3 core Virtues:  Weird, Looks, and Gear.  Each Virtue starts at a single d6; roll these d6 at character creation to determine your starting Weird, Looks, and Gear. Add the 3 d6 up to determine your Snag

  As you go up in level, you have the opportunity to move your Looks, Gear, and/or Weird \DCUP - and to roll additional Virtues. See the section on \mylink{Advancement}{advancement}. 

  \mybold{Starting Gear}: In addition to your Gear roll below, you start with:

  \mybullet {
    \item half a pair of scissors (dagger) and a big stick (club);
    \item 5 useless items (examples: a wad of used tissues, a spoon, a taxidermied toad, a parasol).  Let the Arbiter know what these are
  }



  \newpage


  \end{multicols}




  \mytable{l X X X}{
    \thead{Roll} & \thead{Weird} & \thead{Looks} & \thead{Gear} \\
  }{
        1 & Bug Barf & Fishy & Bedlam Bag \\
        2 & Crafty & Glass Teeth & Big Helm \\
        3 & Gassy & Owl Eyes & Big Shield \\
        4 & Run Away & Rat Tail & Bug Pal \\
        5 & Shocky & Spider Eyes & Devil Pen \\
        6 & Spin Silk & Sticky & Gobbomb \\
        7 & Anklebiter  & Bat Ears & Gobsword \\
        8 & Twitchy & Tusky & Trunk Pal \\
        9 & Bad Blood & Frog Mouth & Little Buddy \\
        10 & Shedding & Pig Snout & Skelly Key \\
        11 & Bad Spit & Harpy Claws & Big Pal \\
        12 & Rando & Rooty & Gremlin Tools \\
        13 & Bloodthirsty & Bigg'un & Bogeylatch \\
        14 & Bouncy & Camo & Kazoo \\
        15 & Crazy & Skin Bag & Magic Beans \\
        16 & Meat on Menu & Tough'un & Mirror Mirror \\
        17 & Boom & Fly Wings & Hole \\
        18 & Eat Brains & Goo & Kissy Lips \\
        19 & Nose Hairs & 'nother Arm & Red Shoes \\
        20 & Wut? & Shell & Spinny Wheel \\
        21 & Bad Breath & Babies! & Fly Rug \\
        22 & Sleepy & Beardy & Packpack \\
        23 & Troll Blood &  Smoky & The Crew \\
        24 & Me Human! & Lie Can & Vorpal Sword \\ 
  }

  \mybold{Snags} (total of Weird, Looks, and Gear)

  \mytable{l X l X l X}{
    \thead{Roll} & \thead{} & \thead{Roll} & \thead{} & \thead{Roll} & \thead{} \\
      3 & Angry & 9 & Glowy & 15 & Smell Yummy \\
      4 & Backwards & 10 & Me Cold! & 16 & Stealy \\
      5 & Bad Mouth & 11 & Me Hot! & 17 & Weird Voice \\
      6 & Bumpback & 12 & Me Hungry! & 18 & Who That? \\
      7 & Dirty & 13 & Me Tired ... & - & - \\
      8 & Fat & 14 & Pinhead & - & - \\
  }
      

  \callout {
    Weird and Looks get more powerful the more times you roll the result. See the description for details.
    ~\\
    ~\\
    Gear is unique.  If you roll a result you've rolled before, roll again.
  }


  \newpage


  \begin{multicols}{2}
  \raggedcolumns


  \mysubsection{Weird}{night-children-virtues-weird}

  \mybold{Anklebiter}
  \mylist {
    \item 1st time: You deal +1 damage
    \item 2nd time: You deal +4 damage
    \item 3rd time: You deal +\LVL damage
    \item 4th or more: Roll again
  }

  \mybold{Bad Blood}
  \mylist {
    \item 1st time: Your blood is acidic. When enough of your blood mixes with air (that is, outside your body), it becomes an Iron acid.  You need to bleed about a pint of blood for it to work.  Bleeding more doesn't increase the effectiveness.
    \item 2nd time: As above, but it's a Silver acid
    \item 3rd time: As above, but it's a Gold acid
    \item 4th or more: Roll again
  }

  \mybold{Bad Breath}
  \mylist {
    \item 1st time: Once per Session, you can breathe out a cone of fire, acid, frost, etc (your choice).  The breath does 3d6 damage, Save vs. Doom for half damage.
    \item 2nd time: As above, but you deal 5d6 damage
    \item 3rd time: As above, but you deal \LVL d6 damage
    \item 4th or more: Roll again
  }

  \mybold{Bad Spit}
  \mylist {
    \item 1st time: Your saliva is toxic in high enough quantities.  Once per Session, you can spit out a dram or so of liquid that acts as an Iron toxin.  Treat this toxin as an Ungeant.
    \item 2nd time: As above, but it's a Silver toxin
    \item 3rd time: As above, but it's a Gold toxin
    \item 4th or more: Roll again
  }

  \mybold{Bloodthirsty}
  \mylist {
    \item 1st time: If a Monster is already injured (has taken damage to Flesh), deal +1 damage.  Stacks with Anklebiter.
    \item 2nd time: As above, but +3 damage
    \item 3rd time: As above, but +5 damage
    \item 4th or more: Roll again
  }


  \mybold{Boom}
  \mylist {
    \item 1st time: You can explode.  This will absolutely kill you.  Everyone Close to you must Save vs Doom or immediately perish; everyone Nearby to you must Save vs Doom or fall to 0 Flesh.
    \item 2nd time: Roll again
  }

  \mybold{Bouncy}
  \mylist {
    \item 1st time: You can fall up to 10m without any negative effect (unless you fall into lava or something)
    \item 2nd time: You can fall any distance without negative effect (unless you fall into lava or something)
    \item 3rd time: You can "bounce" up to half the distance you've fallen.  For example, if you fall 10m, you can then "bounce" 5m up.  If you're trying to bounce up to something else, common sense prevails about the angle and the material of the thing you're bouncing off of.
    \item 4th time: Roll again
  }



  \mybold{Bug Barf}
  \mylist {
    \item 1st time: One per Session, barf up big sack of spiders, worms. Feed up to 6 friends
    \item 2nd time: As above, but you can barf the spiders and bugs into a wound to cauterize it.  Immediately remove any Bleeding effects or infections.
    \item 3rd time: As above, but the spiders and bugs also have healing properties when you eat them.  Everyone who partakes heals your \LVL Flesh
    \item 4th time: Roll again
  }



  \mybold{Crafty}
  \mylist {
    \item 1st time: You gain the Skill: Tinker at \mybold{Trained (d8)}
    \item 2nd time: You gain the Skill: Tinker at \mybold{Skilled (d12)}.  If you're already Skilled, roll again.
    \item 3rd time: You gain the Skill: Tinker at \mybold{Master (d20)}.  If you're aleady a Master, roll again
    \item 4th time: Roll again
  }


  \mybold{Crazy}
  \mylist {
    \item 1st time:  If you fail a Sanity roll, roll a Save vs. Doom.  If you succeed, you don't need to roll on the \mylink{Terrifying Tables}{misc-terrifying-tables}
    \item 2nd time:  You are immune to Madness of all sorts
    \item 3rd time:  Roll again

  }


  \mybold{Eat Brains}
  \mylist {
    \item 1st time:  If you eat a Sorcerer's brain, you learn all of the spells that they have written in their skulls.  These spells become a part of you; you can cast them at will using your Talent \UD
    \item 2nd time:  Roll again
  }

  \mybold{Gassy}
  \mylist {
    \item 1st time: You can emit a foul smelling gas that causes Disgust to everyone Close except you (no Save). This affects friends and foes alike. The smell lasts for Minutes.
    \item 2nd time: As above, but the smell also prompts a Sanity check
    \item 3rd time: As above, but the gas also ignites in open flame, dealing 4d6 damage to everyone Close (Save vs Doom for half damage)
    \item 4th time: Roll again
  }

  \mybold{Meat on Menu}
  \mylist {
    \item 1st time: You can pretty much eat anything without getting sick.  If you eat something with flesh (dead or otherwise) during a Breather, you regain an additional d6 Grit; if you eat something with flesh (dead or otherwise) when taking a \mylink{Bivouac}{combat-resting-bivouac}, you don't need to roll your \UD for Provisions.  
    \item 2nd time:  [Breather]: As above, but it's all your Grit; [Bivouac] Restore an extra \UD of any \myital{one} \mylink{Intangible Stat}{intangible-stats}
    \item 3rd time:  Roll again
  }

  \mybold{Nose Hairs}
  \mylist {
    \item 1st time:  Your nose hairs filter out any airborne toxins, rendering you immune
    \item 2nd time:  As above, but you can form toxic boogers out of the toxin.  By picking these out of your nose, you can get 1 d4 \UD of the toxin that was used on you
    \item 3rd time:  As above, but you can now flick these boogers.  Treat as if they were Thrown weapons that deal 1 point of damage, plus the effect of the Toxin if they strike flesh
    \item 4th time:  Roll again
  }

  \mybold{Rando}
  \mylist {
    \item 1st time: Once per Session, you can turn any die roll anyone rolls into a natural 1 (including \RS, \RO , and \RB rolls )
    \item 2nd time: Once per Session, you can turn any die roll anyone rolls into a natural 1 or a natural 6 (including \RS, \RO, and \RB rolls)
    \item 3rd time: Once per Session, you can turn any die roll anyone rolls into a natural 1, a natural 6, or a natural 20 (provided the die has 20 or more sides) - including \RS, \RO, and \RB rolls
    \item 4th time: Roll again
  }

  \mybold{Run Away!}
  \mylist {
    \item 1st time:  If you announce you are running away from Combat, you automatically win Init.  You \mybold{must} use this opportunity to flee Combat.
    \item 2nd time:  As above, plus you can move 2 movement ranges (Close to Far-Away, Nearby to Distant, etc)
    \item 3rd time:  You can automatically flee Combat (though you can't re-enter it)
    \item 4th time:  Roll again
  }

  \mybold{Shedding}
  \mylist {
    \item 1st time: Once per Session, you can shed your skin during a Breather and restore all damage to Flesh
    \item 2nd time: Once per Session, you can shed your skin during a Breather and restore all damage to Flesh, and remove any Physical Wounds
    \item 3rd time: Roll again
  }

  \cbreak

  \mybold{Shocky}
  \mylist {
    \item 1st time:  You generate a low-level electrical current.  Things that are holding you (including grappling) will automatically drop you when you "shock" them
    \item 2nd time:  As above, but the shock deals 1d3 damage as well
    \item 3rd time:  As above, but you can also shoot this energy as electrical bolts at a target Nearby or Far Away.  For every Action you spend "charging", you deal 2 points of damage when you attack.  Charging is a Maneuver Action, discharging is a Combat Action.  The Monster you're attacking gets a Save vs Doom for half damage.
    \item 4th time: Roll again
  }

 \mybold{Go Night Night}
  \mylist {
    \item 1st time: Once per Session, when taking a \mylink{Bivouac}{combat-resting-bivouac}, you wrap yourself in a cocoon.  You are completely helpless in this state.  When you emerge (a) your Grit and Flesh are completely restored; (b) your \UD for all Intangible Stats are set to their \MAX; and (c) all Physical Wounds are removed
    \item 2nd time: Roll again
  }


  \mybold{Spin Silk}
  \mylist {
    \item 1st time: Once per Session, you can spin up to 25m of silk rope out of ... a place.
    \item 2nd time: As above, plus: once per Session, you can "shoot" webs out of your ... out of the place.  Creatures struck by the webs are stuck (treat as Paralyzed) unless they Save vs Doom.  The effect lasts for d4 Markovian.  The webs are extremely flammable.
    \item 3rd time: As above, except the webs last for d12 Markovian
    \item 4th time: Roll again
  }

  \mybold{Troll Blood}
  \mylist {
    \item 1st time: You can regenerate 1 Flesh over Hours (preventing you from Dying), unless the damage is from fire, acid, or magic (including magic weapons).
    \item 2nd time: As above, plus:  at the end of Combat, when you take a Breather, you heal \LVL Flesh
    \item 3rd time: As above, except: you regenerate 1 Flesh at the top of every Moment.
    \item 4th time: Roll again
  }


 \mybold{Twitchy}
  \mylist {
    \item 1st time: Add +4 to your Init rolls
    \item 2nd time: You always win Init (like a Pooka)
    \item 3rd time: Roll again
  }

  \mybold{Me Human!}
  \mylist {
    \item Every time: You can take a Virtue from any Mortal Trope
  }

  \mybold{Wut?}
  \mylist {
    \item 1st time: You are immune to Fear, Charm, and Sleep
    \item 2nd time: As above, plus you are immune to Illusion
    \item 3rd time: As above, plus you are immune to any spell from the Mind paradigm
    \item 4th time: Roll again
  }



  \mysubsection{Looks}{night-children-virtues-looks}

\mybold{Babies!}
	\mylist {
		\item 1st time: You are infested with worms, maggots, flies, etc.  Once per Session, you can command these vermin to attack in Combat as a 2 \HD Swarm.  This swarm fights using the rules under Spriggan, including using Presence for their Fight rolls.
        \item 2nd time: As above, but it's a 4 \HD Swarm
        \item 3rd time: As above, but it's a 6 \HD Swarm
	}
\mybold{Bat Ears}
	\mylist {
		\item 1st time:  Your Listen Skill is immediately set to Skilled (d12).  If it's already Skilled, roll again.
        \item 2nd time:  You can fight and navigate in complete darkness.
        \item 3rd time:  As above, plus you can never be Surprised and you can "see" Invisible creatures
        \item 4th time:  Roll again
	}

\mybold{Beardy}
	\mylist {
		\item 1st time: You have a glorious, long beard that conveys mystical authority.  People you meet assume you're the one in charge, simple folk bow before you, you are greeted with at worst grudging respect and at best adoration wherever you go (save by certain sects and cults who abhor the Unhallowed).
        \item 2nd time: Your beard becomes a legend.  Referring to your beard becomes a linguistic emphasis:  "I will be avenged, by the beard of Fex!" or "Stump's goatee, that's ugly!" You can wrap yourself in your magnificent beard in lieu of clothing - treat as Heavy Armor with no \MD penalty.
        \item 3rd time: Roll again, but add or subtract between 1 and 4 from your roll, in honor of the Beard
	}

\mybold{Bigg'un}
	\mylist {
		\item 1st time:  You are no longer Tiny
        \item 2nd time:  You are the size of a very large man
        \item 3rd time:  You are gigantic, around 3m tall.  You can fight Florentine with a 2-Handed weapon in each hand.  You can carry +4 Significant Items. Finally, you need special armor made for you, and you eat twice as much
        \item 4th time:  Roll again 
	}
\mybold{Camo}
	\mylist {
		\item 1st time:  Once per Session, you can convince someone to utterly forget you were present at an event that happened in the past.  The Arbiter can give the victim a Save vs Doom at their discretion.
        \item 2nd time:  As above, plus:  once per Session, you can turn \mylink{Invisible}{effect-invisible}, though you can't see other invisible objects
        \item 3rd time:  As above, plus:  once per Session, you can disguise yourself as someone else.  The person you're disguising yourself as can't be more than 1m taller or shorter than yourself, and has to be bipedal.  People who see you in disguise might get a Save vs Doom to realize it's you if they know you or the person you're disguising well (at the Arbiter's discretion)
        \item 4th time:   Roll again 
	}
\mybold{Fishy}
	\mylist {
		\item 1st time:  You can swim very, very fast
        \item 2nd time:  As above, plus you can breathe underwater
        \item 3rd time:  As above, plus you can talk to sea creatures.  Go get 'em, Aquaman!
        \item 4th time:  Roll again
	}
\mybold{Fly Wings}
	\mylist {
		\item 1st time:  Just decorative
        \item 2nd time:  They can carry you for short distances; effectively, they increase the distance you can "jump" by 5x (see the section on \mylink{Jumping Distances}{arbiter-movement-jumping})
        \item 3rd time:  Once per Session, you can fly any distance (including hovering) for Minutes.  The process is exhausting.
        \item 4th time:  Roll again
	}


\mybold{Frog Mouth}
	\mylist {
		\item 1st time:  You have a long, sticky tongue.  You can shoot this tongue out 2m (Close) and use it to "grab" small objects (keys, small rocks, etc).  The object can't weigh more than .5kg
        \item 2nd time:  As above, plus:  once per Session, you can let out a loud croak.  The croak is audible for about a km in every direction.  Monsters and Allies Close to you must Save vs Doom or be Stunned for d6 Markovian
        \item 3rd time:  As above, plus:  once per Session, you can swallow something large (approximately 1 Significant Item in size) and vomit it up at your convenience.  You can swallow living things, but be warned they may fight back.
        \item 4th time:  Roll again
	}
\mybold{Glass Teeth}
	\mylist {
		\item 1st time:  You can use your teeth as a saw or knife.  They don't do any damage.  If you use them in this way, you need to chew glass (bottles, jars, etc) to restore your teeth so you can do it again.
        \item 2nd time:  As above, plus:  you can whistle and blow through your teeth, allowing you to mimic animals or voices
        \item 3rd time:  As above, plus:  you can bite with your teeth, dealing d6 \UD of damage.  You'll need to eat glass in order to restore the \UD.  If you hit Flesh, you inflict Bleeding on the Monster
        \item 4th time:  Roll again
	}
\mybold{Goo}
	\mylist {
		\item 1st time:  You can turn yourself into a big pile of ... goo.  You are immune to physical (but not magical) damage, and you can't move or affect the environment in any way.
        \item 2nd time:  As above, but you can ooze around slowly (at about the pace of a slow walk)
        \item 3rd time:  Roll again
	}

\mybold{Harpy Claws}
	\mylist {
		\item 1st time:  You have sharp nails; you can climb dirt walls and can dig a small hole in soft soil
        \item 2nd time:  Your nails are distinct claws.  You can climb dirt and rough stone walls, and can dig a small hole in hard packed dirt. You can fight with your claws as florentine weapons (Hard Brawl Stabbing weapon, d4)
        \item 3rd time:  Your claws are now talons.  You can make a small hole in stone, and can climb smooth ice or rock walls.  You can fight with your talons as florentine weapons (Hard Brawl Stabbing weapon, d8)
        \item 4th time:  Roll again
	}
\mybold{Lie Can}
	\mylist {
		\item  1st time:  Once per Session, you can turn into a were-beast.  You tell the Arbiter what the beast is.  You can't use this Virtue while wearing armor.  Immediately drop anything you're holding, but gain the following additional abilities:  Berserk, +10 Flesh, Claws (Hard Brawl d8, Florentine), Regenerate 1 Flesh at the top of the Moment (unless you are struck with magic or silver).  
        \item  2nd time: Roll again
	}
\mybold{'nother Arm}
	\mylist {
		\item 1st time:  You get another arm.  It's pretty weak - you can't fight with it or anything, but it's useful for holding stuff
        \item 2nd time:  Your other arm is a lot stronger.  You can use it to hold a shield, or hang from something and keep your other arms free.
        \item 3rd time:  If your \DEX is d16 or greater, you can fight with a weapon in all 3 hands.  Treat as the same rules as Florentine, except the combined damage can't exceed d18.
        \item 4th time:  Roll again
	}
\mybold{Owl Eyes}
	\mylist {
		\item 1st time: You have giant owl eyes, granting you Dark Sight
        \item 2nd time: As above, plus you have Low Light Vision
        \item 3rd time: You can switch between Dark Sight, Low Light Vision, and Day Vision at will
        \item 4th time: Roll again
	}
\mybold{Pig Snout}
	\mylist {
		\item  1st time: You can smell any metal you choose (gold, silver, iron, etc) up to 1m away.
        \item  2nd time: As above, plus you can smell blood and flesh up to 50m away (100m if they are an Englishman)
        \item  3rd time: As above, plus you can smell magic on people, weapons, and objects
        \item  4th time: Roll again
	}
\mybold{Rat Tail}
	\mylist {
		\item 1st time: If a Monster's attack is about to cause you \mybold{physical} damage, you may immediately take a Combat Action and sacrifice your tail, taking no damage
        \item 2nd time: As above, plus the tail is strong enough for you to hang from
        \item 3rd time: As above, but you can use your tail as a whip.  The whips is a Fast Brawl weapon that deals d4 damage.  If you roll a 4, you can forgo damage and try to Disarm your opponent instead by \RB using your \DEX.
        \item 4th time: Roll again
	}


\mybold{Rooty}
	\mylist {
		\item  1st time: You can sprout roots from your hands and/or feet.  These roots can wrap around objects no wider than .5m, holding you in place
        \item  2nd time: As above, but the roots can wrap around things up to 2m wide
        \item  3rd time: As above, but the roots can dig into dirt or rock
        \item  4th time: Roll again
	}

\mybold{Shell}
	\mylist {
		\item 1st time:  A shell of hard chitin, granting you Soak: 1
        \item 2nd time:  The shell is now hard as quartz, granting you Soak: 2
        \item 3rd time:  The shell is as hard as diamond, granting you Soak: 3
        \item 4th time:  Roll again
	}


\mybold{Skin Bag}
	\mylist {
		\item 1st time:  You have a pouch ... somewhere ... on your body.  The pouch is about the size of a cigar box - common sense should prevail what can be stored in it.
        \item 2nd time:  As above, but the pouch has a Hammerspace aspect to it.  You can carry 1 Significant Item
        \item 3rd time:  As above, but you can now carry 10 Significant Items.
        \item 4th time:  Roll again
	}
\mybold{Smoky}
	\mylist {
		\item 1st time: Once per Session, you can turn your body ghostly and insubstantial during Combat.  Monsters must make an immediate Morale roll; further, you're granted a +4 Guard roll, and you are only struck by magic.
        \item 2nd time: You may turn insubstantial during Combat as above; in addition, outside of Combat, you can turn into smoke for d6 minutes (the Arbiter will time you).  You move slowly, but you can seep beneath doors, through cracks, and into chimneys. You can't seep into anyone's lungs, they cough you out right away. Weapons can't harm you, but certain spells or effects that disperse smoke (Arbiter's judgement) will cause you to become substantial.
        \item 3rd time:  Roll again
	}

\mybold{Spider Eyes}
	\mylist {
		\item 1st time:  You can't be \mylink{Blinded}{effect-blinded}
        \item 2nd time:  As above, plus you can't be Surprised
        \item 3rd time:  As above, plus you can see Invisible creatures, and Mirror Image has no effect on you.
        \item 4th time:  Roll again
	}


\mybold{Sticky}
	\mylist {
		\item  1st time: You're generally ... sticky.  Like the adhesive on the back of a sticky note.  You could stick papers to yourself, and you won't lose your grip if you're climbing a rope or ladder
        \item  2nd time: You're now as sticky as tar.  You won't drop things that you're holding (you can't be disarmed).  You could stick a weapon to your body.  You can turn this stickiness "off" at will.
        \item  3rd time: You're now as sticky as soverign glue.  You can't drop things you're holding unless you will it.  You can climb up a wall like a spider and hang from the ceiling like a fly (though you'd need to be naked).
        \item  4th time: Roll again
	}

\mybold{Tough'un}
	\mylist {
		\item 1st time: \myital{He was like a saddlebag with eyes!}  You look (and are) very tough.  You get a +2 to any rolls where you're trying to intimidate someone.  You don't take any damage from effects of mundane weather (snow, rain, sand, etc)
        \item 2nd time: As above, plus you add +4 to any \DEATH rolls
        \item 3rd time: As above, plus you gain +10 Flesh
        \item 4th time: Roll again
	}
\mybold{Tusky}
	\mylist {
		\item 1st time:  You grow a pair of small tusks.  The tusks act as if you're wearing a helmet.  If you should sunder them, they'll grow back after you take a Vacation.
        \item 2nd time:  As above, but your tusks are much bigger.  If you execute the \mylink{Bum Rush}{combat-deeds-bum-rush}, you can strike with your tusks as a Combat Action.  The tusks are Hard Brawl weapons that deal d6 damage.
        \item 3rd time:  As above, but your tusks are huge.  You like to decorate them with bands of iron and rings.  Your tusks are treated as Hard Brawl weapons that do d12 damage in a \mylink{Bum Rush}{combat-deeds-bum-rush}
        \item 4th time:  Roll again
	}


  \mysubsection{Gear}{night-children-virtues-gear}


\mybold{Bedlam Bag}
	\mylist {
		\item When you open the bag and turn it upside down, roll a d4 to see what falls out:  (1) a few thousand ball bearings; (2) a bomb with a countdown timer.  The bomb will explode at the bottom of the \mybold{next} Moment.  There's a 50/50 chance it's a dud (the Arbiter will roll in secret), but will deal 8d6 damage to everyone Close to it if it explodes (Save vs Doom for half damage).  The bomb can be thrown;  (3) a half dozen gremlins fall out and run in different directions, immediately causing as many problems as possible for Minutes; (d)  Bats. A lot.
	}
\mybold{Big Helm}
	\mylist {
		\item A giant helmet.  The helmet will protect you from being \mylink{Dazed}{gear-weapon-daze} and from certain Physical and Serious Wounds.  In addition, if a Monster's attack is about to cause you \mybold{physical} damage, you may immediately take a Combat Action to destroy the helmet, taking no damage.  The helmet is "fixed" at the start of next Session.
	}
\mybold{Big Pal}
	\mylist {
		\item Your big pal is .5m taller than you, looks extremely intimidating, and is very sensitive.  Big pal's feelings get hurt easily.  Big pal can carry you around and boost you up for hard to reach places.  In Combat, Big Pal likes to watch from the back and shout encouragement; however, if you are ever injured in Combat, your Big Pal will immediately join the fight.  Big Pal has 6 Flesh and gives you +4 to your Fight \RO.  You can put any damage you would normally take on Big Pal instead.  If Big Pal should die, another Big Pal shows up at the start of the next Session.
	}


\mybold{Big Shield}
	\mylist {
		\item A giant shield.  The shield should be treated as an additional suit of Light Armor (d4 \UD); however it takes 2 hands to use.  The shield is repaired the same way Armor is.
	}
\mybold{Bogeylatch}
	\mylist {
		\item  Once per Session, you can attach this doorknob to a hard surface and open a door 2m high, 1m wide, and .5m thick.  The door exists until someone closes it; the bogeylatch appears back in your pocket.
	}

\mybold{Bug Pal}
	\mylist {
		\item  You can ride it. If it dies, you find a new bug pal at the start of next Session.  Edible.
	}
\mybold{Devil Pen}
	\mylist {
		\item  Contracts signed with this pen (in blood) between two willing parties are magically enforced. Breaking the contract means the responsible party suffers a permanent Curse which can only be removed by the other party in the contract.
	}
\mybold{Fly Rug}
	\mylist {
		\item  You and up to 4 allies can "ride" this flying carpet.  The rug can levitate up and down and can move forwards and backwards at a slow pace (about walking speed).  The Fly Rug has no handles, so be careful you don't get knocked off.
	}
\mybold{Gobbomb}
	\mylist {
		\item \myital{Anytime I had a problem and I threw a Molotov cocktail, boom! Right away, I had a different problem}  At the start of the Session, you create 3 explosive grenades.  These are Fast Throw weapons that deal 3d6 damage to everything Close to their point of explosion (Save vs Doom for half damage).  Throwing a grenade is a Combat Action.  The grenades will also set flammable things on fire.  Every grenade has a 1-in-4 chance of being a dud (rolled in secret by the Arbiter).  If you don't use the grenades by the end of the Session, they're all duds.
	}
\mybold{Gobsword}
	\mylist {
		\item You gain a weapon appropriate for your species: a pair of Norn scissors, a giant tooth through a club, the mandible of a predatory insect - tell the Arbiter what it is.  The weapon is a Fast Brawl weapon that does d8 damage and is magic.
	}
\mybold{Gremlin Tools}
	\mylist {
		\item  Once per Session, you can use the Gremlin tools to do one of the following:  (a) remove a Trivial or Minor Sigil; (b) "repair" 4 points of Flesh damage (not pretty); (c) repair a suit of Armor to its \MAX \UD; (d) "fix" something that's broken (Arbiter's discretion)
	}
\mybold{Hole}
	\mylist {
		\item  It's a hole you can fold up like a handerchief.  The hole can be laid flat on any surface, but it has to stick there (so you'll have to get creative if you want to hang it from the wall or ceiling).  The hole is 500 cm wide but 3m deep.  Anything you put in here is considered to be in Hammerspace (see Bell, Book, and Candle).  
	}
\mybold{Kazoo}
	\mylist {
		\item  Once per Session, you can put on a little kazoo concert.  Pick 1:  (a) purge a Mental or Spiritual Wound from someone; (b) during a Breather, bring everyone to full grit; (c) end all Markovian effects Close to you; (d) restore 1 point of Flesh to everyone Close to you (friend or foe).  If you actually play the kazoo, pick 2.
	}

\mybold{Kissy Lips}
	\mylist {
		\item  A tube of very bright coral lipstick.  Once per Session, you can apply this lipstick and do one of the following:  (a) tell everyone about the interesting things in a room you're in, even if hidden from view ("there's a secret door in the north wall, a magic dagger hidden in the chimney, and a spider waiting to ambush us in the corner."); (b) tell effortless and undetectable lies for d6 Minutes;  (c) Charm everyone Close to you with a risqué performance (Save vs Doom or Charmed for as long as you perform); (d) whistle a tune that removes all Markovian effects on Allies Close or Nearby.
	}


\mybold{Little Buddy}
	\mylist {
		\item  A little kobold buddy. He can't do much except hold a light source.  Unquestionably loyal and extraordinarily stupid.  If he dies, you find a new friend the next day.  Edible.
	}
\mybold{Magic Beans}
	\mylist {
		\item At any time, you can water your Magic Beans and grow them.  Roll a d24 on this table; that piece of Gear grows from the Magic Beans.  If you roll a piece of Gear you already have - too bad, nothing happens.
	}
\mybold{Mirror Mirror}
	\mylist {
		\item Once per Session, you can reach into the Mirror Mirror and pull out a copy of an object reflected in the mirror.  The object that you pull out must be within reach of the mirror (as if it were a window), small enough to fit through the mirror (as if it were a window) and can’t weigh
more than 10kg. The mirror object looks and feels exactly like the object it copied, though it is a mirror image (so if you were to copy a book, the text would be backwards). You can’t copy any magical properties of the object, and you can only duplicate objects, not living things. The object exists for Minutes. If the object suffers a solid blow, it pops like a bubble.
	}

\newpage

\mybold{Packpack}
	\mylist {
		\item  Giant, colossal backpack that only you can wear.  You can reach into this backpack and produce any mundane item (at the Arbiter's final discretion).  The object can't be valuable in and of itself (no pulling out gems or jewels) and has to be smaller than a human arm (daggers and short swords OK, polearms not so much).  Additionally, you can store 25 Significant Items in the backpack as if they were in Hammerspace.  The backpack doesn't affect your \MD in any way. 
	}
\mybold{Red Shoes}
	\mylist {
		\item  Once per Session, you can click the heels of your Red Shoes together to undo \mybold{any} die roll that hits the table.  The person who rolled immediately re-rolls.  You have to have feet to use the Red Shoes.
	}
\mybold{Skelly Key}
	\mylist {
		\item Once per Session, you can open any mundane locked thing.  
	}
\mybold{Spinny Wheel}
	\mylist {
		\item  Once per Session, you can use the Spinny Wheel when taking a \mylink{Bivouac}{combat-resting-bivouac} to produce one of the following: (a) 10 gold coins (doesn't count for XP).  Requires straw; (b) a single dose of any Iron or Silver Toxin or Sera.  The dose is delivered through the spindle; (c) an unraveling spool of thread that shows you the most direct way out of where you are; (d) a story that enchants all of your Allies, granting +6 Grit (even above their \MAX)
	}
\mybold{The Crew}
	\mylist {
		\item  A crew of goblins, kobolds, orcs, and other unsavories follows you around (d4+2 to start).  Every 2 members of the Crew (rounded down) grant you +1 to all \RO and \RS attempts.  Each Crew member requires a Provision roll when taking a \mylink{Bivouac}{combat-resting-bivouac} (though they are cannibalistic so there's some cost cutting opportunities).  They are loyal, loud, and extraordinarily stupid.  Sneaking up on people is out.  You crew is always between 2 and 10 members.  If you ever get to 0 crew members, 2 crew members show up next Session - otherwise, you gain 1 crew member each Session, up to 10 crew.
	}

\cbreak

\mybold{Trunk Pal}
	\mylist {
		\item A small bureau that follows you around on hundreds of tiny feet.  Surprisingly fast.  Can store up to 25 Significant Items for you and obey simple commands.  Will "give" you an item stored in it at your immediate request. If it gets destroyed, you find it leaning over you when you wake up next Session - but there's a 50/50 chance each Significant Item in it doesn't make it back (roll for each)
	}
\mybold{Vorpal Sword}
	\mylist {
		\item  A beautiful, jewel encrusted sword of extraordinary sharpness.  The Vorpal Sword is a Hard Brawl weapon that deals d8 damage and is magic.  The damage die explodes.  If you ever do 20+ points of damage with the sword, the victim is decapitated unless they make a Save vs Doom.
	}


\mysubsection{Snags}{night-children-complications}

\mybold{Backwards}
	\mylist {
		\item  You're put together backwards, meaning your feet or arms go the other way.  You get easily confused with directions - if you're by yourself, you automatically get lost
	}
\mybold{Bad Mouth}
	\mylist {
		\item   No one can understand your accent until they deal with you for awhile.  You're Allies understand you, but no one else does.
	}
\mybold{Bumpback}
	\mylist {
		\item   Doesn't affect your movement or anything, but everyone always assumes you're the party's assistant / torch-bearer / etc.  You don't get much respect.
	}
\mybold{Dirty}
	\mylist {
		\item  You can't own nice things.  Clothing you wear becomes almost instantly soiled, weapons rusty, armor squeaky.  It doesn't have any mechanical effect, but you're not permitted in polite society
	}
\mybold{Fat}
	\mylist {
		\item  You're a little round around the edges.  Your extra weight takes up 1 Significant Item slot.
	}
\mybold{Glowy}
	\mylist {
		\item  You have a slight ... glow about you. Makes it almost impossible to hide unless you're completely covered by thick cloth. 
	}
\mybold{Me Cold!}
	\mylist {
		\item  You get cold very easily.  You'll refuse to go somewhere if it's too cold.
	}
\mybold{Me Hot!}
	\mylist {
		\item You get hot very easily.  You'll refuse to go somewhere if it's too hot.
	}
\mybold{Me Hungry!}
	\mylist {
		\item You're always starving; you need to roll your Provisions twice when you Bivouac
	}
\mybold{Me Tired...}
	\mylist {
		\item You sleep very deeply.  It takes an extra Action to wake you up.
	}
\mybold{Pinhead}
	\mylist {
		\item You have a really, reaalllly tiny head.  People laugh awkwardly.  You can't wear a Helmet (except for a Big Helm).
	}
\mybold{Smell Yummy}
	\mylist {
		\item You smell delicious to Monsters.  They'll go for you first in a fight.
	}
\mybold{Stealy}
	\mylist {
		\item You like to steal stuff.  You're compelled to try to steal something once a Session.
	}
\mybold{Weird Voice}
	\mylist {
		\item You have a weird voice (roll again if you're not comfortable roleplaying this)
	}
\mybold{Who That?}
	\mylist {
		\item You have absolutely no memory of faces, except for your Allies.
	}






} %END
