\mysection{Appendix A: Combat Tables}{appendixa-combat-tables}


\mysubsection{Fumbles}{appendixa-combat-tables-fumbles}

If you fumble, roll on the following table depending on your armor:

  \mytable{X c }{
    \thead{Weight} & \thead{Die}  \\
  }{
    None & d2  \\
    Light & d4  \\
    Medium & d8 \\
    Heavy & d12 \\  
    Shield & +1 to roll \\
    Helmet & +1 to roll \\
  }


If something doesn't apply, move up the chart (that is, things get worse) to the next available effect that works.

\mynumlist {
  \item  You miss spectacularly and everyone laughs at you and now no one will invite you to prom.  Lose 1 Grit on account of the shame.
  \item You miss and lose your grip on your weapon and you're holding it all awkward and things feel weird.  Your next Fight roll is -4
  \item You'll tell everyone that your opponent dodged but really you got all turned around.  Your next Guard roll is -4
  \item You Trip and Fall - you are now Prone.
  \item You Disarm yourself. If it's a Shoot weapon, the bowstring breaks and it'll take Minutes to fix, so let's hope you have an Option B.
  \item If you're wearing a backpack you sever the straps, it splits open, and all the contents spill onto the ground.  Backpack is now useless and everyone can see your weird collection of things you've been stealing
  \item You really overextend yourself, pull a hammy, and mess up your Armor (if you're wearing any).  Make an Armor \UD roll.
  \item (or more) Stop hitting yourself!  Roll damage against Armor (if you've got it) or Flesh.
}


\mysubsection{Wounds}{appendixa-combat-tables-wounds}

A brush with death is not without its cost.  Roll a d3 to determine what kind of wound  you receive:  1) a Physical Wound; 2) a Mental Wound; 3) a Spiritual Wound.  The effects of Wounds are healed by taking a Bivouac unless the damage is permanent (a Beating, Madness, or Life Drain).  Those can only be healed during a \mylink{Vacation}{civilization-vacation}.

Roll a d10 on the appropriate table below


\mysubsection{Physical Wounds}{physical-wounds}

\mynumlist {
  \item  Permanent superficial scar, you say where.
  \item  Broken nose, you can't smell anything and your \MAX Presence is \DCDOWN until fixed
  \item  Ringing ears, Listen checks are at -1
  \item  Crushed your hand, -2 to any \RO tries requiring fine motor coordination
  \item  Pulled a shoulder muscle, -1 Damage (minimum 1)
  \item  Got your bell rung. No effect if you were wearing a helmet. You can't do anything requiring Concentration (including casting some spells).  Your \MAX Awareness is \DCDOWN until fixed.
  \item  Twisted your knee or ankle.  Your \MD is \DCDOWN
  \item  Knocked d3 teeth out. Your \MAX Presence is \DCDOWN permanently.
  \item  Feeling your age.  You are unable to heal Grit.
  \item  Serious Wound. Roll on the \mylink{Beatings}{appendixa-beatings-table} table
}

  \mysubsection{Mental Wounds}{mental-wounds}

  \mynumlist {
    \item Develop a permanent nervous tic, you say what it is
    \item  Brush with insanity - roll your Sanity die.
    \item  You forget how to use one of your Skills (determined randomly)
    \item  Ennui.  \MD is \DCDOWN
    \item  Hysterical Blindness.  You can only see things Close or Nearby.  Shoot and Throw Fight \RO is at -2
    \item  Distracted.  You can't do anything requiring Concentration (including casting some spells).  Your \MAX Awareness is \DCDOWN until fixed.
    \item  Badly shaken. -2 to any \RO tries requiring fine motor coordination
    \item  Susceptible to suggestion - Sleep and Charm Person work on you automatically, and you'll tend to believe anything someone says
    \item  Confidence shaken.  You are unable to heal Grit
    \item  Serious Wound. Roll on the \mylink{Madness! table}{other-stuff-terror-horror-madness}
  }


  \mysubsection{Spiritual Wounds}{spiritual-wounds}

  \mynumlist{
    \item Your brush with death turns your hair permanently white (can't be healed)
    \item  A random Insignificant Item (Arbiter rolls) rolls off somewhere and is permanently lost (can't be found)
    \item  Only saved by luck.  Your \MAX Talent is \DCDOWN until dealt with.
    \item  Marked for death.  Monsters will target you first in Combat
    \item  Empty luck battery.  Automatically take a 1 in any Luck Contests.
    \item  Winds of Doom.  You've only postponed the inevitable.  Your Saves vs. Doom have a -4 penalty
    \item  Arcane target.  Your Save vs. Hexes have a -4 penalty
    \item  Karma extracts a toll - your \MAX Talent is \DCDOWN permanently.
    \item  Unquiet thoughts.  You are unable to heal Grit.
    \item  Serious Wound. Roll on the \mylink{Life Drain}{appendixa-life-drain-table} table
  }


  \cbreak

  \myhighlight{Beatings}{appendixa-beatings-table} 

  \mytable{X c}{
    \thead{} & \thead{}  \\
  }{
    1 & Arm  \\
    2 & Leg \\
    3 & Face \\
    4 & Groin / Genitals \\  
    5 & Back \\
    6 & Neck  \\
    7 & Chest  \\
    8 & Abdomen \\
    9 & Spine \\  
    10 & Head \\
  }

  \mylist {
    \item \mybold{Arm} You've injured your [1-3 left, 4-6 right] 1) Hand; 2) Forearm; 3) Elbow; 4) Bicep; 5) Triceps; 6) Underarm.  Whichever arm got hit is useless - you can't hold anything with it. You can't use 2h weapons.  If it's your "main hand", make your Fight \RO checks at -4.  If you don't know which one is your "main" hand, roll a d6: 1-4 it's your right, 5-6 it's your left.

    \item \mybold{Legs} You've injured your [1-3 left, 4-6 right]  1) Foot; 2) Shin; 3) Calf; 4) Knee; 5) Thigh; 6) Hip  You can't run and can only walk with a limp.  Your \MD drops \DCDOWN x2 (meaning you're immobile if you're wearing heavy armor)
    
    \item \mybold{Face} You've injured your 1) Cheek; 2) Ear; 3) Mouth; 4) Nose; 5) Eye; 6) Jaw.  That's pretty rough to look at.  If you're wearing a helmet, no effect but the helmet is destroyed.  Otherwise, your \MAX Presence drops \DCDOWN x2 permanently. If it was an eye injury, also take -4 to Fight \RO with Throw or Shoot weapons. 

    \item \mybold{Groin / Genitals}  Everyone winces, you drop to the fetal position for Minutes and can't move.  Kids are probably out of the question.  You can't heal any Grit until the Wound is taken care of.

    \item \mybold{Back} You've injured your 1) left upper; 2) right upper; 3) left lower; 4) right lower back!  You can't carry any Significant Items (including armor and weapons)

    \item \mybold{Neck}  You've injured your 1) throat; 2) back of neck; 3) left side of neck; 4) right side of neck; 5) left shoulder; 6) right shoulder. If it's your shoulder, same as "Arm" above.  If it's your throat or neck, you are unable to speak (including cast spells) until the Wound is taken care of.
    
    \item \mybold{Chest}  You've injured your [1-3 left, 4-6 right] chest and ribcage. Any time you do anything strenuous (like Fighting, Guarding, or running away), make a \RS : \VIG try. If you Fail, you take \mylink{The Vapors}{effect-the-vapors}.

    \item \mybold{Abdomen} Take Minutes to stuff your intestine back inside your body.  Any time you do anything strenuous (like Fighting, Guarding, or running away), make a \RS : \VIG try. If you Fail, you immediately begin \mylink{Bleeding}{effect-bleeding}.

    \item \mybold{Spine} You're partially paralyzed and can only crawl.  Treat as if you were permanently \mylink{Prone}{effect-prone}.

    \item \mybold{Head} Helmets save lives - destroy your helmet if you  have one and take no effect.  Otherwise you fall comatose.  Treat as if you had a permanent case of \mylink{The Vapors}{effect-the-vapors}
  }

  \myhighlight{Life Drain}{appendixa-life-drain-table} 

  \mytable{X c }{
    \thead{} & \thead{}  \\
  }{
    1 & Language  \\
    2 & Civilization \\
    3 & Skill \\
    4 & Passion \\  
    5 & Humanity \\
    6 & Allies \\
  }

\mylist {
  \item \mybold{Language} You can on longer speak, read, or write any language.  You can still moan and holler unintelligibly if desired.

  \item \mybold{Civilization} You can no longer use any tools or weapons; you have to perform all actions directly (with the body)

  \item \mybold{Skill}  You've forgotten how to do anything not related to eating, fighting, and sleeping. All of your Skills drop to Untrained.


  \item \mybold{Passion} You become depressed and lethargic, unable to perform any actions during a Vacation (including going Carousing).  During play, any action that would take Minutes or longer of continuous concentration requires a Sanity roll to complete (remember, a Failure requires a roll on the \mylink{Terrifying Tables}{misc-terrifying-tables})

  \item \mybold{Humanity} You become perceptibly but indescribably inhuman.  Animals growl or otherwise act hostile in your presence, and hirelings won't follow you. 

  \item \mybold{Allies} An attendant spirit was stolen from you. Familiars, intelligent weapons, the ability to remember the Forgotten, and relationships with \TheAuthority or Small Gods are all at risk.
}

\newpage


\end{multicols}
