% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggUnseelie}{%
  \mychapter{The Unseelie Court}{unseelie}
}

\renewcommand{\yggUnseelieText}{%
  
  \flavor{And within the dark circle in which the Freer stood making his curses were no unhallowed things, nor were there strangenesses such as come of night, nor whispers from unknown voices, nor sounds of any music blowing here from no haunts of men; but all was orderly and seemly there and no mysteries troubled the quiet except such as have been justly allowed to man.  And beyond that circle whence so much was beaten back by the bright vehemence of the good man's curses, the will-o'-the-wisps rioted, and many a strangeness that poured in that night from Elfland, and goblins held high holiday. For word was gone forth in Elfland that pleasant folk had now their dwelling in Erl; and many a thing of fable, many a monster of myth, had crept through that border of twilight and had come into Erl to see. And the light and false but friendly will-o'-the-wisps danced in the haunted air and made them welcome.  \Tilde Lord Dunsany }

  The non-mortal races known as the Unseelie Court are \myital{phenomenal} - they lack a definable essence, since they are born of Magic and Chaos (though they stand outside of it in the same way a fish swimming in a stream is both a part of and separate from the water). As long as Magic exists, the Unseelie Court will exist.

  The existence of the Unseelie defies the doctrine of \TheAuthority ; for this reason the Unseelie are considered unholy, anathema, and Unhallowed. By the Grace of  \TheAuthority, Mortal \mylink{Mystics}{trope-mystic} can banish the Unhallowed from their midst.

  The Unseelie are defined by their Species rather than a Trope; though powerful in their own right, they have much less flexibility and choice than the Tribes of \TheAuthority during character creation.  There are thousands of species on the moons of Tartarus, but the four major Species are:
  
  \cbreak\bump

  \mylist {
    \item \mybold{\mylink{The Pooka}{species-pooka}}  Drug-crazed and thought to be half-lapin, Pooka are widely sought by adventuring Bands for their uncanny good fortune.  Pooka have a Luck Die, similar to Knaves, and can use this \UD to affect their Ally's rolls (but not their own). Pooka usually hail from any \mylink{Small, Medium, or Large}{settlements} in Acheron. When they aren't adventuring, they commonly find work as sailors, jesters, scouts, and tavern keepers - but rarely gamblers, since no one will play with them.  Their Primary Stat is \mylink{Presence}{intangible-stats-presence}.

    \item \mybold{\mylink{The Myrkálfar}{species-murk}}  "Murks" (as they are more commonly known) are the escaped slaves of the violent and hateful races of the Veins of the Earth.  Fallen gods doomed to walk among Mortals, they are forever searching for their way home.  They are often grouped under an epithet "Rom", like their cousins the Spriggan. All Murks hail from the Veins of the Earth originally, but they are found throughout Acheron near entrances to the Veins.  Their Primary Stat is \mylink{Sanity}{intangible-stats-sanity}.

    \item \mybold{\mylink{The Spriggan}{species-spriggan}} Ex-vassals of the King of Elfland, wandering the Mortal lands trying to find the bright line of Elfland again.  They are able to summon and control The Forgotten - animals, demons, and forgotten gods - and forge legendary magical blades.  Like the Myrkálfar they are often called "Rom".  All Spriggan hail from Elfland originally, though they can often be found near towns and cities bordering the Great Wood. Their Primary Stat is \mylink{Awareness}{intangible-stats-awareness}.
    
    \item \mybold{\mylink{The Night Children}{species-night-child}}  Night Children are raw chaos incarnate, taking dozens if not hundreds of different forms.  Creating a Night Child is an entirely random affair, with interesting and powerful results. They are found in every climate, city, and cave throughout Acheron. Their Primary Stat is \mylink{Talent}{intangible-stats-talent}.
  }

  \newpage


  \input{species/murks.tex}
  \newpage
  \input{species/spriggan.tex}
  \newpage
  \input{species/pooka.tex}
  \newpage
  \input{species/night_children.tex}
  \newpage





} %END
