% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggMortals}{%
  \mychapter{The Tribes of the Authority}{mortals}
}

\renewcommand{\yggMortalsText}{%

  \flavor{And Kib grew weary of the second game, and raised his hand in the Middle of All, making the sign of Kib, and made Men: out of beasts he made them, and Earth was covered with Men.  \Tilde Lord Dunsany}

  The Tribes of the \TheAuthority, the Mortal races, cover each of the moons of Tartarus - from the tops of Acheron's \myital{Mountains of Madness} to the depths of Styx's \myital{Caliphate of Holes}.  Mortals are pursued by Sish, the Destroyer of Hours, and perish beneath the sign of Mung, the God of All Deaths.  Despite the belief that the children of Kib are just playthings for the Small Gods, they breed and spread prolifically.  Through this cycle of life and death, Order is maintained in the face of Chaos.

 You are marked by the sign of Kib, and blessed with a soul (the \myital{noumenon}, the "thing in itself").  Because you have a soul, you are Hallowed; a member of the Tribes sacred to \TheAuthority.  Hallowed things stand in opposition to Magic - the phenomenon whose rules are bound by Chaos rather than Order.

  Mortals are all of the same species (though their appearance varies greatly!).  Mortal Adventurers divide themselves into four different disciplines called \mybold{Tropes:}


    \mylist {
      \item \mybold{\mylink{The Sellsword}{trope-sellsword}}  \\ The heresy of the Saigoths prophesizes that at the end of things, Mung will set his back against Trehagobol and "...wielding the Sword of Severing which is called Death, shall fight out his last fight with the hound Time, his empty scabbard Sleep clattering loose behind him".  You see the inevitability of Death in everything around you, and seek to be the last standing.  Your Primary Stat is \VIG
      

    }

    \cbreak

    \mylist{


      \item \mybold{\mylink{The Knave}{trope-knave}} \\ In the "Sayings of Limpang-Tung", he vows to "... send jests into the world and a little mirth", and that we should pray to Limpang-Tung "... while Death seems to thee as far away as the purple rim of hills; or sorrow as far off as rain in the blue days of summer".   But ... as we grow old, then it is pointless to pray to Limpang-Tung, for you have become "...part of a scheme that he doth not understand".  You are a thrill-seeker and materialist; you seek to drink down life to the last dregs.  You prefer stealth over violence, but you are capable of much violence if need be.  Your Primary Stat is \DEX 

      \item \mybold{\mylink{The Philosopher}{trope-philosopher}} \\ Eld, first of the high Prophets, told the prophet Imbaun on his initiation that "... we have all looked upwards in the Hall of Night towards the secret of Things, and ever it was dark, and the Secret faint and in an unknown tongue."  As we know, however, Imbaun was to become the prophet of Dorozhand, and was shown "... the paths of Sish stretching far down into future time".  There is always more to know before THE END. You seek to understand the Secret and uncover its power, before you fall beneath the sword of Mung.  Your Primary Stat is \INT
      
      \item \mybold{\mylink{The Mystic}{trope-mystic}}   \\ The eyes of Dorozhand, god of Destiny, have gazed upon the Mystic - they become "... the arrow from the bow of Dorozhand hurled forward at a mark he may not see - to the goal of Dorozhand."  Even the Small Gods fear Dorozhand, for "... they have seen a look in the eyes of Dorozhand that regardeth beyond the gods."  You believe in believing; in fate, kismet, and destiny; that we all have a role to play in the Small God's game at the bedside of \TheAuthority. Your Primary Stat is \FOC
    }
  
  \newpage

  \input{tropes/sellswords.tex}
  \newpage
  \input{tropes/knaves.tex}
  \newpage
  \input{tropes/philosophers.tex}
  \newpage
  \input{tropes/mystics.tex}
  \newpage


   
} %end
