% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\renewcommand{\yggIntroduction}{%
  \mychapter{Introduction}{introduction}
}

\renewcommand{\yggIntroductionText}{%

  \end{multicols}


    \topskip0pt
    \vspace*{\fill}

    I don't know if you're reading this, but if you are ... thanks.  Thanks for picking up this game.  I hope it finds a spot at your table.

    So, what can you expect?

    \mybold{"Dungeon Master" friendly}.   I've been the group DM for forever.  I've spent many, many (so many) hours prepping, statting, rolling dice, and trying to create an adventure 2 hours before the game is supposed to start.  These rules are my answer to problems and issues I've seen pop up time and again in games I've run.  Players roll most of the dice (which eases narration for the DM); balanced monster stats can be generated quickly and easily on the fly; and there are multiple resource levers you can pull (instead of just hit points, XP, and money) to give your players a good challenge with plenty of middle ground.

    \mybold{Medium "Crunch"}.  The ToY rules lie in the middle ground between high and low crunch.  While I've got great memories of someone at the table poring over a rulebook and having a sudden "Eureka!" moment, I've also got less happy memories of certain unnamed games losing themselves in the complex rules of their cyberpunk future (random example).  There are plenty of charts and plenty of dice rolling, but I've tried to keep the door open to the "rulings not rules" approach that I think is the most fun

    \mybold{"Old School" feel}. OSR has been an absolute embarassment of riches for the hobby; the involvement of artists in the community has mixed the joy of those old Red Box games with an inventiveness and creativity that has had me jump out of my seat more than once.  OSR is how I remember playing the 80s (or, at least, how I \mybold{wish} my games had been in the 80s).

    I hope you enjoy these rules as much as I did writing them.  May your games be fun, your memories endless, and your friendships eternal!

    \center

    Welcome to the \mybold{Totality of Ygg}

    \vspace*{\fill}

  \begin{multicols}{2}

} %end
